---
title: "Immigration and Customs Enforcement"
toc: false
---

```{r}
library(reactable)
library(tidyverse)
library(glue)

col_defs_ice <- list(
  Type = colDef(
    minWidth = 110,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Type of enforcement action",
        "Type"
      )
    },
    cell = function(value) {
      markdown::markdownToHTML(text = value, fragment.only = TRUE)
    }
  ),
  Start = colDef(
    minWidth = 65,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of first records in the dataset",
        "Start"
      )
    }
  ),
  End = colDef(
    minWidth = 80,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of last records in the dataset",
        "End"
      )
    }
  ),
  Identifiers = colDef(
    name = "IDs",
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Whether the dataset includes unique identifiers that allow linking records across different data types",
        "IDs"
      )
    },
    align = "left",
    minWidth = 35,
    html = TRUE,
    cell = function(value) {
      if (is.na(value)) {
        return(as.character(
          htmltools::tags$div(
            style = "display: flex; align-items: left;",
            htmltools::tags$i(
              class = "fas fa-xmark",
              style = "color: red; font-size: 1.2em;"
            )
          )
        ))
      }

      val <- trimws(value)

      if (val == "--") {
        return("&ndash;") # en dash
      }

      as.character(
        htmltools::tags$div(
          style = "display: flex; align-items: left",
          htmltools::tags$i(
            class = "fas fa-check",
            style = "color: green; font-size: 1.2em;"
          )
        )
      )
    }
  ),
  Records = colDef(
    minWidth = 50,
    align = "right",
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Number of records in the dataset",
        "Records"
      )
    }
  ),
  Raw = colDef(
    show = FALSE,
    minWidth = 40,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Download the raw, unprocessed data as provided by ICE",
        "Raw"
      )
    },
    cell = function(value) {
      if (is.null(value) || length(value) == 0) {
        return("&ndash;") # en dash
      }

      url <- as.character(value[[1]])
      ext <- tolower(trimws(as.character(value[[3]])))

      paste0(
        "<a href='",
        url,
        "'>",
        "<img src='/img/",
        ext,
        ".svg' width=25 height=25 alt='",
        ext,
        "'>",
        "</a>"
      )
    }
  ),
  Processed = colDef(
    # name = "Cleaned",
    minWidth = 85,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Download data cleaned and processed by the Deportation Data Project",
        "Processed"
      )
    },
    cell = function(value) {
      if (is.null(value) || length(value) == 0 || is.na(value[[1]][[1]])) {
        return("&ndash;") # en dash
      }

      links <- map(
        value,
        ~ {
          paste0(
            "<a href='",
            .x[[1]],
            "'>",
            "<img src='/img/",
            .x[[3]],
            ".svg' width=25 height=25 alt='",
            .x[[3]],
            "'>",
            "</a>"
          )
        }
      )

      paste(links, collapse = " ")
    }
  ),
  Explore = colDef(
    minWidth = 55,
    html = TRUE,
    align = "center",
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Explore the data in an interactive tool, filter it, and download subsets.",
        "Explore"
      )
    },
    cell = function(value) {
      if (is.null(value) || length(value) == 0 || is.na(value[[1]][[1]])) {
        return("&ndash;") # en dash
      }

      glue::glue(
        "<a href='{value}'><i class='bi bi-binoculars-fill'></i></a>"
      )
    }
  )
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

ICE collects data on every person it encounters, arrests, detains, transports via flight, and deports, and every detainer request to local jails. We post lightly processed versions of the arrests, detainer requests, detentions, and removals datasets to facilitate analysis. We also post a more heavily processed version of the detention data, collapsed to the detention stay level, to make analysis more straightforward.

::: {.callout-tip appearance="default"}

## Getting started with ICE data

Our [ICE frequently asked data questions](/docs/ice.html#sec-faq) is a good place to start before analyzing the data, and this [page](/docs/ice/processing.html) the steps we have taken to process the datasets on this page. We also provide a [codebook](/docs/ice.html#sec-codebook) that describes each data table and the fields within it.

:::

We recommend citing these data as "government data provided by ICE in response to a FOIA request, processed by the Deportation Data Project, and analyzed by [your organization]."

## Latest data release

The most recent release of data covers ICE enforcement actions through late July 2025. We are actively seeking ongoing updates.

::: {style='text-align: right'}

Explore the data in our interactive tool <i class="bi bi-arrow-down" style="margin-right: 2.1em"></i>

:::

```{r}
tibble::tribble(
  ~Type                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        ,
  ~Start                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  ~End                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         ,
  ~Identifiers                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 ,
  ~Records                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     ,
  ~Raw                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         ,
  ~Processed                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   ,
  ~Explore                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     ,

  # edit all these to have the new info

  "Arrests"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    ,
  "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "292K"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  list("https://ucla.box.com/shared/static/8o9t933aq750z7eblcch11z7twexjbn5.xlsx", "48MB", "xlsx")                                                                                                                                                                                                                                                                                                                                                                                             ,
  list(list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/arrests-latest.xlsx", "38MB", "xlsx"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/arrests-latest.dta", "144MB", "dta"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/arrests-latest.sav", "119MB", "sav"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/arrests-latest.feather", "37MB", "feather"))                                 ,
  "https://deportationdata-ice-arrests.share.connect.posit.cloud"                                                                                                                                                                                                                                                                                                                                                                                                                              ,

  "Detainers"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "339K"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  list("https://ucla.box.com/shared/static/k699orsf5wm8i9ehr1x4foownlj5zuyn.xlsx", "107MB", "xlsx")                                                                                                                                                                                                                                                                                                                                                                                            ,
  list(list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detainers-latest.xlsx", "38MB", "xlsx"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detainers.dta", "144MB", "dta"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detainers.sav", "119MB", "sav"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detainers.feather", "37MB", "feather"))                                              ,
  "https://deportationdata-ice-detainers.share.connect.posit.cloud"                                                                                                                                                                                                                                                                                                                                                                                                                            ,

  "Detention **stints**"                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "1.32M"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      ,
  list("https://ucla.box.com/shared/static/c6tfgtq90er5df898vaq912okchn9o66.xlsx", "280MB", "xlsx")                                                                                                                                                                                                                                                                                                                                                                                            ,
  list(list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detentions-latest.xlsx", "38MB", "xlsx"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detentions-latest.dta", "144MB", "dta"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detentions-latest.sav", "119MB", "sav"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detentions-latest.feather", "37MB", "feather"))                     ,
  list()                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,

  "Detention **stays**"                                                                                                                                                                                                                                                                                                                                                                                                                                                                        ,
  "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "1.32M"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      ,
  list()                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  list(list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detention-stays-latest.xlsx", "38MB", "xlsx"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detention-stays-latest.dta", "144MB", "dta"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detention-stays-latest.sav", "119MB", "sav"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/detention-stays-latest.feather", "37MB", "feather")) ,
  "https://deportationdata-ice-detention-stays.share.connect.posit.cloud"                                                                                                                                                                                                                                                                                                                                                                                                                      ,

  # "Encounters"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 ,
  # "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  # "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  # "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  # "1.36M"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      ,
  # list("https://ucla.box.com/shared/static/tp02l4356coo3vzjbbksk51olobzis73.xlsx", "192MB", "xlsx")                                                                                                                                                                                                                                                                                                                                                                                            ,
  # list()                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  # list()                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,

  "Removals"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   ,
  "Sep. 2023"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "Late Jul. 2025"                                                                                                                                                                                                                                                                                                                                                                                                                                                                             ,
  "528K"                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       ,
  list("https://ucla.box.com/shared/static/hrofkgyefmmvki95f487rpk1wigcefd5.xlsx", "129MB", "xlsx")                                                                                                                                                                                                                                                                                                                                                                                            ,
  list(list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/removals-latest.xlsx", "38MB", "xlsx"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/removals-latest.dta", "144MB", "dta"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/removals-latest.sav", "119MB", "sav"), list("https://github.com/deportationdata/ice/raw/refs/heads/main/data/removals-latest.feather", "37MB", "feather"))                             ,
  "https://deportationdata-ice-removals.share.connect.posit.cloud"
) |>
  reactable::reactable(
    columns = col_defs_ice,
    sortable = FALSE,
    pagination = FALSE
  )
```

<!-- <div style="height: 15px;"></div> -->

