---
title: "Data repository"
---

```{r}
library(reactable)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

col_defs_ice <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Identifiers = colDef(minWidth=50,
    cell = function(value) {
      icon <- if (is.na(value)) "xmark" else "check"
      color <- if (is.na(value)) "red" else "green"
      text <- if (is.na(value)) "" else value
      
      htmltools::tags$div(
        style = "display: flex; align-items: center; gap: 6px;",
        htmltools::tags$i(
          class = paste("fas", paste0("fa-", icon)), 
          style = paste("color:", color, "; font-size: 1.2em;")
        ),
        text
      )
    }
  ),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

col_defs_description <- list(
  Description = colDef(minWidth = 125),
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

This page collects and reposts individual-level Immigration and Customs Enforcement (ICE), Customs and Border Patrol (CBP), and Justice Department Executive Office of Immigration Review (EOIR) datasets. In most cases, these datasets are also available for download elsewhere. The original source is always a government agency (ICE, CBP or EOIR), but where other third parties have posted the data before we have, we link to their sites as the source.

## Immigration and Customs Enforcement

### Arrests

This dataset shows the date and method of every arrest (apprehension), along with some other case information, including basic information about individuals' nationality and whether they had criminal convictions.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
          ~Start,            ~End, ~Identifiers, ~Records,                                                                                      ~Source,                                                                                                                                                          ~Download,
  "Oct. 1, 2016", "Sep. 30, 2023",  "Feb. 2024",   "912K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836542152676'>xlsx</a> (53 MB)",
  "Oct. 1, 2011", "Sep. 30, 2016",  "Feb. 2024",   "901K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555467571'>xlsx</a> (53 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015",           NA,     "1M",                                   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540105544'>xlsx</a> (71 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012",           NA,   "682K",                                   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557464054'>xlsx</a> (41 MB)",
 "Mid Nov. 2023", "Mid Feb. 2025",  "Mar. 2025",   "146K",                                                      "<a href='https://www.ice.gov'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554372496'>xlsx</a> (21 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

### Detainers

Detainers are requests that ICE makes to prisons and jails to hold individuals for transfer to immigration custody and/or to notify ICE of their release dates. This dataset tracks each detainer request.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
                                                                         ~Start,            ~End, ~Records,                                                           ~Source, ~Identifiers,                                                                                                                                                          ~Download,
                                                                 "Oct. 1, 2016", "Sep. 30, 2017",    "94K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554262318'>csv</a> (21 MB)",
                                                                 "Oct. 1, 2015", "Sep. 30, 2016",    "86K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555104717'>csv</a> (19 MB)",
                                                                 "Oct. 1, 2014", "Sep. 30, 2015",    "97K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547271446'>csv</a> (22 MB)",
                                                                 "Oct. 1, 2014", "Sep. 30, 2015",    "79K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,     "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556496547'>txt</a> (9 MB)",
                                                                 "Oct. 1, 2013", "Sep. 30, 2014",   "164K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551310786'>csv</a> (37 MB)",
                                                                 "Oct. 1, 2012", "Sep. 30, 2013",   "217K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550482581'>csv</a> (49 MB)",
                                                                 "Oct. 1, 2012", "Sep. 30, 2013",   "381K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551433566'>txt</a> (22 MB)",
                                                                 "Oct. 1, 2011", "Sep. 30, 2012",   "287K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540940171'>csv</a> (65 MB)",
                                                                 "Oct. 1, 2010", "Sep. 30, 2011",   "317K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552467952'>csv</a> (72 MB)",
                                                                 "Oct. 1, 2010", "Sep. 30, 2011",   "604K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543308523'>txt</a> (35 MB)",
                                                                 "Oct. 1, 2009", "Sep. 30, 2010",   "290K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555210688'>csv</a> (66 MB)",
                                                                 "Oct. 1, 2009", "Sep. 30, 2010",   "290K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543397795'>txt</a> (17 MB)",
                                                                 "Oct. 1, 2008", "Sep. 30, 2009",   "248K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543616508'>csv</a> (53 MB)",
                                                                 "Oct. 1, 2008", "Sep. 30, 2009",   "248K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539862966'>txt</a> (14 MB)",
                                                                 "Oct. 1, 2007", "Sep. 30, 2008",   "212K",   "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836553974742'>txt</a> (12 MB)",
                                                                "Mid Nov. 2023", "Mid Feb. 2025",   "199K",                           "<a href='https://www.ice.gov'>ICE</a>",  "Mar. 2025",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552782163'>xlsx</a> (59 MB)"
                                                                ) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

### Detentions

This dataset includes a row for every detention book-in/book-out. Notice that a single stay in detention—defined by a stay book-in and stay book-out date—may include multiple rows because ICE frequently transfers people between detention centers. We urge particular caution in using this dataset because it only includes book-outs that occurred after November 15, 2023; this means that some information concerning individuals detained at the beginnning of the data may be missing.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
                                                                         ~Start,            ~End, ~Records,                                                                                      ~Source, ~Identifiers,                                                                                                                                                           ~Download,
                                                                 "Oct. 1, 2023", "Sep. 30, 2024",   "115K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538575856'>xlsx</a> (21 MB)",
                                                                 "Oct. 1, 2022", "Sep. 30, 2023",   "471K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557968001'>xlsx</a> (81 MB)",
                                                                 "Oct. 1, 2022", "Sep. 30, 2023",   "514K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556182456'>xlsx</a> (96 MB)",
                                                                 "Oct. 1, 2021", "Sep. 30, 2022",   "447K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537649686'>xlsx</a> (79 MB)",
                                                                 "Oct. 1, 2021", "Sep. 30, 2022",   "481K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551672923'>xlsx</a> (92 MB)",
                                                                 "Oct. 1, 2020", "Sep. 30, 2021",   "441K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547497285'>xlsx</a> (77 MB)",
                                                                 "Oct. 1, 2020", "Sep. 30, 2021",   "363K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545015666'>xlsx</a> (69 MB)",
                                                                 "Oct. 1, 2019", "Sep. 30, 2020",   "355K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540368526'>xlsx</a> (60 MB)",
                                                                 "Oct. 1, 2019", "Sep. 30, 2020",   "415K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540429374'>xlsx</a> (76 MB)",
                                                                 "Oct. 1, 2018", "Sep. 30, 2019",   "878K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548415787'>xlsx</a> (149 MB)",
                                                                 "Oct. 1, 2018", "Sep. 30, 2019",   "941K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545192598'>xlsx</a> (172 MB)",
                                                                 "Oct. 1, 2017", "Sep. 30, 2018",   "929K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541465248'>xlsx</a> (158 MB)",
                                                                 "Oct. 1, 2017", "Sep. 30, 2018",   "904K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550118061'>xlsx</a> (165 MB)",
                                                                 "Oct. 1, 2016", "Sep. 30, 2017",   "781K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537006671'>xlsx</a> (132 MB)",
                                                                 "Oct. 1, 2016", "Sep. 30, 2017",   "757K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545300833'>xlsx</a> (139 MB)",
                                                                 "Oct. 1, 2015", "Sep. 30, 2016",   "772K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547134723'>xlsx</a> (132 MB)",
                                                                 "Oct. 1, 2015", "Sep. 30, 2016",   "748K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551270304'>xlsx</a> (138 MB)",
                                                                 "Oct. 1, 2014", "Sep. 30, 2015",   "684K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538472510'>xlsx</a> (117 MB)",
                                                                 "Oct. 1, 2014", "Sep. 30, 2015",   "655K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545212556'>xlsx</a> (120 MB)",
                                                                 "Oct. 1, 2013", "Sep. 30, 2014",   "823K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538338110'>xlsx</a> (149 MB)",
                                                                 "Oct. 1, 2013", "Sep. 30, 2014",   "849K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270445'>xlsx</a> (157 MB)",
                                                                 "Oct. 1, 2012", "Sep. 30, 2013",   "868K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543474267'>xlsx</a> (149 MB)",
                                                                 "Oct. 1, 2012", "Sep. 30, 2013",   "877K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539896765'>xlsx</a> (163 MB)",
                                                                 "Oct. 1, 2011", "Sep. 30, 2012",     "1M",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",  "Feb. 2024",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551063854'>xlsx</a> (172 MB)",
                                                                 "Oct. 1, 2011", "Sep. 30, 2012",   "988K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538890174'>xlsx</a> (180 MB)",
                                                                 "Oct. 1, 2010", "Sep. 30, 2011",    "60K",                                    "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558695933'>xlsx</a> (12 MB)",
                                                                "Mid Nov. 2023", "Mid Feb. 2025",   "768K",                                                      "<a href='https://www.ice.gov'>ICE</a>",  "Mar. 2025",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836559130180'>xlsx</a> (142 MB)"
                                                                ) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

### Encounters

This dataset records each encounter that an ICE officer had with someone, whether or not that encounter resulted in an arrest.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
                                                                         ~Start,            ~End, ~Records,                                                      ~Source, ~Identifiers,                                                                                                                                                           ~Download,
                                                                 "Oct. 1, 2014", "Sep. 30, 2015",     "3M",   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",           NA,   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539886526'>xlsx</a> (163 MB)",
                                                                 "Oct. 1, 2011", "Sep. 30, 2012",     "2M",   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",           NA,    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545587160'>xlsx</a> (97 MB)",
                                                                "Mid Nov. 2023", "Mid Feb. 2025",   "869K",                      "<a href='https://www.ice.gov'>ICE</a>",  "Mar. 2025",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544630925'>xlsx</a> (112 MB)"
                                                                ) |> 
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

### Flights

Data on ICE-operated charter flights and passenger manifests from the Immigration and Customs Enforcement's ARTS system.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
       ~Description,         ~Start,            ~End, ~Records,                                                  ~Source,                                                                                                                                                           ~Download,
  "Flight missions", "Oct. 1, 2018",  "May. 8, 2020",     "3K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545668509'>xlsx</a> (460 kB)",
       "Passengers", "Oct. 1, 2018",  "May. 8, 2020",   "341K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550007406'>xlsx</a> (55 MB)",
  "Flight missions", "Oct. 1, 2018", "Sep. 30, 2019",     "1K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537162853'>xlsx</a> (188 kB)",
       "Passengers", "Oct. 1, 2018", "Sep. 30, 2019",    "37K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",     "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536207751'>xlsx</a> (6 MB)",
  "Flight missions", "Oct. 1, 2017", "Sep. 30, 2018",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550883008'>xlsx</a> (246 kB)",
       "Passengers", "Oct. 1, 2017", "Sep. 30, 2018",   "192K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836553076817'>xlsx</a> (28 MB)",
  "Flight missions", "Oct. 1, 2016", "Sep. 30, 2017",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549806043'>xlsx</a> (240 kB)",
       "Passengers", "Oct. 1, 2016", "Sep. 30, 2017",   "180K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541672269'>xlsx</a> (27 MB)",
  "Flight missions", "Oct. 1, 2015", "Sep. 30, 2016",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536493019'>xlsx</a> (273 kB)",
       "Passengers", "Oct. 1, 2015", "Sep. 30, 2016",   "168K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549772221'>xlsx</a> (25 MB)",
  "Flight missions", "Oct. 1, 2014", "Sep. 30, 2015",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538695921'>xlsx</a> (226 kB)",
       "Passengers", "Oct. 1, 2014", "Sep. 30, 2015",   "157K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539073027'>xlsx</a> (23 MB)",
  "Flight missions", "Oct. 1, 2013", "Sep. 30, 2014",     "6K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540958981'>xlsx</a> (642 kB)",
       "Passengers", "Oct. 1, 2013", "Sep. 30, 2014",   "250K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545751933'>xlsx</a> (37 MB)",
  "Flight missions", "Oct. 1, 2012", "Sep. 30, 2013",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549849021'>xlsx</a> (311 kB)",
       "Passengers", "Oct. 1, 2012", "Sep. 30, 2013",   "264K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555001702'>xlsx</a> (40 MB)",
  "Flight missions", "Oct. 1, 2011", "Sep. 30, 2012",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552599950'>xlsx</a> (322 kB)",
       "Passengers", "Oct. 1, 2011", "Sep. 30, 2012",   "282K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538136812'>xlsx</a> (44 MB)",
  "Flight missions", "Oct. 1, 2010", "Sep. 30, 2011",     "2K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540049661'>xlsx</a> (265 kB)",
       "Passengers", "Oct. 1, 2010", "Sep. 30, 2011",   "233K",   "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536399014'>xlsx</a> (36 MB)"
  ) |>
  reactable::reactable(columns = col_defs_description, pagination = FALSE)
```

</details>

### Removals (deportations)

This dataset includes a row for every removal (deportation) that ICE conducted. Note that individuals can be returned or expelled by CBP at the border without appearing in this dataset. 

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
          ~Start,            ~End, ~Identifiers, ~Records,                                                                                      ~Source,                                                                                                                                                           ~Download,
  "Oct. 1, 2019", "Sep. 30, 2023",  "Feb. 2024",   "454K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552901309'>xlsx</a> (85 MB)",
  "Oct. 1, 2016", "Sep. 30, 2019",  "Feb. 2024",   "752K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537875130'>xlsx</a> (137 MB)",
  "Oct. 1, 2013", "Sep. 30, 2016",  "Feb. 2024",   "793K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543019179'>xlsx</a> (143 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015",           NA,     "2M",                                   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555735995'>xlsx</a> (95 MB)",
  "Oct. 1, 2011", "Sep. 30, 2013",  "Feb. 2024",   "773K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836542804617'>xlsx</a> (139 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012",           NA,     "1M",                                   "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557461924'>xlsx</a> (60 MB)"
  ) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

### Risk classification assessments

This dataset shows information on each risk classification assessment (RCA)–the procedure used by ICE to determine danger and flight risk. Note that the RCA tool is used both to help ICE officers decide whether to detain or release a person and to determine risk levels for detention (see the `rca_decision_type` field). 

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
          ~Start,            ~End, ~Identifiers, ~Records,                                                                                      ~Source,                                                                                                                                                           ~Download,
  "Oct. 1, 2022", "Sep. 30, 2023",  "Feb. 2024",   "330K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551596696'>xlsx</a> (58 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022",  "Feb. 2024",   "347K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544905050'>xlsx</a> (60 MB)",
  "Oct. 1, 2020", "Sep. 30, 2021",  "Feb. 2024",   "207K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549849007'>xlsx</a> (36 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020",  "Feb. 2024",    "83K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554341800'>xlsx</a> (22 MB)",
  "Oct. 1, 2018", "Sep. 30, 2019",  "Feb. 2024",   "435K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540750526'>xlsx</a> (77 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018",  "Feb. 2024",   "433K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552112243'>xlsx</a> (77 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017",  "Feb. 2024",   "393K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539522069'>xlsx</a> (70 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016",  "Feb. 2024",   "353K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552159782'>xlsx</a> (63 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015",  "Feb. 2024",   "273K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554502095'>xlsx</a> (49 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014",  "Feb. 2024",   "368K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546882084'>xlsx</a> (66 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013",  "Feb. 2024",   "320K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",    "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546882337'>xlsx</a> (63 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012",  "Feb. 2024",     "2K",   "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540294710'>xlsx</a> (432 kB)"
  ) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Customs and Border Protection

CBP collects individual-level data on every person it arrests or expels at the border as well as on every person who arrives at a port of entry whom it deems inadmissible (most frequently asylum seekers). Border arrest data are collected by the Border Patrol; inadmissible arrivals data are collected by the Office of Field Operations. CBP maintains a detailed [FOIA library](https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room) with these datasets and others.

### Apprehensions at the border

This dataset includes every apprehension at the border. Before 2020, all border arrests were apprehensions, and these files therefore include all arrests for those years. With the onset of the Title 42 pandemic expulsions program, some border arrests led to expulsions, which CBP does not categorize as apprehensions.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Records, ~Source, ~Download,
  "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529466108'>xlsx</a> (45 MB)",
  "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524552711'>xlsx</a> (35 MB)",
  "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524452168'>xlsx</a> (35 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537472516'>xlsx</a> (26 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522219652'>xlsx</a> (31 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522010833'>xlsx</a> (40 MB)",
  "Oct. 1, 2013", "Mar. 31, 2014", "215K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536497781'>xlsx</a> (24 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523485219'>xlsx</a> (34 MB)",
  "Oct. 1, 2015", "Mar. 31, 2016", "189K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527949432'>xlsx</a> (20 MB)",
  "Apr. 1, 2016", "Sep. 30, 2016", "227K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536771304'>xlsx</a> (30 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522642202'>xlsx</a> (34 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536816904'>xlsx</a> (42 MB)",
  "Oct. 1, 2018", "Mar. 31, 2019", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534563529'>xlsx</a> (38 MB)",
  "Apr. 1, 2019", "Jun. 30, 2019", "329K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539665388'>xlsx</a> (34 MB)",
  "Jul. 1, 2019", "Sep. 30, 2019", "165K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538377500'>xlsx</a> (17 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836518613189'>xlsx</a> (23 MB)",
  "Oct. 1, 2020", "Mar. 31, 2021", "126K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532799369'>xlsx</a> (14 MB)",
  "Apr. 1, 2021", "Jun. 30, 2021", "200K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531099951'>xlsx</a> (21 MB)",
  "Jul. 1, 2021", "Sep. 30, 2021", "296K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535939039'>xlsx</a> (30 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527984953'>xlsx</a> (110 MB)"
) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>

### People deemed inadmissable at ports of entry

This dataset includes records of each person CBP found inadmissible at a port of entry. These are mostly asylum seekers.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Records, ~Source, ~Download,
  "Jan. 1, 2014", "Dec. 31, 2014", "557K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536350802'>xlsx</a> (61 MB)",
  "Jan. 1, 2015", "Dec. 31, 2015", "671K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517811895'>xlsx</a> (74 MB)",
  "Jan. 1, 2016", "Dec. 31, 2016", "829K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530605254'>xlsx</a> (91 MB)",
  "Jan. 1, 2017", "Dec. 31, 2017", "546K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529580929'>xlsx</a> (64 MB)",
  "Jan. 1, 2018", "Dec. 31, 2018", "673K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538742245'>xlsx</a> (77 MB)",
  "Jan. 1, 2019", "Dec. 31, 2019", "49K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519445234'>xlsx</a> (26 MB)",
  "Jan. 1, 2020", "Dec. 31, 2020", "391K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519054034'>xlsx</a> (44 MB)",
  "Apr. 2020", "Mar. 2022", "503K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517807065'>xlsx</a> (38 MB)",
  "Jan. 1, 2021", "Dec. 31, 2021", "602K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537280774'>xlsx</a> (68 MB)",
  "Jan. 1, 2022", "Dec. 31, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527086921'>xlsx</a> (119 MB)",
  "Jan. 1, 2022", "Dec. 31, 2022", "281K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534928426'>xlsx</a> (31 MB)",
  "Apr. 2022", "Apr. 2022", "53K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522332574'>xlsx</a> (4 MB)",
  "Jul. 2022", "Feb. 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525107263'>xlsx</a> (38 MB)",
  "Jul. 2022", "Feb. 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529242001'>xlsx</a> (38 MB)",
  "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524171859'>xlsx</a> (119 MB)",
  "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526905068'>xlsx</a> (115 MB)",
  "Jan. 1, 2023", "Dec. 31, 2023", "775K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522164658'>xlsx</a> (85 MB)",
  "May. 2023", "Jul. 2023", "175K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524781374'>xlsx</a> (12 MB)",
  "Jul. 2023", "Jul. 2023", "110K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521186280'>xlsx</a> (8 MB)",
  "Jul. 1, 2023", "Dec. 31, 2023", "708K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525779953'>xlsx</a> (52 MB)",
  "Nov. 1, 2023", "Aug. 1, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533367753'>xlsx</a> (76 MB)",
  "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530361246'>xlsx</a> (118 MB)",
  "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519236948'>xlsx</a> (115 MB)",
  "Jan. 1, 2024", "Dec. 31, 2024", "477K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536102266'>xlsx</a> (52 MB)",
  "Jan. 1, 2024", "Jun. 30, 2024", "692K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522055139'>xlsx</a> (51 MB)",
  "Oct. 1, 2024", "Nov. 30, 2024", "163K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533627763'>xlsx</a> (12 MB)",
  "Oct. 1, 2024", "Mar. 19, 2025", "478K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842173428525'>xlsx</a>, part 1 (52 MB)",
  "Oct. 1, 2024", "Mar. 19, 2025", "430K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842164368478'>xlsx</a>, part 2 (46 MB)"
) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>


### Title 42 expulsions

This dataset includes Title 42 expulsions: the border arrests that CBP does not categorize as apprehensions.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Records, ~Source, ~Download,
  "Oct. 1, 2019", "Sep. 30, 2020", "197K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519515324'>xlsx</a> (18 MB)",
  "Oct. 1, 2020", "Sep. 30, 2021", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538878230'>xlsx</a> (98 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "738K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530089384'>xlsx</a> (74 MB)"
) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>

### Encounters 

This dataset includes all border arrests, both apprehensions and Title 42 expulsions. Notice, however, that it exists currently only for a relatively short period.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Records, ~Source, ~Download,
  "Oct. 1, 2022", "Dec. 31, 2022", "640K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519013469'>xlsx</a> (95 MB)",
  "Jan. 1, 2023", "Mar. 31, 2023", "428K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523031829'>xlsx</a> (64 MB)",
  "Apr. 1, 2023", "Jun. 30, 2023", "458K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539840495'>xlsx</a> (68 MB)",
  "Jul. 1, 2023", "Sep. 30, 2023", "537K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528623980'>xlsx</a> (80 MB)",
  "Oct. 1, 2023", "Dec. 31, 2023", "634K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529574328'>xlsx</a> (95 MB)",
  "Jan. 1, 2024", "Mar. 31, 2024", "407K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538501297'>xlsx</a> (61 MB)",
  "Apr. 1, 2024", "Jun. 30, 2024", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524426045'>xlsx</a> (51 MB)",
  "Jul. 1, 2024", "Sep. 30, 2024", "176K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522527618'>xlsx</a> (27 MB)"
) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>

### Annual apprehensions with place of origin

This dataset includes each person's city and state of origin, but it lacks precise dates for each apprehension (it shows only the fiscal year), limiting its use. The file names suggest that these files only contain family apprehensions, but they actually contain all apprehensions.

<details>
<summary>Show datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Records, ~Source, ~Download,
  "Oct. 1, 1999", "Sep. 30, 2000", "2M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526779834'>xlsx</a> (56 MB)",
  "Oct. 1, 2000", "Sep. 30, 2001", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521865479'>xlsx</a> (44 MB)",
  "Oct. 1, 2001", "Sep. 30, 2002", "954K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536752416'>xlsx</a> (34 MB)",
  "Oct. 1, 2002", "Sep. 30, 2003", "932K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535002120'>xlsx</a> (34 MB)",
  "Oct. 1, 2003", "Sep. 30, 2004", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523854174'>xlsx</a> (43 MB)",
  "Oct. 1, 2004", "Sep. 30, 2005", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538413035'>xlsx</a> (43 MB)",
  "Oct. 1, 2005", "Sep. 30, 2006", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525352489'>xlsx</a> (39 MB)",
  "Oct. 1, 2006", "Sep. 30, 2007", "877K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836520753674'>xlsx</a> (35 MB)",
  "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397984'>xlsx</a> (28 MB)",
  "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528500592'>xlsx</a> (22 MB)",
  "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537505751'>xlsx</a> (18 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536574704'>xlsx</a> (14 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523110035'>xlsx</a> (15 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527799721'>xlsx</a> (17 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014", "487K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529955831'>xlsx</a> (20 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531582054'>xlsx</a> (14 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", "416K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397977'>xlsx</a> (20 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525028767'>xlsx</a> (15 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539329278'>xlsx</a> (20 MB)",
  "Oct. 1, 2018", "Sep. 30, 2019", "860K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526972753'>xlsx</a> (42 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527670543'>xlsx</a> (10 MB)",
  "Oct. 1, 2020", "Sep. 30, 2021", "621K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522751005'>xlsx</a> (30 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529123179'>xlsx</a> (54 MB)"
) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>

## Executive Office for Immigration Review<br>(Immigration Courts)

The Executive Office for Immigration Review at the Department of Justice collects information on every immigration court case, including information on scheduling, case type, immigration charges, applications for relief, and appeals. The datasets includes records from the 1970s to the last year, though most are much more recent. The agency posts an updated dataset monthly in their [FOIA Library](https://www.justice.gov/eoir/foia-library-0), because of a FOIA request originally filed by [TRAC](https://tracreports.org). 

<details>
<summary>Show datasets</summary>

```{r}
col_defs_description <- list(
  Description = colDef(minWidth = 125),
  `Release date` = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 75, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

tibble::tribble(
  ~Description, ~`Release date`, ~Records, ~Source, ~Download,
  "A_TblCase_raw.csv", "Apr. 14, 2025", "12M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954823189'>csv</a> (2 GB)",
  "A_TblCaseIdentifier_raw.csv", "Apr. 14, 2025", "2M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947358092'>csv</a> (45 MB)",
  "B_TblProceedCharges_raw.csv", "Apr. 14, 2025", "18M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952799263'>csv</a> (680 MB)",
  "B_TblProceeding_raw.csv", "Apr. 14, 2025", "15M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952424406'>csv</a> (3 GB)",
  "D_TblAssociatedBond_raw.csv", "Apr. 14, 2025", "2M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948167414'>csv</a> (409 MB)",
  "tbl_br_DeductCodes_raw.csv", "Apr. 14, 2025", "14", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951242204'>csv</a> (803 B)",
  "tbl_CasePriorityHistory_raw.csv", "Apr. 14, 2025", "133K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839956173976'>csv</a> (9 MB)",
  "tbl_Court_Appln_raw.csv", "Apr. 14, 2025", "14M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949403111'>csv</a> (807 MB)",
  "tbl_Court_Motions_raw.csv", "Apr. 14, 2025", "7M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947425637'>csv</a> (2 GB)",
  "tbl_CustodyHistory_raw.csv", "Apr. 14, 2025", "9M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947210035'>csv</a> (271 MB)",
  "tbl_EOIR_Attorney_raw.csv", "Apr. 14, 2025", "393K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947374844'>csv</a> (40 MB)",
  "tbl_JuvenileHistory_raw.csv", "Apr. 14, 2025", "3M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954429047'>csv</a> (169 MB)",
  "tbl_Lead_Rider_raw.csv", "Apr. 14, 2025", "2M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947295912'>csv</a> (247 MB)",
  "tbl_RepsAssigned_raw.csv", "Apr. 14, 2025", "24M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955799231'>csv</a> (2 GB)",
  "tbl_schedule_raw.csv", "Apr. 14, 2025", "42M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947569468'>csv</a> (9 GB)",
  "tblAdjournmentcodes_raw.csv", "Apr. 14, 2025", "122", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839950678164'>csv</a> (11 kB)",
  "tblAppeal_raw.csv", "Apr. 14, 2025", "1M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955197423'>csv</a> (167 MB)",
  "tblAppeal2_raw.csv", "Apr. 14, 2025", "1M", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954303740'>csv</a> (27 MB)",
  "tblAppealFedCourts_raw.csv", "Apr. 14, 2025", "177K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955470163'>csv</a> (7 MB)",
  "tblBarCodeType_raw.csv", "Apr. 14, 2025", "141", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946751217'>csv</a> (11 kB)",
  "tblDecCode_raw.csv", "Apr. 14, 2025", "12", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839953735200'>csv</a> (655 B)",
  "tblInmateHousing_raw.csv", "Apr. 14, 2025", "5K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948739133'>csv</a> (393 kB)",
  "tblINSoffice_raw.csv", "Apr. 14, 2025", "71", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949268696'>csv</a> (6 kB)",
  "tblLanguage_raw.csv", "Apr. 14, 2025", "699", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952065547'>csv</a> (49 kB)",
  "tblPanels_raw.csv", "Apr. 14, 2025", "20", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948020547'>csv</a> (1 kB)",
  "tblProBono_raw.csv", "Apr. 14, 2025", "63K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949952518'>csv</a> (14 MB)",
  "tblResponsibleParty_raw.csv", "Apr. 14, 2025", "3K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947404215'>csv</a> (223 kB)",
  "tblTeams_raw.csv", "Apr. 14, 2025", "37", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839950403872'>csv</a> (2 kB)",
  "tblThreeMbrReferrals_raw.csv", "Apr. 14, 2025", "82K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952280406'>csv</a> (4 MB)",
  "tblTortureConvID_raw.csv", "Apr. 14, 2025", "8", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839953841356'>csv</a> (475 B)"
) |>
  reactable::reactable(columns = col_defs_description, pagination = FALSE)
```

</details>

<details>
<summary>Show lookup tables (codebooks)</summary>

```{r}
col_defs_description <- list(
  Description = colDef(minWidth = 125),
  `Release date` = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 75, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

tibble::tribble(
  ~Description, ~`Release date`, ~Records, ~Source, ~Download,
  
  "tblLookUp_Appln_raw.csv", "Apr. 14, 2025", "40", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948129242'>csv</a> (5 kB)",
  "tblLookup_BIACluster_raw.csv", "Apr. 14, 2025", "242", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952290089'>csv</a> (13 kB)",
  "tblLookup_CasePriority_raw.csv", "Apr. 14, 2025", "6", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947764045'>csv</a> (624 B)",
  "tbllookup_Category_raw.csv", "Apr. 14, 2025", "7", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948059484'>csv</a> (465 B)",
  "tblLookup_INS_Clock_Entry_Status_raw.csv", "Apr. 14, 2025", "8", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954299137'>csv</a> (777 B)",
  "tblLookup_Juvenile_raw.csv", "Apr. 14, 2025", "6", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949835774'>csv</a> (547 B)",
  "tblLookup3MbrReferredReason_raw.csv", "Apr. 14, 2025", "7", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948166932'>csv</a> (636 B)",
  "tblLookupAlienNat_raw.csv", "Apr. 14, 2025", "256", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947464303'>csv</a> (18 kB)",
  "tblLookUpAllegationStmt_raw.csv", "Apr. 14, 2025", "3", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954870587'>csv</a> (367 B)",
  "tblLookupAppealIssues_raw.csv", "Apr. 14, 2025", "246", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947670137'>csv</a> (19 kB)",
  "tbllookupAppealType_raw.csv", "Apr. 14, 2025", "19", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954164737'>csv</a> (2 kB)",
  "tblLookupBaseCity_raw.csv", "Apr. 14, 2025", "96", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946717359'>csv</a> (23 kB)",
  "tblLookupBIA_raw.csv", "Apr. 14, 2025", "841", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951176883'>csv</a> (57 kB)",
  "tblLookupBIADecision_raw.csv", "Apr. 14, 2025", "53", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946628894'>csv</a> (4 kB)",
  "tblLookupBIADecisionType_raw.csv", "Apr. 14, 2025", "5", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949720465'>csv</a> (364 B)",
  "tblLookupBoardMotions_raw.csv", "Apr. 14, 2025", "16", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954416414'>csv</a> (2 kB)",
  "tbllookupCal_Type_raw.csv", "Apr. 14, 2025", "29", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955657411'>csv</a> (2 kB)",
  "tblLookupCallup_Reasons_raw.csv", "Apr. 14, 2025", "29", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952856875'>csv</a> (3 kB)",
  "tblLookUpCaseIdentifier_raw.csv", "Apr. 14, 2025", "110", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955749386'>csv</a> (9 kB)",
  "tblLookupCaseType_raw.csv", "Apr. 14, 2025", "13", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948940116'>csv</a> (904 B)",
  "tbllookupCharges_raw.csv", "Apr. 14, 2025", "252", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952852544'>csv</a> (30 kB)",
  "tblLookupClaimedIssue_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954904633'>csv</a> (236 B)",
  "tblLookupCommentTypeBoard_raw.csv", "Apr. 14, 2025", "9", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839950451921'>csv</a> (540 B)",
  "tblLookupComponents_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952022108'>csv</a> (228 B)",
  "tblLookupConsultedWith_raw.csv", "Apr. 14, 2025", "5", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947216444'>csv</a> (280 B)",
  "tblLookupContactChange_raw.csv", "Apr. 14, 2025", "9", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951896425'>csv</a> (859 B)",
  "tblLookupCountry_raw.csv", "Apr. 14, 2025", "254", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946629296'>csv</a> (18 kB)",
  "tblLookupCourtAppDecisions_raw.csv", "Apr. 14, 2025", "14", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839957513413'>csv</a> (990 B)",
  "tblLookupCourtDecision_raw.csv", "Apr. 14, 2025", "207", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947728019'>csv</a> (14 kB)",
  "tblLookupCustodyStatus_raw.csv", "Apr. 14, 2025", "3", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946100616'>csv</a> (182 B)",
  "tblLookUpDDDecisionTypes_raw.csv", "Apr. 14, 2025", "23", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954700355'>csv</a> (2 kB)",
  "tblLookupDistrictLocation_raw.csv", "Apr. 14, 2025", "268", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839946420798'>csv</a> (24 kB)",
  "tblLookupFedCourtDecision_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948766986'>csv</a> (350 B)",
  "tblLookupFedCourtRemandTo_raw.csv", "Apr. 14, 2025", "2", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947859633'>csv</a> (193 B)",
  "tblLookupFeeStatus_raw.csv", "Apr. 14, 2025", "5", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949684465'>csv</a> (386 B)",
  "tblLookupFeeType_raw.csv", "Apr. 14, 2025", "3", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947012482'>csv</a> (297 B)",
  "tblLookupFiledBy_raw.csv", "Apr. 14, 2025", "9", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948584989'>csv</a> (578 B)",
  "tblLookupFiling_Method_Party_raw.csv", "Apr. 14, 2025", "10", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955810967'>csv</a> (595 B)",
  "tblLookupFiling_Method_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951165182'>csv</a> (305 B)",
  "tblLookupFinalDisposition_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949626559'>csv</a> (339 B)",
  "tblLookupGender_raw.csv", "Apr. 14, 2025", "2", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952518926'>csv</a> (147 B)",
  "tblLookupHloc_raw.csv", "Apr. 14, 2025", "1K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949643246'>csv</a> (228 kB)",
  "tblLookupHoldReason_raw.csv", "Apr. 14, 2025", "37", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952155685'>csv</a> (3 kB)",
  "tblLookupHolidays_raw.csv", "Apr. 14, 2025", "613", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947176615'>csv</a> (47 kB)",
  "tblLookupInmate_raw.csv", "Apr. 14, 2025", "5K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839953051339'>csv</a> (835 kB)",
  "tblLookUpINSAddress_raw.csv", "Apr. 14, 2025", "730", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952225381'>csv</a> (100 kB)",
  "tblLookupINSLOC_raw.csv", "Apr. 14, 2025", "1K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839949336419'>csv</a> (76 kB)",
  "tblLookupINSTA_raw.csv", "Apr. 14, 2025", "8K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948402873'>csv</a> (477 kB)",
  "tblLookupInTrPr_raw.csv", "Apr. 14, 2025", "94", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952225640'>csv</a> (5 kB)",
  "tblLookupInTrPrAgenda_raw.csv", "Apr. 14, 2025", "5", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955053060'>csv</a> (603 B)",
  "tblLookupIntrPrLang_raw.csv", "Apr. 14, 2025", "14", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952746475'>csv</a> (970 B)",
  "tblLookupInTrPrLangGroup_raw.csv", "Apr. 14, 2025", "2", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955425046'>csv</a> (226 B)",
  "tblLookupJudge_raw.csv", "Apr. 14, 2025", "1K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955372246'>csv</a> (131 kB)",
  "tblLookupJudgeBaseCity_raw.csv", "Apr. 14, 2025", "10K", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839953665729'>csv</a> (1 MB)",
  "tblLookupMotionType_raw.csv", "Apr. 14, 2025", "71", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839948403080'>csv</a> (8 kB)",
  "tblLookupNationality_raw.csv", "Apr. 14, 2025", "251", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839956987222'>csv</a> (15 kB)",
  "tblLookupNOTICE_raw.csv", "Apr. 14, 2025", "598", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839956138314'>csv</a> (38 kB)",
  "tblLookupOAResponse_raw.csv", "Apr. 14, 2025", "4", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947490564'>csv</a> (292 B)",
  "tblLookupOfficeLocation_raw.csv", "Apr. 14, 2025", "243", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952283993'>csv</a> (21 kB)",
  "tblLookupPriority_raw.csv", "Apr. 14, 2025", "15", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951237404'>csv</a> (1 kB)",
  "tblLookupRegion_raw.csv", "Apr. 14, 2025", "2", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839947901057'>csv</a> (163 B)",
  "tbllookupSchedule_Type_raw.csv", "Apr. 14, 2025", "36", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839955998744'>csv</a> (2 kB)",
  "tblLookupService_Method_raw.csv", "Apr. 14, 2025", "6", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839954476511'>csv</a> (413 B)",
  "tblLookupSpecialIssue_raw.csv", "Apr. 14, 2025", "43", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839952027087'>csv</a> (3 kB)",
  "tblLookupState_raw.csv", "Apr. 14, 2025", "59", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839950050918'>csv</a> (3 kB)",
  "tblLookupTranscribers_raw.csv", "Apr. 14, 2025", "14", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839956411281'>csv</a> (1 kB)",
  "tblLookupVote_raw.csv", "Apr. 14, 2025", "7", "<a href='https://www.justice.gov/eoir/foia-library-0'>EOIR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1839951788645'>csv</a> (448 B)"
) |>
  reactable::reactable(columns = col_defs_description, pagination = FALSE)
```

</details>


