---
title: "Report repository"
---

```{r}
library(tidyverse)
library(reactable)
library(tibble)

format_date <- function(date) {
  format(date, "%b. %Y")
}

options(reactable.theme = reactableTheme(
  backgroundColor = "#F4F6F7"
))
```

This page collects and reposts reports that include data from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Patrol (CBP), and Justice Department Executive Office of Immigration Review (EOIR) datasets. In most cases, these reports are also available for download elsewhere. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the data before we have, we link to their sites as the source.

## Customs and Border Patrol 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Extensive set of statistics covering many parts of CBP's enforcement actions.

[Criminal Noncitizen Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics/criminal-noncitizen-statistics)
: Arrests and convictions of noncitizens by year and type of crime. 

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
[Border Search of Electronic Devices at Ports of Entry](https://www.cbp.gov/travel/cbp-search-authority/border-search-electronic-devices)
[Weapons and Ammunition Seizures](https://www.cbp.gov/newsroom/stats/weapons-and-ammunition-seizures)
[Intellectual Property Rights Seizures](https://www.cbp.gov/newsroom/stats/intellectual-property-rights-ipr-seizures)
[Air and Marine Operations Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics/air-and-marine-operations-statistics)
[Drug Seizure Statistics](https://www.cbp.gov/newsroom/stats/drug-seizure-statistics)
[Currency & Other Monetary Instrument Seizures](https://www.cbp.gov/newsroom/stats/currency-other-monetary-instrument-seizures)
[Criminal Noncitizen Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics/criminal-noncitizen-statistics)

## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

```{r}
enf_files <- 
tribble(
  ~Filename, 
  "2024_1108_ohss_immigration-enforcement-and-legal-processes-tables-july-2024.xlsx",
  "2024_1206_ohss_immigration-enforcement-and-legal-processes-tables-august-2024.xlsx",
  "2025_0116_ohss_immigration-enforcement-and-legal-processes-tables-november-2024.xlsx",
  "24_0105_ohss_immigration-enforcement-and-legal-processes-tables-september-2023_v2.xlsx",
  "24-0209_ohss_immigration-enforcement-and-legal-processes-tables-october-2023_v2.xlsx",
  "24-0308_ohss_immigration-enforcement-and-legal-processes-tables-november-2023_2.xlsx",
  "24-0405_ohss_immigration-enforcement-and-legal-processes-tables-december-2023.xlsx",
  "24-0510_ohss_immigration-enforcement-and-legal-processes-tables-january-2024.xlsx",
  "24-0607_ohss_immigration-enforcement-and-legal-processes-tables-february-2024.xlsx",
  "24-0705_ohss_immigration-enforcement-and-legal-processes-tables-march-2024.xlsx",
  "24-0809_ohss_immigration-enforcement-and-legal-processes-tables-april-2024.xlsx",
  "24-0906_ohss_immigration-enforcement-and-legal-processes-tables-may-2024_v2.xlsx",
  "24-1011_ohss_immigration-enforcement-and-legal-processes-tables-june-2024_2.xlsx"
) |> 
  mutate(
    raw = str_extract(Filename, "(?:\\d{4}|\\d{2})[-_]\\d{4}"),
    compact = str_remove_all(raw, "[-_]"),
    Date = if_else(
      nchar(compact) == 6,
      mdy(paste0(str_sub(compact, 3), str_sub(compact, 1, 2))),
      mdy(paste0(str_sub(compact, 5), str_sub(compact, 1, 4)))
    )
   ) |> 
    arrange(desc(Date)) |> 
    mutate(
  Date = format(Date, "%b. %Y"),
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>")
) |> 
  transmute(Date, Source, Download)
```

```{r}
enf_files |> 
  slice(1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<details>
<summary>Past reports</summary>

```{r}
enf_files |> 
  slice(-1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>



## Immigration and Customs Enforcement

### Annual report

```{r}
ice_annual_reports_files <- 
  tibble(
  Filename = c(
  "iceAnnualReportFY2021.pdf",
  "iceAnnualReportFY2022.pdf",
  "iceAnnualReportFY2023.pdf",
  "iceAnnualReportFY2024.pdf",
  "iceReportFY2020.pdf")
) |> 
  mutate(
    Date = str_extract(Filename, "\\d{4}") 
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>")
) |> 
  transmute(Date, Source, Download) 
```

```{r}
ice_annual_reports_files |> 
  slice(1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |> 
  slice(-1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

### Detention management spreadsheet

#### Year-to-date:

```{r}
tibble(
  Filename = "https://www.dropbox.com/scl/fi/afrhtn32ven3r4pkzmvmt/FY25_detentionStats04162025.xlsx?rlkey=kuxbpcae0jdgamultzp0xai27&dl=1",
  Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"), 
  Date = format(as.Date("2025-04-16"), "%b. %d, %Y"),
  Download = glue::glue("<a href='{Filename}'>FY25_detentionStats04162025.xlsx</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
tribble(
  ~Filename, 
  "FY25_detentionStats01032025.xlsx",
  "FY25_detentionStats01162025.xlsx",
  "FY25_detentionStats02032025.xlsx",
  "FY25_detentionStats02142025.xlsx",
  "FY25_detentionStats02272025.xlsx",
  "FY25_detentionStats03052025.xlsx",
  "FY25_detentionStats03142025.xlsx",
  "FY25_detentionStats03262025.xlsx",
  "FY25_detentionStats04162025.xlsx",
  "FY25_detentionStats11212024.xlsx",
  "FY25_detentionStats12112024.xlsx",
  "FY25_detentionStats12122024.xlsx",
  "FY25_detentionStats12182024.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "\\d{8}(?=\\.xlsx)") |> mdy()
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
  Date = format(Date, "%b. %d, %Y"),
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

#### End-of-fiscal-year:

```{r}
tribble(
  ~Filename, 
  "FY24_detentionStats.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "(?<=FY)\\d{2}") |> as.integer(),
    Date = Date + 2000
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```
<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
tribble(
  ~Filename, 
    "FY19-detentionstats.xlsx",
  "FY20-detentionstats.xlsx",
  "FY21-detentionstats.xlsx",
  "FY22-detentionStats.xlsx",
  "FY23_detentionStats.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "(?<=FY)\\d{2}") |> as.integer(),
    Date = Date + 2000
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

<!-- ## Customs and Border Patrol -->

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a thorough set of reports on [court workload and adjudication statistics](Workload and Adjudication Statistics).
