---
title: "Report repository"
---

```{r}
library(tidyverse)
library(reactable)
library(tibble)

format_date <- function(date) {
  format(date, "%b. %Y")
}

options(reactable.theme = reactableTheme(
  backgroundColor = "#F4F6F7"
))
```

Our project's focus is on collecting and posting individual-level data, but this page is an exception: here, we collect and repost government reports that draw from the individual-level datasets we post. We hope that this centralized repository of reports (and links to government websites) will help users of the individual-level data.  The reports come from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Patrol (CBP), and the Executive Office of Immigration Review (EOIR). These reports are generally available for download from the government directly; we repost them for users' convenience. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the reports before we have, we link to their sites as the source.

## Customs and Border Patrol 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Southwest Land Border Encounters](https://www.cbp.gov/newsroom/stats/southwest-land-border-encounters)
: Dashboard tracking encounters along the southern border at and between ports of entry.

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Statistics covering many aspects of CBP's enforcement actions.

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
: Statistics tracking detention and outcomes after border encounters at and between ports of entry.

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a set of [court workload and adjudication statistics](Workload and Adjudication Statistics).




## Immigration and Customs Enforcement

### Annual report

ICE compiles a variety of descriptive statistics in its annual report.

```{r}
ice_annual_reports_files <- 
  tibble(
  Filename = c(
  "iceAnnualReportFY2021.pdf",
  "iceAnnualReportFY2022.pdf",
  "iceAnnualReportFY2023.pdf",
  "iceAnnualReportFY2024.pdf",
  "iceReportFY2020.pdf")
) |> 
  mutate(
    Date = str_extract(Filename, "\\d{4}") 
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>")
) |> 
  transmute(Date, Source, Download) 
```

```{r}
ice_annual_reports_files |> 
  slice(1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |> 
  slice(-1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

### Detention management spreadsheet

ICE releases a spreadsheet about twice a month that tracks book-ins, case types, detention facility information, and other descriptive statistics related to detention. 

#### Year-to-date:

```{r}
tibble(
  Filename = "https://www.dropbox.com/scl/fi/afrhtn32ven3r4pkzmvmt/FY25_detentionStats04162025.xlsx?rlkey=kuxbpcae0jdgamultzp0xai27&dl=1",
  Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"), 
  Date = format(as.Date("2025-04-16"), "%b. %d, %Y"),
  Download = glue::glue("<a href='{Filename}'>FY25_detentionStats04162025.xlsx</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
tribble(
  ~Filename, 
  "FY25_detentionStats01032025.xlsx",
  "FY25_detentionStats01162025.xlsx",
  "FY25_detentionStats02032025.xlsx",
  "FY25_detentionStats02142025.xlsx",
  "FY25_detentionStats02272025.xlsx",
  "FY25_detentionStats03052025.xlsx",
  "FY25_detentionStats03142025.xlsx",
  "FY25_detentionStats03262025.xlsx",
  "FY25_detentionStats04162025.xlsx",
  "FY25_detentionStats11212024.xlsx",
  "FY25_detentionStats12112024.xlsx",
  "FY25_detentionStats12122024.xlsx",
  "FY25_detentionStats12182024.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "\\d{8}(?=\\.xlsx)") |> mdy()
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
  Date = format(Date, "%b. %d, %Y"),
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

#### End-of-fiscal-year:

```{r}
tribble(
  ~Filename, 
  "FY24_detentionStats.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "(?<=FY)\\d{2}") |> as.integer(),
    Date = Date + 2000
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```
<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
tribble(
  ~Filename, 
    "FY19-detentionstats.xlsx",
  "FY20-detentionstats.xlsx",
  "FY21-detentionstats.xlsx",
  "FY22-detentionStats.xlsx",
  "FY23_detentionStats.xlsx"
) |> 
  mutate(
    Date = str_extract(Filename, "(?<=FY)\\d{2}") |> as.integer(),
    Date = Date + 2000
  ) |> 
    arrange(desc(Date)) |> 
    mutate(
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://www.ice.gov/detain/detention-management'>ICE</a>")
) |> 
  transmute(Date, Source, Download) |> 
  reactable::reactable(columns = list(
  Date = colDef(),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

<!-- ## Customs and Border Patrol -->



## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

Through January 2025, the Office of Homeland Security Statistics released a monthly spreadsheet tracking a variety of actions by both CBP and ICE. We do not know whether to expect future releases.

```{r}
enf_files <- 
tribble(
  ~Filename, 
  "2024_1108_ohss_immigration-enforcement-and-legal-processes-tables-july-2024.xlsx",
  "2024_1206_ohss_immigration-enforcement-and-legal-processes-tables-august-2024.xlsx",
  "2025_0116_ohss_immigration-enforcement-and-legal-processes-tables-november-2024.xlsx",
  "24_0105_ohss_immigration-enforcement-and-legal-processes-tables-september-2023_v2.xlsx",
  "24-0209_ohss_immigration-enforcement-and-legal-processes-tables-october-2023_v2.xlsx",
  "24-0308_ohss_immigration-enforcement-and-legal-processes-tables-november-2023_2.xlsx",
  "24-0405_ohss_immigration-enforcement-and-legal-processes-tables-december-2023.xlsx",
  "24-0510_ohss_immigration-enforcement-and-legal-processes-tables-january-2024.xlsx",
  "24-0607_ohss_immigration-enforcement-and-legal-processes-tables-february-2024.xlsx",
  "24-0705_ohss_immigration-enforcement-and-legal-processes-tables-march-2024.xlsx",
  "24-0809_ohss_immigration-enforcement-and-legal-processes-tables-april-2024.xlsx",
  "24-0906_ohss_immigration-enforcement-and-legal-processes-tables-may-2024_v2.xlsx",
  "24-1011_ohss_immigration-enforcement-and-legal-processes-tables-june-2024_2.xlsx"
) |> 
  mutate(
    raw = str_extract(Filename, "(?:\\d{4}|\\d{2})[-_]\\d{4}"),
    compact = str_remove_all(raw, "[-_]"),
    Date = if_else(
      nchar(compact) == 6,
      mdy(paste0(str_sub(compact, 3), str_sub(compact, 1, 2))),
      mdy(paste0(str_sub(compact, 5), str_sub(compact, 1, 4)))
    )
   ) |> 
    arrange(desc(Date)) |> 
    mutate(
  Date = format(Date, "%b. %Y"),
    Download = glue::glue("<a href='{Filename}'>{Filename}</a>"),
      Source = glue::glue("<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>")
) |> 
  transmute(Date, Source, Download)
```

```{r}
enf_files |> 
  slice(1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

<details>
<summary>Past reports</summary>

```{r}
enf_files |> 
  slice(-1) |> 
  reactable::reactable(columns = list(
  Date = colDef(align = "left"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
), pagination = FALSE)
```

</details>

