---
title: "Customs and Border Protection"
---

```{r}
library(reactable)
library(tidyverse)
library(htmltools)

# Load centralized dataset definitions
source("datasets.R")

col_defs <- list(
  Type = colDef(
    minWidth = 85,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Type of enforcement action",
        "Type"
      )
    }
  ),
  Start = colDef(
    minWidth = 75,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of first records in the dataset",
        "Start"
      )
    },
    cell = function(value) {
      if (is.null(value) || is.na(value)) {
        return("")
      }
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  End = colDef(
    minWidth = 75,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of last records in the dataset",
        "End"
      )
    },
    cell = function(value) {
      if (is.null(value) || is.na(value)) {
        return("")
      }
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  Records = colDef(
    minWidth = 45,
    align = "right",
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Number of records in the dataset",
        "Records"
      )
    }
  ),
  Source = colDef(
    minWidth = 45,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Organization that provided the data",
        "Source"
      )
    }
  ),
  Raw = colDef(
    minWidth = 40,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Download the raw, unprocessed data as provided by CBP",
        "Raw"
      )
    },
    cell = function(value) {
      if (is.null(value) || length(value) == 0) {
        return("&ndash;") # en dash
      }

      url <- as.character(value[[1]])
      ext <- tolower(trimws(as.character(value[[3]])))

      paste0(
        "<a href='",
        url,
        "'>",
        "<img src='/img/",
        ext,
        ".svg' width=25 height=25 alt='",
        ext,
        "'>",
        "</a>"
      )
    }
  )
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

CBP collects individual-level data on every person it arrests or expels at the border as well as on every person who arrives at a port of entry whom it deems inadmissible (most frequently asylum seekers). Border arrest data are collected by the Border Patrol; inadmissible arrivals data are collected by the Office of Field Operations. CBP maintains a detailed [FOIA library](https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room) with these datasets and others.


## Data for 2025

<div style="margin-top: 0.5em;"></div>

The most recent release of data is from June 2025 for apprehensions and August 2025 for people deemed inadmissible at the border. We are actively seeking more recent updates, including for encounters. 

```{r}
# Get CBP current datasets and prepare for display
get_datasets("CBP", "current") %>%
  prepare_cbp_for_display() %>%
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

::: {.callout-warning appearance="default"}

## Inconsistencies in inadmissibles data in 2025

CBP posted several datasets of people deemed inadmissible at the border, covering overlapping periods of FY 2025. The counts of the number of people deemed inadmissible by week differ substantially between releases. We are seeking clarification, and urge caution in using these data until the discrepancies are resolved.

:::


## Historical data archive

We post below historical data that CBP produced either in response to FOIA requests or proactively in its FOIA reading room. 

<details class="column-page-inset-right">

<summary>Show archive</summary>

```{r}
tibble::tribble(
  ~Type,
  ~Start,
  ~End,
  ~Records,
  ~Source,
  ~Raw,
  "Apprehensions",
  as.Date("2007-10-01"),
  as.Date("2008-09-30"),
  "724K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529466108",
    "45 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2008-10-01"),
  as.Date("2009-09-30"),
  "556K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524552711",
    "35 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2009-10-01"),
  as.Date("2010-09-30"),
  "463K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524452168",
    "35 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2010-10-01"),
  as.Date("2011-09-30"),
  "340K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537472516",
    "26 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2011-10-01"),
  as.Date("2012-09-30"),
  "365K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522219652",
    "31 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2012-10-01"),
  as.Date("2013-09-30"),
  "421K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522010833",
    "40 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2013-10-01"),
  as.Date("2014-03-31"),
  "215K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536497781",
    "24 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2014-10-01"),
  as.Date("2015-09-30"),
  "337K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523485219",
    "34 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2015-10-01"),
  as.Date("2016-03-31"),
  "189K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527949432",
    "20 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2016-04-01"),
  as.Date("2016-09-30"),
  "227K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536771304",
    "30 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2016-10-01"),
  as.Date("2017-09-30"),
  "311K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522642202",
    "34 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2017-10-01"),
  as.Date("2018-09-30"),
  "404K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536816904",
    "42 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2018-10-01"),
  as.Date("2019-03-31"),
  "365K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534563529",
    "38 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2019-04-01"),
  as.Date("2019-06-30"),
  "329K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539665388",
    "34 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2019-07-01"),
  as.Date("2019-09-30"),
  "165K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538377500",
    "17 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2019-10-01"),
  as.Date("2020-09-30"),
  "208K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836518613189",
    "23 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2020-10-01"),
  as.Date("2021-03-31"),
  "126K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532799369",
    "14 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2021-04-01"),
  as.Date("2021-06-30"),
  "200K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531099951",
    "21 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2021-07-01"),
  as.Date("2021-09-30"),
  "296K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535939039",
    "30 MB",
    "xlsx"
  ),
  "Apprehensions",
  as.Date("2021-10-01"),
  as.Date("2022-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527984953",
    "110 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2014-01-01"),
  as.Date("2014-12-31"),
  "557K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536350802",
    "61 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2015-01-01"),
  as.Date("2015-12-31"),
  "671K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517811895",
    "74 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2016-01-01"),
  as.Date("2016-12-31"),
  "829K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530605254",
    "91 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2017-01-01"),
  as.Date("2017-12-31"),
  "546K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529580929",
    "64 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2018-01-01"),
  as.Date("2018-12-31"),
  "673K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538742245",
    "77 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2019-01-01"),
  as.Date("2019-12-31"),
  "49K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519445234",
    "26 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2020-01-01"),
  as.Date("2020-12-31"),
  "391K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519054034",
    "44 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2020-04-01"),
  as.Date("2022-03-31"),
  "503K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517807065",
    "38 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2021-01-01"),
  as.Date("2021-12-31"),
  "602K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537280774",
    "68 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2022-01-01"),
  as.Date("2022-12-31"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527086921",
    "119 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2022-01-01"),
  as.Date("2022-12-31"),
  "281K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534928426",
    "31 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2022-04-01"),
  as.Date("2022-04-30"),
  "53K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522332574",
    "4 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2022-07-01"),
  as.Date("2023-02-28"),
  "525K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525107263",
    "38 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2022-07-01"),
  as.Date("2023-02-28"),
  "525K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529242001",
    "38 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-01-01"),
  as.Date("2023-12-31"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524171859",
    "119 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-01-01"),
  as.Date("2023-12-31"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526905068",
    "115 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-01-01"),
  as.Date("2023-12-31"),
  "775K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522164658",
    "85 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-05-01"),
  as.Date("2023-06-20"),
  "175K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524781374",
    "12 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-07-01"),
  as.Date("2023-07-31"),
  "110K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521186280",
    "8 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-07-01"),
  as.Date("2023-12-31"),
  "708K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525779953",
    "52 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2023-11-01"),
  as.Date("2024-08-01"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533367753",
    "76 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2024-01-01"),
  as.Date("2024-12-31"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530361246",
    "118 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2024-01-01"),
  as.Date("2024-12-31"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519236948",
    "115 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2024-01-01"),
  as.Date("2024-12-31"),
  "477K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536102266",
    "52 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2024-01-01"),
  as.Date("2024-06-30"),
  "692K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522055139",
    "51 MB",
    "xlsx"
  ),
  "Deemed inadmissible",
  as.Date("2024-10-01"),
  as.Date("2024-11-30"),
  "163K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533627763",
    "12 MB",
    "xlsx"
  ),
  "Title 42 expulsions",
  as.Date("2021-10-01"),
  as.Date("2022-09-30"),
  "738K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530089384",
    "74 MB",
    "xlsx"
  ),
  "Title 42 expulsions",
  as.Date("2019-10-01"),
  as.Date("2020-09-30"),
  "197K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519515324",
    "18 MB",
    "xlsx"
  ),
  "Title 42 expulsions",
  as.Date("2020-10-01"),
  as.Date("2021-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538878230",
    "98 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2024-07-01"),
  as.Date("2024-09-30"),
  "176K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522527618",
    "27 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2022-10-01"),
  as.Date("2022-12-31"),
  "640K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519013469",
    "95 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2023-01-01"),
  as.Date("2023-03-31"),
  "428K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523031829",
    "64 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2023-04-01"),
  as.Date("2023-06-30"),
  "458K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539840495",
    "68 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2023-07-01"),
  as.Date("2023-09-30"),
  "537K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528623980",
    "80 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2023-10-01"),
  as.Date("2023-12-31"),
  "634K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529574328",
    "95 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2024-01-01"),
  as.Date("2024-03-31"),
  "407K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538501297",
    "61 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2024-04-01"),
  as.Date("2024-06-30"),
  "340K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524426045",
    "51 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2012-10-01"),
  as.Date("2013-09-30"),
  "420K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1973649671540",
    "63 MB",
    "xlsx"
  ),
  "Encounters",
  as.Date("2017-10-01"),
  as.Date("2018-09-30"),
  "404K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1973646575195",
    "64 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("1999-10-01"),
  as.Date("2000-09-30"),
  "2M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526779834",
    "56 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2000-10-01"),
  as.Date("2001-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521865479",
    "44 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2001-10-01"),
  as.Date("2002-09-30"),
  "954K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536752416",
    "34 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2002-10-01"),
  as.Date("2003-09-30"),
  "932K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535002120",
    "34 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2003-10-01"),
  as.Date("2004-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523854174",
    "43 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2004-10-01"),
  as.Date("2005-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538413035",
    "43 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2005-10-01"),
  as.Date("2006-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525352489",
    "39 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2006-10-01"),
  as.Date("2007-09-30"),
  "877K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836520753674",
    "35 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2007-10-01"),
  as.Date("2008-09-30"),
  "724K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397984",
    "28 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2008-10-01"),
  as.Date("2009-09-30"),
  "556K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528500592",
    "22 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2009-10-01"),
  as.Date("2010-09-30"),
  "463K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537505751",
    "18 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2010-10-01"),
  as.Date("2011-09-30"),
  "340K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536574704",
    "14 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2011-10-01"),
  as.Date("2012-09-30"),
  "365K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523110035",
    "15 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2012-10-01"),
  as.Date("2013-09-30"),
  "421K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527799721",
    "17 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2013-10-01"),
  as.Date("2014-09-30"),
  "487K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529955831",
    "20 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2014-10-01"),
  as.Date("2015-09-30"),
  "337K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531582054",
    "14 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2015-10-01"),
  as.Date("2016-09-30"),
  "416K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397977",
    "20 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2016-10-01"),
  as.Date("2017-09-30"),
  "311K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525028767",
    "15 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2017-10-01"),
  as.Date("2018-09-30"),
  "404K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539329278",
    "20 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2018-10-01"),
  as.Date("2019-09-30"),
  "860K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526972753",
    "42 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2019-10-01"),
  as.Date("2020-09-30"),
  "208K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527670543",
    "10 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2020-10-01"),
  as.Date("2021-09-30"),
  "621K",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522751005",
    "30 MB",
    "xlsx"
  ),
  "Apprehensions with place of origin",
  as.Date("2021-10-01"),
  as.Date("2022-09-30"),
  "1M",
  "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529123179",
    "54 MB",
    "xlsx"
  )
) |>
  arrange(desc(End)) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>


```{js}
// Initialize Bootstrap tooltips
document.addEventListener('DOMContentLoaded', function() {
  var tooltipTriggerList = [].slice.call(document.querySelectorAll('[data-bs-toggle="tooltip"]'));
  var tooltipList = tooltipTriggerList.map(function (tooltipTriggerEl) {
    return new bootstrap.Tooltip(tooltipTriggerEl);
  });
});
```

