---
title: "Customs and Border Protection"
---

```{r}
library(reactable)
library(tidyverse)

col_defs <- list(
  Type = colDef(minWidth = 85),
  Start = colDef(
    minWidth = 75,
    cell = function(value) {
      if (is.null(value) || is.na(value)) return("")
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  End = colDef(
    minWidth = 75,
    cell = function(value) {
      if (is.null(value) || is.na(value)) return("")
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  Records = colDef(minWidth = 45, align = "right"),
  Source = colDef(minWidth = 45, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

CBP collects individual-level data on every person it arrests or expels at the border as well as on every person who arrives at a port of entry whom it deems inadmissible (most frequently asylum seekers). Border arrest data are collected by the Border Patrol; inadmissible arrivals data are collected by the Office of Field Operations. CBP maintains a detailed [FOIA library](https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room) with these datasets and others.


## Data for 2025

<div style="margin-top: 0.5em;"></div>

The most recent release of data is from May 2025 for apprehensions and June 2025 for people deemed inadmissible at the border. We are actively seeking more recent updates, including for encounters. 

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Records, ~Source, ~Download,
  "Apprehensions", "Apr. 1, 2025", "Apr. 30, 2025", "10K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905008519753'>xlsx</a> (2 MB)",
  "Apprehensions", "May. 1, 2025", "May. 31, 2025", "10K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1947452927480'>xlsx</a> (2 MB)",
  "Deemed inadmissible", "Oct. 1, 2024", "Mar. 19, 2025", "478K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842173428525'>xlsx</a>, part 1 (52 MB)",
  "Deemed inadmissible", "Oct. 1, 2024", "Mar. 19, 2025", "430K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842164368478'>xlsx</a>, part 2 (46 MB)",
  "Deemed inadmissible", "Mar. 1, 2025", "Mar. 31, 2025", "20K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905033897281'>xlsx</a> (2 MB)",
  "Deemed inadmissible", "Apr. 1, 2025", "Apr. 30, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1904995214241'>xlsx</a> (1 MB)",
  "Deemed inadmissible", "May. 1, 2025", "May. 31, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905002524123'>xlsx</a> (2 MB)",
  "Deemed inadmissible", "Jun. 1, 2025", "Jun. 30, 2025", "17K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1919506153967'>xlsx</a> (1 MB)",
  ) |>
    mutate(
    Start = as.Date(Start, format = "%b. %d, %Y"),
    End = as.Date(End, format = "%b. %d, %Y"),
  ) |> 
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

## Historical data archive

We post below historical data that CBP produced either in response to FOIA requests or proactively in its FOIA reading room. 

<details class="column-page-inset-right">

<summary>Show archive</summary>

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Records, ~Source, ~Download,
  "Apprehensions", "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529466108'>xlsx</a> (45 MB)",
  "Apprehensions", "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524552711'>xlsx</a> (35 MB)",
  "Apprehensions", "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524452168'>xlsx</a> (35 MB)",
  "Apprehensions", "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537472516'>xlsx</a> (26 MB)",
  "Apprehensions", "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522219652'>xlsx</a> (31 MB)",
  "Apprehensions", "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522010833'>xlsx</a> (40 MB)",
  "Apprehensions", "Oct. 1, 2013", "Mar. 31, 2014", "215K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536497781'>xlsx</a> (24 MB)",
  "Apprehensions", "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523485219'>xlsx</a> (34 MB)",
  "Apprehensions", "Oct. 1, 2015", "Mar. 31, 2016", "189K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527949432'>xlsx</a> (20 MB)",
  "Apprehensions", "Apr. 1, 2016", "Sep. 30, 2016", "227K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536771304'>xlsx</a> (30 MB)",
  "Apprehensions", "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522642202'>xlsx</a> (34 MB)",
  "Apprehensions", "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536816904'>xlsx</a> (42 MB)",
  "Apprehensions", "Oct. 1, 2018", "Mar. 31, 2019", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534563529'>xlsx</a> (38 MB)",
  "Apprehensions", "Apr. 1, 2019", "Jun. 30, 2019", "329K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539665388'>xlsx</a> (34 MB)",
  "Apprehensions", "Jul. 1, 2019", "Sep. 30, 2019", "165K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538377500'>xlsx</a> (17 MB)",
  "Apprehensions", "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836518613189'>xlsx</a> (23 MB)",
  "Apprehensions", "Oct. 1, 2020", "Mar. 31, 2021", "126K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532799369'>xlsx</a> (14 MB)",
  "Apprehensions", "Apr. 1, 2021", "Jun. 30, 2021", "200K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531099951'>xlsx</a> (21 MB)",
  "Apprehensions", "Jul. 1, 2021", "Sep. 30, 2021", "296K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535939039'>xlsx</a> (30 MB)",
  "Apprehensions", "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527984953'>xlsx</a> (110 MB)",
  "Deemed inadmissible", "Jan. 1, 2014", "Dec. 31, 2014", "557K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536350802'>xlsx</a> (61 MB)",
  "Deemed inadmissible", "Jan. 1, 2015", "Dec. 31, 2015", "671K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517811895'>xlsx</a> (74 MB)",
  "Deemed inadmissible", "Jan. 1, 2016", "Dec. 31, 2016", "829K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530605254'>xlsx</a> (91 MB)",
  "Deemed inadmissible", "Jan. 1, 2017", "Dec. 31, 2017", "546K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529580929'>xlsx</a> (64 MB)",
  "Deemed inadmissible", "Jan. 1, 2018", "Dec. 31, 2018", "673K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538742245'>xlsx</a> (77 MB)",
  "Deemed inadmissible", "Jan. 1, 2019", "Dec. 31, 2019", "49K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519445234'>xlsx</a> (26 MB)",
  "Deemed inadmissible", "Jan. 1, 2020", "Dec. 31, 2020", "391K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519054034'>xlsx</a> (44 MB)",
  "Deemed inadmissible", "Apr. 1, 2020", "Mar. 31, 2022", "503K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517807065'>xlsx</a> (38 MB)",
  "Deemed inadmissible", "Jan. 1, 2021", "Dec. 31, 2021", "602K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537280774'>xlsx</a> (68 MB)",
  "Deemed inadmissible", "Jan. 1, 2022", "Dec. 31, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527086921'>xlsx</a> (119 MB)",
  "Deemed inadmissible", "Jan. 1, 2022", "Dec. 31, 2022", "281K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534928426'>xlsx</a> (31 MB)",
  "Deemed inadmissible", "Apr. 1, 2022", "Apr. 30, 2022", "53K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522332574'>xlsx</a> (4 MB)",
  "Deemed inadmissible", "Jul. 1, 2022", "Feb. 28, 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525107263'>xlsx</a> (38 MB)",
  "Deemed inadmissible", "Jul. 1, 2022", "Feb. 28, 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529242001'>xlsx</a> (38 MB)",
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524171859'>xlsx</a> (119 MB)",
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526905068'>xlsx</a> (115 MB)",
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "775K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522164658'>xlsx</a> (85 MB)",
  "Deemed inadmissible", "May. 1, 2023", "Jun. 20, 2023", "175K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524781374'>xlsx</a> (12 MB)",
  "Deemed inadmissible", "Jul. 1, 2023", "Jul. 31, 2023", "110K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521186280'>xlsx</a> (8 MB)",
  "Deemed inadmissible", "Jul. 1, 2023", "Dec. 31, 2023", "708K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525779953'>xlsx</a> (52 MB)",
  "Deemed inadmissible", "Nov. 1, 2023", "Aug. 1, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533367753'>xlsx</a> (76 MB)",
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530361246'>xlsx</a> (118 MB)",
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519236948'>xlsx</a> (115 MB)",
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "477K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536102266'>xlsx</a> (52 MB)",
  "Deemed inadmissible", "Jan. 1, 2024", "Jun. 30, 2024", "692K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522055139'>xlsx</a> (51 MB)",
  "Deemed inadmissible", "Oct. 1, 2024", "Nov. 30, 2024", "163K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533627763'>xlsx</a> (12 MB)",
   "Title 42 expulsions", "Oct. 1, 2021", "Sep. 30, 2022", "738K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530089384'>xlsx</a> (74 MB)",
  "Title 42 expulsions", "Oct. 1, 2019", "Sep. 30, 2020", "197K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519515324'>xlsx</a> (18 MB)",
  "Title 42 expulsions", "Oct. 1, 2020", "Sep. 30, 2021", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538878230'>xlsx</a> (98 MB)",
  "Encounters", "Jul. 1, 2024", "Sep. 30, 2024", "176K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522527618'>xlsx</a> (27 MB)",
  "Encounters", "Oct. 1, 2022", "Dec. 31, 2022", "640K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519013469'>xlsx</a> (95 MB)",
  "Encounters", "Jan. 1, 2023", "Mar. 31, 2023", "428K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523031829'>xlsx</a> (64 MB)",
  "Encounters", "Apr. 1, 2023", "Jun. 30, 2023", "458K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539840495'>xlsx</a> (68 MB)",
  "Encounters", "Jul. 1, 2023", "Sep. 30, 2023", "537K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528623980'>xlsx</a> (80 MB)",
  "Encounters", "Oct. 1, 2023", "Dec. 31, 2023", "634K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529574328'>xlsx</a> (95 MB)",
  "Encounters", "Jan. 1, 2024", "Mar. 31, 2024", "407K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538501297'>xlsx</a> (61 MB)",
  "Encounters", "Apr. 1, 2024", "Jun. 30, 2024", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524426045'>xlsx</a> (51 MB)",
  "Apprehensions with place of origin", "Oct. 1, 1999", "Sep. 30, 2000", "2M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526779834'>xlsx</a> (56 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2000", "Sep. 30, 2001", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521865479'>xlsx</a> (44 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2001", "Sep. 30, 2002", "954K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536752416'>xlsx</a> (34 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2002", "Sep. 30, 2003", "932K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535002120'>xlsx</a> (34 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2003", "Sep. 30, 2004", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523854174'>xlsx</a> (43 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2004", "Sep. 30, 2005", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538413035'>xlsx</a> (43 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2005", "Sep. 30, 2006", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525352489'>xlsx</a> (39 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2006", "Sep. 30, 2007", "877K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836520753674'>xlsx</a> (35 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397984'>xlsx</a> (28 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528500592'>xlsx</a> (22 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537505751'>xlsx</a> (18 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536574704'>xlsx</a> (14 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523110035'>xlsx</a> (15 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527799721'>xlsx</a> (17 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2013", "Sep. 30, 2014", "487K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529955831'>xlsx</a> (20 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531582054'>xlsx</a> (14 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2015", "Sep. 30, 2016", "416K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397977'>xlsx</a> (20 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525028767'>xlsx</a> (15 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539329278'>xlsx</a> (20 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2018", "Sep. 30, 2019", "860K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526972753'>xlsx</a> (42 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527670543'>xlsx</a> (10 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2020", "Sep. 30, 2021", "621K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522751005'>xlsx</a> (30 MB)",
  "Apprehensions with place of origin", "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529123179'>xlsx</a> (54 MB)"
) |> 
  mutate(
    Start = as.Date(Start, format = "%b. %d, %Y"),
    End = as.Date(End, format = "%b. %d, %Y"),
  ) |> 
  arrange(desc(End)) |> 
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>
