---
title: "Customs and Border Protection"
---

```{r}
library(reactable)
library(tidyverse)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

col_defs_cbp <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  # Identifiers = colDef(
  #   minWidth = 65,
  #   cell = function(value) {
  #     icon <- if (is.na(value)) "xmark" else "check"
  #     color <- if (is.na(value)) "red" else "green"
  #     text <- if (is.na(value)) "" else value
  # 
  #     htmltools::tags$div(
  #       style = "display: flex; align-items: center; gap: 6px;",
  #       htmltools::tags$i(
  #         class = paste("fas", paste0("fa-", icon)),
  #         style = paste("color:", color, "; font-size: 1.2em;")
  #       ),
  #       text
  #     )
  #   }
  # ),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 55, html = TRUE),
  Download = colDef(minWidth = 75, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

CBP collects individual-level data on every person it arrests or expels at the border as well as on every person who arrives at a port of entry whom it deems inadmissible (most frequently asylum seekers). Border arrest data are collected by the Border Patrol; inadmissible arrivals data are collected by the Office of Field Operations. CBP maintains a detailed [FOIA library](https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room) with these datasets and others.


## Latest data

<div style="margin-top: 0.5em;"></div>

The most recent release of data is from April 2025 for apprehensions, June 2025 for people deemed inadmissible at the border, and September 2024 for encounters. We are actively seeking more recent updates.

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Records, ~Source, ~Download,
  "Apprehensions", "May. 1, 2025", "May. 31, 2025", "10K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1947452927480'>xlsx</a> (2 MB)",
  "Apprehensions", "Apr. 1, 2024", "Jun. 30, 2024", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1952962832425'>xlsx</a> (55 MB)",
  "Deemed inadmissible", "Jun. 1, 2025", "Jun. 30, 2025", "17K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1919506153967'>xlsx</a> (1 MB)",
  "Encounters", "Jul. 1, 2024", "Sep. 30, 2024", "176K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522527618'>xlsx</a> (27 MB)"
  ) |>
  reactable::reactable(columns = c(col_defs_cbp, list(Type = colDef(minWidth = 75))), pagination = FALSE)
```

## Historical data archive

We post below historical data that CBP produced either in response to FOIA requests or proactively in its FOIA reading room. 

<details class="column-page-inset-right">

<summary>Show archive</summary>

```{r}
tibble::tribble(
                                 ~Type,       ~Start,         ~End, ~Records,                                                                                              ~Source,     ~Download,
                       "Apprehensions", "2025-05-01", "2025-05-01",    "10K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1947452927480,
                       "Apprehensions", "2007-10-01", "2007-10-01",   "724K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529466108,
                       "Apprehensions", "2008-10-01", "2008-10-01",   "556K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836524552711,
                       "Apprehensions", "2009-10-01", "2009-10-01",   "463K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836524452168,
                       "Apprehensions", "2010-10-01", "2010-10-01",   "340K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836537472516,
                       "Apprehensions", "2011-10-01", "2011-10-01",   "365K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522219652,
                       "Apprehensions", "2012-10-01", "2012-10-01",   "421K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522010833,
                       "Apprehensions", "2013-10-01", "2013-10-01",   "215K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536497781,
                       "Apprehensions", "2014-10-01", "2014-10-01",   "337K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836523485219,
                       "Apprehensions", "2015-10-01", "2015-10-01",   "189K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836527949432,
                       "Apprehensions", "2016-04-01", "2016-04-01",   "227K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536771304,
                       "Apprehensions", "2016-10-01", "2016-10-01",   "311K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522642202,
                       "Apprehensions", "2017-10-01", "2017-10-01",   "404K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536816904,
                       "Apprehensions", "2018-10-01", "2018-10-01",   "365K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836534563529,
                       "Apprehensions", "2019-04-01", "2019-04-01",   "329K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836539665388,
                       "Apprehensions", "2019-07-01", "2019-07-01",   "165K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836538377500,
                       "Apprehensions", "2019-10-01", "2019-10-01",   "208K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836518613189,
                       "Apprehensions", "2020-10-01", "2020-10-01",   "126K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836532799369,
                       "Apprehensions", "2021-04-01", "2021-04-01",   "200K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836531099951,
                       "Apprehensions", "2021-07-01", "2021-07-01",   "296K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836535939039,
                       "Apprehensions", "2021-10-01", "2021-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836527984953,
                       "Apprehensions", "2025-04-01", "2025-04-01",    "10K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1905008519753,
                 "Deemed inadmissible", "2025-06-01", "2025-06-01",    "17K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1919506153967,
                 "Deemed inadmissible", "2014-01-01", "2014-01-01",   "557K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536350802,
                 "Deemed inadmissible", "2015-01-01", "2015-01-01",   "671K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836517811895,
                 "Deemed inadmissible", "2016-01-01", "2016-01-01",   "829K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836530605254,
                 "Deemed inadmissible", "2017-01-01", "2017-01-01",   "546K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529580929,
                 "Deemed inadmissible", "2018-01-01", "2018-01-01",   "673K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836538742245,
                 "Deemed inadmissible", "2019-01-01", "2019-01-01",    "49K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836519445234,
                 "Deemed inadmissible", "2020-01-01", "2020-01-01",   "391K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836519054034,
                 "Deemed inadmissible",           NA,           NA,   "503K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836517807065,
                 "Deemed inadmissible", "2021-01-01", "2021-01-01",   "602K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836537280774,
                 "Deemed inadmissible", "2022-01-01", "2022-01-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836527086921,
                 "Deemed inadmissible", "2022-01-01", "2022-01-01",   "281K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836534928426,
                 "Deemed inadmissible",           NA,           NA,    "53K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522332574,
                 "Deemed inadmissible",           NA,           NA,   "525K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836525107263,
                 "Deemed inadmissible",           NA,           NA,   "525K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529242001,
                 "Deemed inadmissible", "2023-01-01", "2023-01-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836524171859,
                 "Deemed inadmissible", "2023-01-01", "2023-01-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836526905068,
                 "Deemed inadmissible", "2023-01-01", "2023-01-01",   "775K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522164658,
                 "Deemed inadmissible",           NA,           NA,   "175K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836524781374,
                 "Deemed inadmissible",           NA,           NA,   "110K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836521186280,
                 "Deemed inadmissible", "2023-07-01", "2023-07-01",   "708K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836525779953,
                 "Deemed inadmissible", "2023-11-01", "2023-11-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836533367753,
                 "Deemed inadmissible", "2024-01-01", "2024-01-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836530361246,
                 "Deemed inadmissible", "2024-01-01", "2024-01-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836519236948,
                 "Deemed inadmissible", "2024-01-01", "2024-01-01",   "477K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536102266,
                 "Deemed inadmissible", "2024-01-01", "2024-01-01",   "692K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522055139,
                 "Deemed inadmissible", "2024-10-01", "2024-10-01",   "163K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836533627763,
                 "Deemed inadmissible", "2024-10-01", "2024-10-01",   "478K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1842173428525,
                 "Deemed inadmissible", "2024-10-01", "2024-10-01",   "430K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1842164368478,
                 "Deemed inadmissible", "2025-03-01", "2025-03-01",    "20K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1905033897281,
                 "Deemed inadmissible", "2025-04-01", "2025-04-01",    "18K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1904995214241,
                 "Deemed inadmissible",           NA,           NA,    "18K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1905002524123,
                 "Title 42 expulsions", "2021-10-01", "2021-10-01",   "738K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836530089384,
                 "Title 42 expulsions", "2019-10-01", "2019-10-01",   "197K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836519515324,
                 "Title 42 expulsions", "2020-10-01", "2020-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836538878230,
                          "Encounters", "2024-07-01", "2024-07-01",   "176K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522527618,
                          "Encounters", "2022-10-01", "2022-10-01",   "640K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836519013469,
                          "Encounters", "2023-01-01", "2023-01-01",   "428K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836523031829,
                          "Encounters", "2023-04-01", "2023-04-01",   "458K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836539840495,
                          "Encounters", "2023-07-01", "2023-07-01",   "537K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836528623980,
                          "Encounters", "2023-10-01", "2023-10-01",   "634K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529574328,
                          "Encounters", "2024-01-01", "2024-01-01",   "407K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836538501297,
                          "Encounters", "2024-04-01", "2024-04-01",   "340K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836524426045,
  "Apprehensions with place of origin", "2021-10-01", "2021-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529123179,
  "Apprehensions with place of origin", "1999-10-01", "1999-10-01",     "2M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836526779834,
  "Apprehensions with place of origin", "2000-10-01", "2000-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836521865479,
  "Apprehensions with place of origin", "2001-10-01", "2001-10-01",   "954K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536752416,
  "Apprehensions with place of origin", "2002-10-01", "2002-10-01",   "932K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836535002120,
  "Apprehensions with place of origin", "2003-10-01", "2003-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836523854174,
  "Apprehensions with place of origin", "2004-10-01", "2004-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836538413035,
  "Apprehensions with place of origin", "2005-10-01", "2005-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836525352489,
  "Apprehensions with place of origin", "2006-10-01", "2006-10-01",   "877K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836520753674,
  "Apprehensions with place of origin", "2007-10-01", "2007-10-01",   "724K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836537397984,
  "Apprehensions with place of origin", "2008-10-01", "2008-10-01",   "556K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836528500592,
  "Apprehensions with place of origin", "2009-10-01", "2009-10-01",   "463K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836537505751,
  "Apprehensions with place of origin", "2010-10-01", "2010-10-01",   "340K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836536574704,
  "Apprehensions with place of origin", "2011-10-01", "2011-10-01",   "365K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836523110035,
  "Apprehensions with place of origin", "2012-10-01", "2012-10-01",   "421K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836527799721,
  "Apprehensions with place of origin", "2013-10-01", "2013-10-01",   "487K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529955831,
  "Apprehensions with place of origin", "2014-10-01", "2014-10-01",   "337K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836531582054,
  "Apprehensions with place of origin", "2015-10-01", "2015-10-01",   "416K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836537397977,
  "Apprehensions with place of origin", "2016-10-01", "2016-10-01",   "311K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836525028767,
  "Apprehensions with place of origin", "2017-10-01", "2017-10-01",   "404K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836539329278,
  "Apprehensions with place of origin", "2018-10-01", "2018-10-01",   "860K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836526972753,
  "Apprehensions with place of origin", "2019-10-01", "2019-10-01",   "208K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836527670543,
  "Apprehensions with place of origin", "2020-10-01", "2020-10-01",   "621K",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836522751005,
  "Apprehensions with place of origin", "2021-10-01", "2021-10-01",     "1M",   "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", 1836529123179
  ) |>
  mutate(
    Start = format(as.Date(Start), "%b. %d, %Y"),
    End = format(as.Date(End), "%b. %d, %Y"),
    Download = paste0("<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_", Download, "'>xlsx</a>")
  ) |>
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>
