---
title: "Customs and Border Protection"
---

```{r}
library(reactable)
library(tidyverse)
library(htmltools)

col_defs <- list(
  Type = colDef(
    minWidth = 85,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Type of enforcement action",
        "Type"
      )
    }
  ),
  Start = colDef(
    minWidth = 75,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of first records in the dataset",
        "Start"
      )
    },
    cell = function(value) {
      if (is.null(value) || is.na(value)) return("")
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  End = colDef(
    minWidth = 75,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Date of last records in the dataset",
        "End"
      )
    },
    cell = function(value) {
      if (is.null(value) || is.na(value)) return("")
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  Records = colDef(
    minWidth = 45,
    align = "right",
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Number of records in the dataset",
        "Records"
      )
    }
  ),
  Source = colDef(
    minWidth = 45,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Organization that provided the data",
        "Source"
      )
    }
  ),
  Raw = colDef(
    minWidth = 40,
    html = TRUE,
    header = function(value) {
      htmltools::tags$span(
        `data-bs-toggle` = "tooltip",
        `data-bs-placement` = "top",
        title = "Download the raw, unprocessed data as provided by CBP",
        "Raw"
      )
    },
    cell = function(value) {
      if (is.null(value) || length(value) == 0) {
        return("&ndash;") # en dash
      }

      url <- as.character(value[[1]])
      ext <- tolower(trimws(as.character(value[[3]])))

      paste0(
        "<a href='",
        url,
        "'>",
        "<img src='/img/",
        ext,
        ".svg' width=25 height=25 alt='",
        ext,
        "'>",
        "</a>"
      )
    }
  )
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

CBP collects individual-level data on every person it arrests or expels at the border as well as on every person who arrives at a port of entry whom it deems inadmissible (most frequently asylum seekers). Border arrest data are collected by the Border Patrol; inadmissible arrivals data are collected by the Office of Field Operations. CBP maintains a detailed [FOIA library](https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room) with these datasets and others.


## Data for 2025

<div style="margin-top: 0.5em;"></div>

The most recent release of data is from June 2025 for apprehensions and August 2025 for people deemed inadmissible at the border. We are actively seeking more recent updates, including for encounters. 

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Records, ~Source, ~Raw,
  "Apprehensions", "Apr. 1, 2024", "Jun. 30, 2024", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1952962832425", "55 MB", "xlsx"),
  "Apprehensions", "Dec. 1, 2024", "Mar. 31, 2025", "96K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1967490095971", "16 MB", "xlsx"),
  "Apprehensions", "Apr. 1, 2025", "Apr. 30, 2025", "10K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905008519753", "2 MB", "xlsx"),
  "Apprehensions", "May. 1, 2025", "May. 31, 2025", "10K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1947452927480", "2 MB", "xlsx"),
  "Apprehensions", "Jun. 1, 2025", "Jun. 30, 2025", "8K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1981826641425", "5 MB", "xlsx"),
  "Deemed inadmissible", "Oct. 1, 2024", "Mar. 19, 2025", "478K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842173428525", "52 MB", "xlsx"),
  "Deemed inadmissible", "Oct. 1, 2024", "Mar. 19, 2025", "430K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1842164368478", "46 MB", "xlsx"),
  "Deemed inadmissible", "Mar. 1, 2025", "Mar. 31, 2025", "20K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905033897281", "2 MB", "xlsx"),
  "Deemed inadmissible", "Apr. 1, 2025", "Apr. 30, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1904995214241", "1 MB", "xlsx"),
  "Deemed inadmissible", "May. 1, 2025", "May. 31, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1905002524123", "2 MB", "xlsx"),
  "Deemed inadmissible", "Jun. 1, 2025", "Jun. 30, 2025", "17K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1919506153967", "1 MB", "xlsx"),
  "Deemed inadmissible", "Jul. 1, 2025", "Jul. 31, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1962793389174", "1 MB", "xlsx"),
  "Deemed inadmissible", "Aug. 1, 2025", "Aug. 31, 2025", "18K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1981871111017", "1 MB", "xlsx")
  ) |>
    mutate(
    Start = as.Date(Start, format = "%b. %d, %Y"),
    End = as.Date(End, format = "%b. %d, %Y"),
  ) |> 
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

## Historical data archive

We post below historical data that CBP produced either in response to FOIA requests or proactively in its FOIA reading room. 

<details class="column-page-inset-right">

<summary>Show archive</summary>

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Records, ~Source, ~Raw,
  "Apprehensions", "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529466108", "45 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524552711", "35 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524452168", "35 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537472516", "26 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522219652", "31 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522010833", "40 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2013", "Mar. 31, 2014", "215K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536497781", "24 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523485219", "34 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2015", "Mar. 31, 2016", "189K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527949432", "20 MB", "xlsx"),
  "Apprehensions", "Apr. 1, 2016", "Sep. 30, 2016", "227K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536771304", "30 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522642202", "34 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536816904", "42 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2018", "Mar. 31, 2019", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534563529", "38 MB", "xlsx"),
  "Apprehensions", "Apr. 1, 2019", "Jun. 30, 2019", "329K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539665388", "34 MB", "xlsx"),
  "Apprehensions", "Jul. 1, 2019", "Sep. 30, 2019", "165K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538377500", "17 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836518613189", "23 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2020", "Mar. 31, 2021", "126K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532799369", "14 MB", "xlsx"),
  "Apprehensions", "Apr. 1, 2021", "Jun. 30, 2021", "200K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531099951", "21 MB", "xlsx"),
  "Apprehensions", "Jul. 1, 2021", "Sep. 30, 2021", "296K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535939039", "30 MB", "xlsx"),
  "Apprehensions", "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527984953", "110 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2014", "Dec. 31, 2014", "557K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536350802", "61 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2015", "Dec. 31, 2015", "671K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517811895", "74 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2016", "Dec. 31, 2016", "829K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530605254", "91 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2017", "Dec. 31, 2017", "546K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529580929", "64 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2018", "Dec. 31, 2018", "673K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538742245", "77 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2019", "Dec. 31, 2019", "49K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519445234", "26 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2020", "Dec. 31, 2020", "391K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519054034", "44 MB", "xlsx"),
  "Deemed inadmissible", "Apr. 1, 2020", "Mar. 31, 2022", "503K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836517807065", "38 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2021", "Dec. 31, 2021", "602K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537280774", "68 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2022", "Dec. 31, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527086921", "119 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2022", "Dec. 31, 2022", "281K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534928426", "31 MB", "xlsx"),
  "Deemed inadmissible", "Apr. 1, 2022", "Apr. 30, 2022", "53K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522332574", "4 MB", "xlsx"),
  "Deemed inadmissible", "Jul. 1, 2022", "Feb. 28, 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525107263", "38 MB", "xlsx"),
  "Deemed inadmissible", "Jul. 1, 2022", "Feb. 28, 2023", "525K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529242001", "38 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524171859", "119 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526905068", "115 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2023", "Dec. 31, 2023", "775K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522164658", "85 MB", "xlsx"),
  "Deemed inadmissible", "May. 1, 2023", "Jun. 20, 2023", "175K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524781374", "12 MB", "xlsx"),
  "Deemed inadmissible", "Jul. 1, 2023", "Jul. 31, 2023", "110K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521186280", "8 MB", "xlsx"),
  "Deemed inadmissible", "Jul. 1, 2023", "Dec. 31, 2023", "708K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525779953", "52 MB", "xlsx"),
  "Deemed inadmissible", "Nov. 1, 2023", "Aug. 1, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533367753", "76 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530361246", "118 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519236948", "115 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2024", "Dec. 31, 2024", "477K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536102266", "52 MB", "xlsx"),
  "Deemed inadmissible", "Jan. 1, 2024", "Jun. 30, 2024", "692K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522055139", "51 MB", "xlsx"),
  "Deemed inadmissible", "Oct. 1, 2024", "Nov. 30, 2024", "163K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836533627763", "12 MB", "xlsx"),
   "Title 42 expulsions", "Oct. 1, 2021", "Sep. 30, 2022", "738K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530089384", "74 MB", "xlsx"),
  "Title 42 expulsions", "Oct. 1, 2019", "Sep. 30, 2020", "197K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519515324", "18 MB", "xlsx"),
  "Title 42 expulsions", "Oct. 1, 2020", "Sep. 30, 2021", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538878230", "98 MB", "xlsx"),
  "Encounters", "Jul. 1, 2024", "Sep. 30, 2024", "176K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522527618", "27 MB", "xlsx"),
  "Encounters", "Oct. 1, 2022", "Dec. 31, 2022", "640K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836519013469", "95 MB", "xlsx"),
  "Encounters", "Jan. 1, 2023", "Mar. 31, 2023", "428K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523031829", "64 MB", "xlsx"),
  "Encounters", "Apr. 1, 2023", "Jun. 30, 2023", "458K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539840495", "68 MB", "xlsx"),
  "Encounters", "Jul. 1, 2023", "Sep. 30, 2023", "537K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528623980", "80 MB", "xlsx"),
  "Encounters", "Oct. 1, 2023", "Dec. 31, 2023", "634K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529574328", "95 MB", "xlsx"),
  "Encounters", "Jan. 1, 2024", "Mar. 31, 2024", "407K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538501297", "61 MB", "xlsx"),
  "Encounters", "Apr. 1, 2024", "Jun. 30, 2024", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524426045", "51 MB", "xlsx"),
  "Encounters", "Oct. 1, 2012", "Sep. 30, 2013", "420K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1973649671540", "63 MB", "xlsx"),
  "Encounters", "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1973646575195", "64 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 1999", "Sep. 30, 2000", "2M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526779834", "56 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2000", "Sep. 30, 2001", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521865479", "44 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2001", "Sep. 30, 2002", "954K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536752416", "34 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2002", "Sep. 30, 2003", "932K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535002120", "34 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2003", "Sep. 30, 2004", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523854174", "43 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2004", "Sep. 30, 2005", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538413035", "43 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2005", "Sep. 30, 2006", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525352489", "39 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2006", "Sep. 30, 2007", "877K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836520753674", "35 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2007", "Sep. 30, 2008", "724K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397984", "28 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2008", "Sep. 30, 2009", "556K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836528500592", "22 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2009", "Sep. 30, 2010", "463K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537505751", "18 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2010", "Sep. 30, 2011", "340K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536574704", "14 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2011", "Sep. 30, 2012", "365K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836523110035", "15 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2012", "Sep. 30, 2013", "421K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527799721", "17 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2013", "Sep. 30, 2014", "487K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529955831", "20 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2014", "Sep. 30, 2015", "337K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836531582054", "14 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2015", "Sep. 30, 2016", "416K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537397977", "20 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2016", "Sep. 30, 2017", "311K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836525028767", "15 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2017", "Sep. 30, 2018", "404K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539329278", "20 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2018", "Sep. 30, 2019", "860K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836526972753", "42 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2019", "Sep. 30, 2020", "208K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836527670543", "10 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2020", "Sep. 30, 2021", "621K", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522751005", "30 MB", "xlsx"),
  "Apprehensions with place of origin", "Oct. 1, 2021", "Sep. 30, 2022", "1M", "<a href='https://www.cbp.gov/newsroom/accountability-and-transparency/foia-reading-room'>CBP</a>", list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836529123179", "54 MB", "xlsx")
) |> 
  mutate(
    Start = as.Date(Start, format = "%b. %d, %Y"),
    End = as.Date(End, format = "%b. %d, %Y"),
  ) |> 
  arrange(desc(End)) |> 
  reactable::reactable(columns = col_defs, pagination = FALSE)
```

</details>


```{js}
// Initialize Bootstrap tooltips
document.addEventListener('DOMContentLoaded', function() {
  var tooltipTriggerList = [].slice.call(document.querySelectorAll('[data-bs-toggle="tooltip"]'));
  var tooltipList = tooltipTriggerList.map(function (tooltipTriggerEl) {
    return new bootstrap.Tooltip(tooltipTriggerEl);
  });
});
```
