---
title: "Immigration and Customs Enforcement"
---

```{r}
library(reactable)
library(tidyverse)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

col_defs_ice <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Identifiers = colDef(
    align = "left",
    minWidth = 50,
    html = TRUE,
    cell = function(value) {
      if (is.na(value)) {
        return(as.character(
          htmltools::tags$div(
            style = "display: flex; align-items: left;",
            htmltools::tags$i(
              class = "fas fa-xmark",
              style = "color: red; font-size: 1.2em;"
            )
          )
        ))
      }
  
      val <- trimws(value)
  
      if (val == "--") {
        return("&ndash;")  # en dash
      }
  
      as.character(
        htmltools::tags$div(
          style = "display: flex; align-items: left",
          htmltools::tags$i(
            class = "fas fa-check",
            style = "color: green; font-size: 1.2em;"
          )
        )
      )
    }
  ),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 55, html = TRUE),
  Download = colDef(minWidth = 75, html = TRUE)
)

col_defs_ice_cleaned <- 
  c(col_defs_ice[-length(col_defs_ice)], 
    list(
      Raw = colDef(
        minWidth = 50,
        html = TRUE,
        cell = function(value) {
          if (is.null(value) || length(value) == 0) {
            return("&ndash;")  # en dash
          }

          paste0(
            # "<a href='", value[1], "'>",
            "<img src='/img/", value[3], ".svg' width=25 height=25 alt='", value[3], "'>"
            # "</a>"
          )
        }
      ),
      Processed = colDef(
        # name = "Cleaned",
        minWidth = 100,
        html = TRUE,
        cell = function(value) {
          if (is.null(value) || length(value) == 0 || is.na(value[[1]][[1]])) {
            return("&ndash;")  # en dash
          }

          links <- map(value, ~ {
            paste0(
              "<a href='", .x[[1]], "'>",
              "<img src='/img/", .x[[3]], ".svg' width=25 height=25 alt='", .x[[3]], "'>",
              "</a>"
            )
          })

          paste(links, collapse = " ")
        }
      )
    )
  )

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

ICE collects data on every person it encounters, arrests, detains, transports via flight, and deports. 

We post below data that ICE produced in response to several FOIA requests by multiple organizations. Crucially, in some data releases, there are linked identifiers across data types such as arrests and detainers, allowing merges that enable tracing immigrants' pathways (anonymously) through the immigration enforcement pipeline. The identifiers are, unfortunately, different across releases, only enabling merging within a data release. See [below](#sec-about) for a description of each release.

::: {.callout-tip appearance="default"}

## Getting started with ICE data

Our [ICE frequently asked data questions](/docs/ice.html#sec-faq) is a good place to start before analyzing the data. We also provide a [codebook](/docs/ice.html#sec-codebook) describes each data table and the fields within them.

:::

## Latest data release

The most recent release of data covers ICE enforcement actions through late June 2025. We are actively seeking ongoing updates.

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  # edit all these to have the new info
  "Arrests", "Sep. 2023", "Late Jun. 2025", "Jul. 2025", "265K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1922082018423'>xlsx</a> (39 MB)",
  "Detainers", "Sep. 2023", "Late Jun. 2025", "Jul. 2025", "316K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1922081034353'>xlsx</a> (100 MB)",
  "Detentions", "Sep. 2023", "Late Jun. 2025", "Jul. 2025", "1.23M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1922078517539'>xlsx</a> (255 MB)", 
  "Encounters", "Sep. 2023", "Late Jun. 2025", "Jul. 2025", "1.28M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1922075106849'>xlsx</a> (179 MB)",
  "Removals", "Jan. 2025", "Late Jun. 2025", "Jul. 2025", "144K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/03884yy0d04c74vi63fs1htzel2zfj1u.xlsx'>xlsx</a> (31 MB)"
) |>
  reactable::reactable(columns = c(col_defs_ice, list(Type = colDef(minWidth = 65))), pagination = FALSE)
```

<!-- edit the link below with a Box link to a ZIP file you create with all the new release files -->

[Download the complete latest release as a ZIP file](https://ucla.box.com/shared/static/f9ish3m738cnke6xo1f4h7xnsc1b17x0.zip) (592 MB)

::: {.callout-warning appearance="simple"}

The removals dataset in this latest release (late June) includes significantly more records, for the same date range, than the removals dataset in the previous release (early June). **We therefore urge users not to rely on the previous, early June release of the removals table, and to exercise extreme caution in using the removals table at all.** In both releases, removals from FY2024 are far below the number reported by ICE's annual report, and we therefore have doubts about the reliability of the removals table. The problems appear to be less extreme in 2025, and we have posted the table starting in January 2025, but we remain concerned that the table may not include all relevant records, and that associated fields in the other tables, such as the departure date, may also create an incomplete picture of removals. These concerns lead us to advise caution when performing any analysis of removals. If you have insight into these problems or find other concerns, please let us know. We are actively seeking updated and corrected data.

:::

## Historical data 2012-2023

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Raw, ~Processed,
  # edit all these to have the new info
  # arrests
  "Arrests", "Oct. 1, 2011", "Sep. 30, 2023", "Nov. 2023", "912K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", 
  list("https://ucla.box.com/shared/static/xslezyadivfi27xar08ht1l35lbvuq8e.xlsx", "38MB", "xlsx"), # raw
  list( # processed
    list("https://ucla.box.com/shared/static/xslezyadivfi27xar08ht1l35lbvuq8e.xlsx", "38MB", "xlsx"),
    list("https://ucla.box.com/shared/static/fuyyppc4e5n4kzv120h5ed5bh5tn3gq8.dta", "144MB", "dta"),
    list("https://ucla.box.com/shared/static/tei14gumwoid9jt6sslk5zaeh6tfsk7q.sav", "119MB", "sav"),
    list("https://ucla.box.com/shared/static/1zv9nrvz3hixbzv95uwm2rfda299zzpt.feather", "37MB", "feather")
  ),
) |>
  reactable::reactable(columns = c(col_defs_ice_cleaned, list(Type = colDef(minWidth = 65))), pagination = FALSE)
```

## Data archive

```{r}
tibble::tribble(
~Type, ~Description, ~Start, ~End, ~Records, ~Release, ~URL,
"Arrests", "", "9/1/23", "3/20/25", 145802, "32025", 1836554372496,
"Arrests", "", "9/1/23", "6/20/25", 249280, "62025", 1903641913782,
"Arrests", "", "10/1/15", "9/30/16", 107300, "2022-ICFO-22955", 1851836294057,
"Arrests", "", "10/1/16", "9/30/17", 138876, "2022-ICFO-22955", 1851833536271,
"Arrests", "", "10/1/17", "9/30/18", 153214, "2022-ICFO-22955", 1851837546731,
"Arrests", "", "10/1/18", "9/30/19", 138775, "2022-ICFO-22955", 1851831800585,
"Arrests", "", "10/1/19", "9/30/20", 100429, "2022-ICFO-22955", 1851835191968,
"Arrests", "", "10/1/20", "9/30/21", 72849, "2022-ICFO-22955", 1851833034596,
"Arrests", "", "10/1/21", "9/30/22", 142954, "2022-ICFO-22955", 1851830686826,
"Arrests", "", "10/1/22", "9/30/23", 170864, "2022-ICFO-22955", 1851836416108,
"Arrests", "", "10/1/23", "9/30/24", 95188, "2022-ICFO-22955", 1851836311169,
"Arrests", "", "10/1/11", "9/30/12", 681578, "uwchr", 1836557464054,
"Arrests", "", "10/1/14", "9/30/15", 1059656, "uwchr", 1836540105544,
"Arts", "Flights", "10/1/10", "9/30/11", 2160, "uwchr", 1836540049661,
"Arts", "Flights", "10/1/11", "9/30/12", 2399, "uwchr", 1836552599950,
"Arts", "Flights", "10/1/12", "9/30/13", 2333, "uwchr", 1836549849021,
"Arts", "Flights", "10/1/13", "9/30/14", 5756, "uwchr", 1836540958981,
"Arts", "Flights", "10/1/14", "9/30/15", 1663, "uwchr", 1836538695921,
"Arts", "Flights", "10/1/15", "9/30/16", 1884, "uwchr", 1836536493019,
"Arts", "Flights", "10/1/16", "9/30/17", 1658, "uwchr", 1836549806043,
"Arts", "Flights", "10/1/17", "9/30/18", 1703, "uwchr", 1836550883008,
"Arts", "Flights", "10/1/18", "9/30/19", 1122, "uwchr", 1836537162853,
"Arts", "Passengers", "10/1/10", "9/30/11", 233061, "uwchr", 1836536399014,
"Arts", "Passengers", "10/1/11", "9/30/12", 282178, "uwchr", 1836538136812,
"Arts", "Passengers", "10/1/12", "9/30/13", 263621, "uwchr", 1836555001702,
"Arts", "Passengers", "10/1/13", "9/30/14", 249563, "uwchr", 1836545751933,
"Arts", "Passengers", "10/1/14", "9/30/15", 157067, "uwchr", 1836539073027,
"Arts", "Passengers", "10/1/15", "9/30/16", 168239, "uwchr", 1836549772221,
"Arts", "Passengers", "10/1/16", "9/30/17", 180384, "uwchr", 1836541672269,
"Arts", "Passengers", "10/1/17", "9/30/18", 191648, "uwchr", 1836553076817,
"Arts", "Passengers", "10/1/18", "9/30/19", 37259, "uwchr", 1836536207751,
"Arts", "Passengers", "10/1/18", "5/8/20", 3182, "uwchr", 1836545668509,
"Arts", "Passengers", "10/1/18", "5/8/20", 341290, "uwchr", 1836550007406,
"Detainers", "", "9/1/23", "3/20/25", 199335, "32025", 1836552782163,
"Detainers", "", "9/1/23", "6/20/25", 305738, "62025", 1903648700489,
"Detainers", "", "10/1/09", "9/30/10", 290253, "npr", 1836555210688,
"Detainers", "", "10/1/10", "9/30/11", 317327, "npr", 1836552467952,
"Detainers", "", "10/1/11", "9/30/12", 286507, "npr", 1836540940171,
"Detainers", "", "10/1/12", "9/30/13", 216717, "npr", 1836550482581,
"Detainers", "", "10/1/13", "9/30/14", 164188, "npr", 1836551310786,
"Detainers", "", "10/1/14", "9/30/15", 97021, "npr", 1836547271446,
"Detainers", "", "10/1/15", "9/30/16", 85561, "npr", 1836555104717,
"Detainers", "", "10/1/16", "9/30/17", 94013, "npr", 1836554262318,
"Detainers", "", "10/1/08", "9/30/09", 248255, "npr", 1836543616508,
"Detainers", "", "10/1/07", "9/30/08", 212407, "npr", 1836553974742,
"Detainers", "", "10/1/08", "9/30/09", 248272, "npr", 1836539862966,
"Detainers", "", "10/1/09", "9/30/10", 290304, "npr", 1836543397795,
"Detainers", "", "10/1/10", "9/30/11", 603877, "npr", 1836543308523,
"Detainers", "", "10/1/12", "9/30/13", 380916, "npr", 1836551433566,
"Detainers", "", "10/1/14", "9/30/15", 79053, "npr", 1836556496547,
"Detentions", "", "9/1/23", "3/20/25", 767747, "32025", 1836559130180,
"Detentions", "", "9/1/23", "6/20/25", 1173910, "62025", 1903652224645,
"Detentions", "", "10/1/15", "9/30/16", 764332, "2019-ICFO-21307", 1851662838490,
"Detentions", "", "10/1/14", "9/30/15", 665212, "2019-ICFO-21307", 1851667352417,
"Detentions", "", "10/1/16", "9/30/17", 692356, "2019-ICFO-21307", 1851661107897,
"Detentions", "", "10/1/10", "9/30/11", 60200, "uwchr", 1836558695933,
"Detentions", "", "10/1/11", "9/30/12", 988494, "uwchr", 1836538890174,
"Detentions", "", "10/1/12", "9/30/13", 877453, "uwchr", 1836539896765,
"Detentions", "", "10/1/13", "9/30/14", 848952, "uwchr", 1836558270445,
"Detentions", "", "10/1/14", "9/30/15", 654963, "uwchr", 1836545212556,
"Detentions", "", "10/1/15", "9/30/16", 748077, "uwchr", 1836551270304,
"Detentions", "", "10/1/16", "9/30/17", 756918, "uwchr", 1836545300833,
"Detentions", "", "10/1/17", "9/30/18", 903960, "uwchr", 1836550118061,
"Detentions", "", "10/1/18", "9/30/19", 940511, "uwchr", 1836545192598,
"Detentions", "", "10/1/19", "9/30/20", 415226, "uwchr", 1836540429374,
"Detentions", "", "10/1/20", "9/30/21", 363380, "uwchr", 1836545015666,
"Detentions", "", "10/1/21", "9/30/22", 480921, "uwchr", 1836551672923,
"Detentions", "", "10/1/22", "9/30/23", 513664, "uwchr", 1836556182456,
"Detentions", "", "10/1/23", "9/30/24", 114833, "uwchr", 1836538575856,
"Encounters", "", "9/1/23", "3/20/25", 868569, "32025", 1836544630925,
"Encounters", "", "9/1/23", "6/20/25", 1241817, "62025", 1903642269570,
"Encounters", "", "10/1/11", "9/30/12", 2054228, "uwchr", 1836545587160,
"Encounters", "", "10/1/14", "9/30/15", 3470882, "uwchr", 1836539886526,
"Removals", "", "9/1/23", "6/20/25", 106469, "62025", 1903640338806,
"Removals", "", "10/1/02", "9/30/03", 159611, "14-03290", 1875129596640,
"Removals", "", "10/1/11", "9/30/12", 409504, "14-03290", 1875139734735,
"Removals", "", "10/1/12", "9/30/13", 368807, "14-03290", 1875139943394,
"Removals", "", "10/1/03", "9/30/04", 177707, "14-03290", 1875132208001,
"Removals", "", "10/1/04", "9/30/05", 183543, "14-03290", 1875135429164,
"Removals", "", "10/1/05", "9/30/06", 212205, "14-03290", 1875129589363,
"Removals", "", "10/1/06", "9/30/07", 300420, "14-03290", 1875129774679,
"Removals", "", "10/1/07", "9/30/08", 383941, "14-03290", 1875130303126,
"Removals", "", "10/1/08", "9/30/09", 384567, "14-03290", 1875137637027,
"Removals", "", "10/1/09", "9/30/10", 391694, "14-03290", 1875138789538,
"Removals", "", "10/1/10", "9/30/11", 396245, "14-03290", 1875127271383,
"Removals", "", "10/1/11", "9/30/12", 1094451, "uwchr", 1836557461924,
"Removals", "", "10/1/14", "9/30/15", 1571114, "uwchr", 1836555735995) |> 
  mutate(
    Start = as.Date(Start, format = "%m/%d/%y"),
    End = as.Date(End, format = "%m/%d/%y"),
    URL = paste0("<a href='https://ucla.box.com/shared/static/", URL, ".zip'>", URL, "</a>"),
  ) |> 
    reactable::reactable(
      columns = list(
        Type = colDef(name = "Type", minWidth = 65),
        Description = colDef(name = "Description", minWidth = 150),
        Start = colDef(
          name = "Start", 
          minWidth = 75, 
          cell = function(value) format(value, "%b. %Y")
        ),
        End = colDef(
          name = "End", 
          minWidth = 75, 
          cell = function(value) format(value, "%b. %Y")
        ),

        Records = colDef(
          name = "Records",
          minWidth = 55,
          align = "right", 
          cell = function(value) scales::label_number(scale_cut = scales::cut_short_scale())(value)
        ),
        Release = colDef(name = "Release", minWidth = 75),

        URL = colDef(name = "URL", minWidth = 100, html = TRUE)
      ),
      groupBy = "Release",
      defaultExpanded = TRUE,
      pagination = FALSE
    )
```