---
title: "Immigration and Customs Enforcement"
---

```{r}
library(reactable)
library(tidyverse)
library(glue)

col_defs_ice <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Identifiers = colDef(
    align = "left",
    minWidth = 50,
    html = TRUE,
    cell = function(value) {
      if (is.na(value)) {
        return(as.character(
          htmltools::tags$div(
            style = "display: flex; align-items: left;",
            htmltools::tags$i(
              class = "fas fa-xmark",
              style = "color: red; font-size: 1.2em;"
            )
          )
        ))
      }
  
      val <- trimws(value)
  
      if (val == "--") {
        return("&ndash;")  # en dash
      }
  
      as.character(
        htmltools::tags$div(
          style = "display: flex; align-items: left",
          htmltools::tags$i(
            class = "fas fa-check",
            style = "color: green; font-size: 1.2em;"
          )
        )
      )
    }
  ),
  Records = colDef(minWidth = 55, align = "right"),
  Download = colDef(minWidth = 75, html = TRUE)
)

col_defs_ice_cleaned <- 
  c(col_defs_ice[-length(col_defs_ice)], 
    list(
      Raw = colDef(
        minWidth = 50,
        html = TRUE,
        cell = function(value) {
          if (is.null(value) || length(value) == 0) {
            return("&ndash;")  # en dash
          }

          paste0(
            # "<a href='", value[1], "'>",
            "<img src='/img/", value[3], ".svg' width=25 height=25 alt='", value[3], "'>"
            # "</a>"
          )
        }
      ),
      Processed = colDef(
        # name = "Cleaned",
        minWidth = 100,
        html = TRUE,
        cell = function(value) {
          if (is.null(value) || length(value) == 0 || is.na(value[[1]][[1]])) {
            return("&ndash;")  # en dash
          }

          links <- map(value, ~ {
            paste0(
              "<a href='", .x[[1]], "'>",
              "<img src='/img/", .x[[3]], ".svg' width=25 height=25 alt='", .x[[3]], "'>",
              "</a>"
            )
          })

          paste(links, collapse = " ")
        }
      )
    )
  )

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)

releases_df <- 
  tibble::tribble(
  ~Agency, ~`FOIA request`, ~Date_Sort, ~Date, ~Release, ~Types, ~Identifiers, ~source_label, ~source_URL,
  "ICE", "2024-ICFO-39357", "2025-08-08", "Early Aug. 2025", "Early Aug. 2025", "Arrests, Detainers, Detentions, Encounters, Removals", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2024-ICFO-39357", "2025-07-08", "Late Jun. 2025", "Late Jun. 2025", "Arrests, Detainers, Detentions, Encounters, Removals", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2024-ICFO-39357", "2025-06-20", "Early Jun. 2025", "Early Jun. 2025", "Arrests, Detainers, Detentions, Encounters, Removals", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2024-ICFO-39357", "2025-03-20", "Feb. 2025", "Feb. 2025", "Arrests, Detainers, Detentions, Encounters", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2022-ICFO-22955", "2024-07-01", "Jul. 2024", NA_character_, "Arrests", "Yes", "García Hernández", "https://www.ccgarciahernandez.com",
  "ICE", "2022-ICFO-09022", "2024-01-01", "Jan. 2024", NA_character_, "Detentions", "Yes", "UWCHR", "https://github.com/UWCHR/ice-detain",
  "ICE", "2023-ICFO-42034", "2023-11-01", "Nov. 2023", NA_character_, "Arrests, Detentions, Removals, Risk classification assessments", "Feb. 2024", "ICE", "https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip",
  "ICE", "2022-ICFO-09023", "2023-03-01", "Mar. 2023, Apr. 2023", NA_character_,  "Arrests, Encounters, Removals", NA, "UWCHR", "https://github.com/UWCHR/ice-enforce",
  "ICE", "2021-ICAP-00188", "2022-01-01", "2022", NA_character_, "Flights",  NA, "UWCHR", "https://github.com/UWCHR/ice-air",
  "ICE", "2019-ICFO-32423", "2019-01-01", "2019", NA_character_, "Flights",  NA, "UWCHR", "https://github.com/UWCHR/ice-air",
  "ICE", "2019-ICFO-21307", "2017-08-01", "Aug. 2017", NA_character_, "Detentions", NA, "García Hernández", "https://www.ccgarciahernandez.com",
  "ICE", "npr", "2016-01-01", "2016", NA_character_,  "Detainers", NA, "NPR", "https://github.com/nprapps/sanctuary-cities",
  "ICE", "14-03290", "2014-01-01", "2014", NA_character_,  "Removals", NA, "NYT", "https://nytimes.com"
)
```

ICE collects data on every person it encounters, arrests, detains, transports via flight, and deports. 

::: {.callout-tip appearance="default"}

## Getting started with ICE data

Our [ICE frequently asked data questions](/docs/ice.html#sec-faq) is a good place to start before analyzing the data. We also provide a [codebook](/docs/ice.html#sec-codebook) describes each data table and the fields within them.

:::

## Latest data release

The most recent release of data covers ICE enforcement actions through early August 2025. We are actively seeking ongoing updates.

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Identifiers, ~Records, ~Download,
  # edit all these to have the new info
  "Arrests", "Sep. 2023", "Late Jul. 2025", "Late Jul. 2025", "292K", "<a href='https://ucla.box.com/shared/static/oztwzsxc45ngwi26vk98o2l7g7tpwcjw.xlsx'>xlsx</a> (45 MB)",
  "Detainers", "Sep. 2023", "Late Jul. 2025", "Late Jul. 2025", "339K", "<a href='https://ucla.box.com/shared/static/k699orsf5wm8i9ehr1x4foownlj5zuyn.xlsx'>xlsx</a> (107 MB)",
  "Detentions", "Sep. 2023", "Late Jul. 2025", "Late Jul. 2025", "1.32M", "<a href='https://ucla.box.com/shared/static/c6tfgtq90er5df898vaq912okchn9o66.xlsx'>xlsx</a> (280 MB)", 
  "Encounters", "Sep. 2023", "Late Jul. 2025", "Late Jul. 2025", "1.36M", "<a href='https://ucla.box.com/shared/static/tp02l4356coo3vzjbbksk51olobzis73.xlsx'>xlsx</a> (192 MB)"
) |>
  reactable::reactable(columns = c(col_defs_ice, list(Type = colDef(minWidth = 65))), sortable = FALSE, pagination = FALSE)
```

<div style="height: 10px;"></div>

<!-- edit the link below with a Box link to a ZIP file you create with all the new release files -->

[Download the complete latest release as a ZIP file](https://ucla.box.com/s/1ja2vev1o073u15s7hce58axpz700ga7.zip) (704 MB)

::: {.callout-warning appearance="simple"}

We are not posting a removals dataset in this release, because we found that it included far fewer records in 2025 than the previous release in late June. We remain concerned that the late June removals table may not include all relevant records, and that associated fields in the other tables, such as the departure date, may also create an incomplete picture of removals. These concerns lead us to advise caution when performing any analysis of removals in any ICE data release in 2025. If you have insight into these problems or find other concerns, please let us know. We are actively seeking updated and corrected data.

:::

## Linked data from 2012-2023

To enable longer-term analysis, we provide data for major ICE enforcement actions from October 2011 through September 2023 [obtained by the ACLU](/foia.html#aclu-v-ice-20182023).

The four tables are linked by unique identifiers for each noncitizen, but these identifiers differ from the latest data release and do not enable merging across the two data releases.

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Identifiers, ~Records, ~Download,
  # edit all these to have the new info
  "Arrests", "Oct. 2011", "Sep. 2023", "Aug. 2025", "1.8M", "<a href='https://ucla.box.com/shared/static/3i6xhnd5cig3qacy5phxvw9cmy7a71k1.zip'>zip</a> (99 MB)",
  "Detentions", "Oct. 2011", "Sep. 2023", "Aug. 2025", "8.5M", "<a href='https://ucla.box.com/shared/static/gjfcedj3ne4d6l6rt5sv0t6yfao18jzp.zip'>zip</a> (1.41 GB)", 
  "Removals", "Oct. 2011", "Sep. 2023", "Aug. 2025", "2.8M", "<a href='https://ucla.box.com/shared/static/hanv0cqbvxole910mo63z9uy40cwwi9t.zip'>zip</a> (499 MB)",
  "Risk classification assessment decisions", "Oct. 2011", "Sep. 2023", "Aug. 2025", "3.5M", "<a href='https://ucla.box.com/shared/static/x6jxz982onabumgfx0dwnd39b27ggoqz.zip'>zip</a> (596 MB)"
) |>
  reactable::reactable(columns = c(col_defs_ice, list(Type = colDef(minWidth = 65))), sortable = FALSE, pagination = FALSE)
```

<div style="height: 10px;"></div>

[Download the complete 2012-2023 release as a ZIP file](https://ucla.box.com/shared/static/csnihndb826omzizlps90szm60q39jxd.zip) (2.6 GB)

## Historical data archive 

We post below historical data that ICE produced in response to several FOIA requests by multiple organizations. Crucially, in some data releases, there are linked identifiers across data types such as arrests and detainers, allowing merges that enable tracing immigrants' pathways (anonymously) through the immigration enforcement pipeline. The identifiers are, unfortunately, different across releases, only enabling merging within a data release. See [below](#sec-about) for a description of each release.

<details class="column-page-inset-right">
<summary>Show archive</summary>

```{r}
tibble::tribble(
  ~Type,   ~Start,	    ~End,	      ~Records,	~FOIA,             ~Release,        ~URL,              
  # Location	                      Filename
  # early aug release
  "Arrests", "9/1/23", "8/8/25", 292000, "2024-ICFO-39357", "Early Aug. 2025",  1949895546724,
  "Detainers", "9/1/23", "8/8/25", 339000, "2024-ICFO-39357", "Early Aug. 2025",  1949896235918,
  "Detentions", "9/1/23", "8/8/25", 1320000, "2024-ICFO-39357", "Early Aug. 2025", 1949891740635, 
  "Encounters", "9/1/23", "8/8/25", 1360000, "2024-ICFO-39357", "Early Aug. 2025", 1949907882237,
  "Removals", "9/1/23", "8/8/25", 528000, "2024-ICFO-39357", "Early Aug. 2025", 1949895143395,

  # late june release
  "Arrests", "9/1/23", "6/20/25", 265000, "2024-ICFO-39357", "Late Jun. 2025",  1922082018423,
  "Detainers", "9/1/23", "6/20/25", 316000, "2024-ICFO-39357", "Late Jun. 2025",  1922081034353,
  "Detentions", "9/1/23", "6/20/25", 1230000, "2024-ICFO-39357", "Late Jun. 2025", 1922078517539, 
  "Encounters", "9/1/23", "6/20/25", 1280000, "2024-ICFO-39357", "Late Jun. 2025", 1922075106849,
  "Removals", "1/1/25", "6/20/25", 144000, "2024-ICFO-39357", "Late Jun. 2025", 1923097705535,

  "Arrests",				    "9/1/23",	  "3/20/25",	145802,	  "2024-ICFO-39357", "Feb. 2025",         1836554372496,    # ice/arrests/032025	            ERO Admin Arrests_2025-ICLI-00019_2024-ICFO-39357_LESA-STU_FINAL_raw.xlsx
  "Arrests",				    "9/1/23",	  "6/20/25",	249280,	  "2024-ICFO-39357", "Early Jun. 2025",         1903641913782,    # ice/arrests/062025	            2025-ICLI-00019_2024-ICFO-39357_ERO Admin Arrests_LESA-STU_FINAL_unprotected.xlsx
  "Arrests",				    "10/1/15",	"9/30/16",	107300,	  "2022-ICFO-22955",	NA_character_,  1851836294057,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY16).xlsx
  "Arrests",				    "10/1/16",	"9/30/17",	138876,	  "2022-ICFO-22955",	NA_character_,  1851833536271,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY17).xlsx
  "Arrests",				    "10/1/17",	"9/30/18",	153214,	  "2022-ICFO-22955",	NA_character_,  1851837546731,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY18).xlsx
  "Arrests",				    "10/1/18",	"9/30/19",	138775,	  "2022-ICFO-22955",	NA_character_,  1851831800585,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY19).xlsx
  "Arrests",				    "10/1/19",	"9/30/20",	100429,	  "2022-ICFO-22955",	NA_character_,  1851835191968,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY20).xlsx
  "Arrests",				    "10/1/20",	"9/30/21",	72849,	  "2022-ICFO-22955",	NA_character_,  1851833034596,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY21).xlsx
  "Arrests",				    "10/1/21",	"9/30/22",	142954,	  "2022-ICFO-22955",	NA_character_,  1851830686826,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY22).xlsx
  "Arrests",				    "10/1/22",	"9/30/23",	170864,	  "2022-ICFO-22955",	NA_character_,  1851836416108,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY23).xlsx
  "Arrests",				    "10/1/23",	"9/30/24",	95188,	  "2022-ICFO-22955",	NA_character_,  1851836311169,    # ice/arrests/2022-ICFO-22955	    ICE ERO Apprehension by AOR & Program (FY24 through July 2024).xlsx
  "Arrests",				    "10/1/11",	"9/30/12",	681578,	  "2022-ICFO-09023",	NA_character_,  1836557464054,    # ice/arrests/uwchr	              ERO_Arrests_FY2012-FY2014-REDACTED_raw.xlsx
  "Arrests",				    "10/1/14",	"9/30/15",	1059656,	"2022-ICFO-09023",	NA_character_,  1836540105544,    # ice/arrests/uwchr	              ERO_Arrests_FY2015-FY2023_YTD-REDACTED_raw.xlsx
  "Flights",				    "10/1/10",	"9/30/11",	2160,	    "2019-ICFO-32423",	NA_character_,  1836540049661,    # ice/arts/uwchr	                ARTS Data FY11-reviewed_raw.xlsx
  "Flights",				    "10/1/11",	"9/30/12",	2399,	    "2019-ICFO-32423",	NA_character_,  1836552599950,    # ice/arts/uwchr	                ARTS Data FY12-reviewed_raw.xlsx
  "Flights",				    "10/1/12",	"9/30/13",	2333,	    "2019-ICFO-32423",	NA_character_,  1836549849021,    # ice/arts/uwchr	                ARTS Data FY13-reviewed_raw.xlsx
  "Flights",				    "10/1/13",	"9/30/14",	5756,	    "2019-ICFO-32423",	NA_character_,  1836540958981,    # ice/arts/uwchr	                ARTS Data FY14-reviewed_raw.xlsx
  "Flights",				    "10/1/14",	"9/30/15",	1663,	    "2019-ICFO-32423",	NA_character_,  1836538695921,    # ice/arts/uwchr	                ARTS Data FY15-reviewed_raw.xlsx
  "Flights",				    "10/1/15",	"9/30/16",	1884,	    "2019-ICFO-32423",	NA_character_,  1836536493019,    # ice/arts/uwchr	                ARTS Data FY16-reviewed_raw.xlsx
  "Flights",				    "10/1/16",	"9/30/17",	1658,	    "2019-ICFO-32423",	NA_character_,  1836549806043,    # ice/arts/uwchr	                ARTS Data FY17-reviewed_raw.xlsx
  "Flights",				    "10/1/17",	"9/30/18",	1703,	    "2019-ICFO-32423",	NA_character_,  1836550883008,    # ice/arts/uwchr	                ARTS Data FY18-reviewed_raw.xlsx
  "Flights",				    "10/1/18",	"9/30/19",	1122,	    "2019-ICFO-32423",	NA_character_,  1836537162853,    # ice/arts/uwchr	                ARTS Data FY19 Year To Date-reviewed_raw.xlsx
  "Flight passengers",	"10/1/10",	"9/30/11",	233061,	  "2019-ICFO-32423",	NA_character_,  1836536399014,    # ice/arts/uwchr	                ARTS Passenger Data FY11_raw.xlsx
  "Flight passengers",	"10/1/11",	"9/30/12",	282178,	  "2019-ICFO-32423",	NA_character_,  1836538136812,    # ice/arts/uwchr	                ARTS Passenger Data FY12_raw.xlsx
  "Flight passengers",	"10/1/12",	"9/30/13",	263621,	  "2019-ICFO-32423",	NA_character_,  1836555001702,    # ice/arts/uwchr	                ARTS Passenger Data FY13_raw.xlsx
  "Flight passengers",	"10/1/13",	"9/30/14",	249563,	  "2019-ICFO-32423",	NA_character_,  1836545751933,    # ice/arts/uwchr	                ARTS Passenger Data FY14_raw.xlsx
  "Flight passengers",	"10/1/14",	"9/30/15",	157067,	  "2019-ICFO-32423",	NA_character_,  1836539073027,    # ice/arts/uwchr	                ARTS Passenger Data FY15_raw.xlsx
  "Flight passengers",	"10/1/15",	"9/30/16",	168239,	  "2019-ICFO-32423",	NA_character_,  1836549772221,    # ice/arts/uwchr	                ARTS Passenger Data FY16_raw.xlsx
  "Flight passengers",	"10/1/16",	"9/30/17",	180384,	  "2019-ICFO-32423",	NA_character_,  1836541672269,    # ice/arts/uwchr	                ARTS Passenger Data FY17_raw.xlsx
  "Flight passengers",	"10/1/17",	"9/30/18",	191648,	  "2019-ICFO-32423",	NA_character_,  1836553076817,    # ice/arts/uwchr	                ARTS Passenger Data FY18_raw.xlsx
  "Flight passengers",	"10/1/18",	"9/30/19",	37259,	  "2019-ICFO-32423",	NA_character_,  1836536207751,    # ice/arts/uwchr	                ARTS Passenger Data FY19_raw.xlsx
  "Flight passengers",	"10/1/18",	"5/8/20",	  3182,	    "2021-ICAP-00188",	NA_character_,  1836545668509,    # ice/arts/uwchr	                ARTS_Missions-redacted_raw.xlsx
  "Flight passengers",	"10/1/18",	"5/8/20",	  341290,	  "2021-ICAP-00188",	NA_character_,  1836550007406,    # ice/arts/uwchr	                ARTS_Passenger-redacted_raw.xlsx
  "Detainers",			    "9/1/23",	  "3/20/25",	199335,	  "2024-ICFO-39357",  "Feb. 2025",        1836552782163,    # ice/detainers/032025	          ERO Detainers_2025-ICLI-00019_2024-ICFO-39357_LESA-STU_FINAL_raw.xlsx
  "Detainers",			    "9/1/23",	  "6/20/25",	305738,	  "2024-ICFO-39357",  "Early Jun. 2025",        1903648700489,    # ice/detainers/062025	          2025-ICLI-00019_2024-ICFO-39357_ERO Detainers_LESA-STU_FINAL_unprotected.xlsx
  "Detainers",			    "10/1/09",	"9/30/10",	290253,	  "npr",					    NA_character_,  1836555210688,    # ice/detainers/npr	              detainersfy10_raw.csv
  "Detainers",			    "10/1/10",	"9/30/11",	317327,	  "npr",					    NA_character_,  1836552467952,    # ice/detainers/npr	              detainersfy11_raw.csv
  "Detainers",			    "10/1/11",	"9/30/12",	286507,	  "npr",					    NA_character_,  1836540940171,    # ice/detainers/npr	              detainersfy12_raw.csv
  "Detainers",			    "10/1/12",	"9/30/13",	216717,	  "npr",					    NA_character_,  1836550482581,    # ice/detainers/npr	              detainersfy13_raw.csv
  "Detainers",			    "10/1/13",	"9/30/14",	164188,	  "npr",					    NA_character_,  1836551310786,    # ice/detainers/npr	              detainersfy14_raw.csv
  "Detainers",			    "10/1/14",	"9/30/15",	97021,	  "npr",					    NA_character_,  1836547271446,    # ice/detainers/npr	              detainersfy15_raw.csv
  "Detainers",			    "10/1/15",	"9/30/16",	85561,	  "npr",					    NA_character_,  1836555104717,    # ice/detainers/npr	              detainersfy16_raw.csv
  "Detainers",			    "10/1/16",	"9/30/17",	94013,	  "npr",					    NA_character_,  1836554262318,    # ice/detainers/npr	              detainersfy17_raw.csv
  "Detainers",			    "10/1/08",	"9/30/09",	248255,	  "npr",					    NA_character_,  1836543616508,    # ice/detainers/npr	              detainersfy9_raw.csv
  "Detainers",			    "10/1/07",	"9/30/08",	212407,	  "npr",					    NA_character_,  1836553974742,    # ice/detainers/npr	              lea-detainers-FY08_raw.txt
  "Detainers",			    "10/1/08",	"9/30/09",	248272,	  "npr",					    NA_character_,  1836539862966,    # ice/detainers/npr	              lea-detainers-FY09_raw.txt
  "Detainers",			    "10/1/09",	"9/30/10",	290304,	  "npr",					    NA_character_,  1836543397795,    # ice/detainers/npr	              lea-detainers-FY10_raw.txt
  "Detainers",			    "10/1/10",	"9/30/11",	603877,	  "npr",					    NA_character_,  1836543308523,    # ice/detainers/npr	              lea-detainers-FY11_12_raw.txt
  "Detainers",			    "10/1/12",	"9/30/13",	380916,	  "npr",					    NA_character_,  1836551433566,    # ice/detainers/npr	              lea-detainers-FY13_14_raw.txt
  "Detainers",			    "10/1/14",	"9/30/15",	79053,	  "npr",					    NA_character_,  1836556496547,    # ice/detainers/npr	              lea-detainers-FY15YTD_raw.txt
  "Detentions",			    "9/1/23",	  "3/20/25",	767747,	  "2024-ICFO-39357",  "Feb. 2025",        1836559130180,    # ice/detentions/032025	          ICE Detentions_2025-ICLI-00019_2024-ICFO-39357_LESA-STU_FINAL_raw.xlsx
  "Detentions",			    "9/1/23",	  "6/20/25",	1173910,	"2024-ICFO-39357",  "Early Jun. 2025",        1903652224645,    # ice/detentions/062025	          2025-ICLI-00019_2024-ICFO-39357_ICE Detentions_LESA-STU_FINAL_unprotected.xlsx
  "Detentions",			    "10/1/15",	"9/30/16",	764332,	  "2019-ICFO-21307",	NA_character_,	1851662838490,    # ice/detentions/2019-ICFO-21307	ICE ERO Detention by AOR (FY16).xlsx
  "Detentions",			    "10/1/14",	"9/30/15",	665212,	  "2019-ICFO-21307",	NA_character_,	1851667352417,    # ice/detentions/2019-ICFO-21307	ICE ERO Detention by AOR & Length of Detention (FY15).xlsx
  "Detentions",			    "10/1/16",	"9/30/17",	692356,	  "2019-ICFO-21307",	NA_character_,	1851661107897,    # ice/detentions/2019-ICFO-21307	ICE ERO Detention by AOR & Length of Detention (FY17 through Aug 18, 2017).xlsx
  "Detentions",			    "10/1/10",	"9/30/11",	60200,	  "2022-ICFO-09022",	NA_character_,	1836558695933,    # ice/detentions/uwchr	          ICE Detentions_FY2011 and Prior_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/11",	"9/30/12",	988494,	  "2022-ICFO-09022",	NA_character_,	1836538890174,    # ice/detentions/uwchr	          ICE Detentions_FY2012_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/12",	"9/30/13",	877453,	  "2022-ICFO-09022",	NA_character_,	1836539896765,    # ice/detentions/uwchr	          ICE Detentions_FY2013_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/13",	"9/30/14",	848952,	  "2022-ICFO-09022",	NA_character_,	1836558270445,    # ice/detentions/uwchr	          ICE Detentions_FY2014_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/14",	"9/30/15",	654963,	  "2022-ICFO-09022",	NA_character_,	1836545212556,    # ice/detentions/uwchr	          ICE Detentions_FY2015_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/15",	"9/30/16",	748077,	  "2022-ICFO-09022",	NA_character_,	1836551270304,    # ice/detentions/uwchr	          ICE Detentions_FY2016_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/16",	"9/30/17",	756918,	  "2022-ICFO-09022",	NA_character_,	1836545300833,    # ice/detentions/uwchr	          ICE Detentions_FY2017_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/17",	"9/30/18",	903960,	  "2022-ICFO-09022",	NA_character_,	1836550118061,    # ice/detentions/uwchr	          ICE Detentions_FY2018_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/18",	"9/30/19",	940511,	  "2022-ICFO-09022",	NA_character_,	1836545192598,    # ice/detentions/uwchr	          ICE Detentions_FY2019_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/19",	"9/30/20",	415226,	  "2022-ICFO-09022",	NA_character_,	1836540429374,    # ice/detentions/uwchr	          ICE Detentions_FY2020_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/20",	"9/30/21",	363380,	  "2022-ICFO-09022",	NA_character_,	1836545015666,    # ice/detentions/uwchr	          ICE Detentions_FY2021_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/21",	"9/30/22",	480921,	  "2022-ICFO-09022",	NA_character_,	1836551672923,    # ice/detentions/uwchr	          ICE Detentions_FY2022_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/22",	"9/30/23",	513664,	  "2022-ICFO-09022",	NA_character_,	1836556182456,    # ice/detentions/uwchr	          ICE Detentions_FY2023_LESA-STU_FINAL-Redacted_raw.xlsx
  "Detentions",			    "10/1/23",	"9/30/24",	114833,	  "2022-ICFO-09022",	NA_character_,	1836538575856,    # ice/detentions/uwchr	          ICE Detentions_FY2024_LESA-STU_FINAL-Redacted_raw.xlsx
  "Encounters",			    "9/1/23",	  "3/20/25",	868569,		"2024-ICFO-39357",  "Feb. 2025",        1836544630925,    # ice/encounters/032025	          ERO Encounters_2025-ICLI-00019_2024-ICFO-39357_LESA-STU_FINAL_raw.xlsx
  "Encounters",			    "9/1/23",	  "6/20/25",	1241817,  "2024-ICFO-39357",  "Early Jun. 2025",        1903642269570,    # ice/encounters/062025	          2025-ICLI-00019_2024-ICFO-39357_ERO Encounters_FINAL_unprotected.xlsx
  "Encounters",			    "10/1/11",	"9/30/12",	2054228,	"2022-ICFO-09023",	NA_character_,	1836545587160,    # ice/encounters/uwchr	          ERO_Encounters_FY2012-FY2014-REDACTED_raw.xlsx
  "Encounters",			    "10/1/14",	"9/30/15",	3470882,	"2022-ICFO-09023",	NA_character_,	1836539886526,    # ice/encounters/uwchr	          ERO_Encounters_FY2015-FY2023_YTD-REDACTED_raw.xlsx
  "Removals",			      "9/1/23",	  "6/20/25",	106469,		"2024-ICFO-39357",  "Early Jun. 2025",        1903640338806,    # ice/removals/062025	            2025-ICLI-00019_2024-ICFO-39357_ICE Removals_LESA-STU_FINAL_2025-only_unprotected.xlsx
  "Removals",			      "10/1/02",	"9/30/03",	159611,	  "14-03290",				  NA_character_,  1875129596640,    # ice/removals/14-03290	          1 14-03290_FY03_Highlighted_raw.xlsx
  "Removals",			      "10/1/11",	"9/30/12",	409504,	  "14-03290",				  NA_character_,  1875139734735,    # ice/removals/14-03290	          10 14-03290_FY12_Highlighted_raw.xlsx
  "Removals",			      "10/1/12",	"9/30/13",	368807,	  "14-03290",				  NA_character_,  1875139943394,    # ice/removals/14-03290	          11 14-03290_FY13_Highlighted_raw.xlsx
  "Removals",			      "10/1/03",	"9/30/04",	177707,	  "14-03290",				  NA_character_,  1875132208001,    # ice/removals/14-03290	          2 14-03290_FY04_Highlighted_raw.xlsx
  "Removals",			      "10/1/04",	"9/30/05",	183543,	  "14-03290",				  NA_character_,  1875135429164,    # ice/removals/14-03290	          3 14-03290_FY05_Highlighted_raw.xlsx
  "Removals",			      "10/1/05",	"9/30/06",	212205,	  "14-03290",				  NA_character_,  1875129589363,    # ice/removals/14-03290	          4 14-03290_FY06_Highlighted_raw.xlsx
  "Removals",			      "10/1/06",	"9/30/07",	300420,	  "14-03290",				  NA_character_,  1875129774679,    # ice/removals/14-03290	          5 14-03290_FY07_Highlighted_raw.xlsx
  "Removals",			      "10/1/07",	"9/30/08",	383941,	  "14-03290",				  NA_character_,  1875130303126,    # ice/removals/14-03290	          6 14-03290_FY08_Highlighted_raw.xlsx
  "Removals",			      "10/1/08",	"9/30/09",	384567,	  "14-03290",				  NA_character_,  1875137637027,    # ice/removals/14-03290	          7 14-03290_FY09_Highlighted_raw.xlsx
  "Removals",			      "10/1/09",	"9/30/10",	391694,	  "14-03290",				  NA_character_,  1875138789538,    # ice/removals/14-03290	          8 14-03290_FY10_Highlighted_raw.xlsx
  "Removals",			      "10/1/10",	"9/30/11",	396245,	  "14-03290",				  NA_character_,  1875127271383,    # ice/removals/14-03290	          9 14-03290_FY11_Highlighted_raw.xlsx
  "Removals",			      "10/1/11",	"9/30/14",	1094451,	"2022-ICFO-09023",	NA_character_,  1836557461924,    # ice/removals/uwchr	            ICE_Removals_FY2012-FY2014-REDACTED_raw.xlsx
  "Removals",			      "10/1/14",	"1/28/23",	1571114,	"2022-ICFO-09023",	NA_character_,  1836555735995,    # ice/removals/uwchr	            ICE_Removals_FY2015-FY2023_YTD-REDACTED_raw.xlsx
  ) |> 
  mutate(
    Start = as.Date(Start, format = "%m/%d/%y"),
    End = as.Date(End, format = "%m/%d/%y"),
    URL = glue("<a href='<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_{URL}'>{if_else(FOIA == 'npr', 'csv', 'xlsx')}</a>")
  ) |> 
    left_join(releases_df |> select(`FOIA request`, `Release`, Identifiers, source_label, source_URL, Date_Sort), by = c("FOIA" = "FOIA request", "Release")) |> 
    arrange(desc(Date_Sort), Type, Start) |> 
    select(-Date_Sort) |> 
    # create a variable for Contributor that links to the source if it is not ICE
    mutate(
      Source = if_else(is.na(source_label) | source_label == "ICE", NA_character_, paste0("<a href='", source_URL, "'>", source_label, "</a>")),
      Release = glue("{FOIA} {if_else(is.na(Release), '', glue('({Release})'))}") |> str_squish() |> str_replace("npr", "FOIA number unknown"),
      .keep = "unused"
    ) |>
      relocate(
        Release
      ) |>
      relocate(Identifiers, .after = End) |>
      relocate(URL, .after = Source) |> 
    reactable::reactable(
      columns = list(
        # release column 
        Release = colDef(
          name = "Release",
          minWidth = 100
        ),
        Type = colDef(name = "Type", minWidth = 75),
        Start = colDef(
          name = "Start", 
          minWidth = 75, 
          cell = function(value) format(value, "%b. %Y")
        ),
        End = colDef(
          name = "End", 
          minWidth = 75, 
          cell = function(value) format(value, "%b. %Y")
        ),
        Identifiers = colDef(
    align = "left",
    minWidth = 75,
    html = TRUE,
    cell = function(value) {
      if (is.na(value)) {
        return(as.character(
          htmltools::tags$div(
            style = "display: flex; align-items: left;",
            htmltools::tags$i(
              class = "fas fa-xmark",
              style = "color: red; font-size: 1.2em;"
            )
          )
        ))
      }
  
      val <- trimws(value)
  
      if (val == "--") {
        return("&ndash;")  # en dash
      }
  
      as.character(
        htmltools::tags$div(
          style = "display: flex; align-items: left",
          htmltools::tags$i(
            class = "fas fa-check",
            style = "color: green; font-size: 1.2em;"
          )
        )
      )
    }
  ),
        Records = colDef(
          name = "Records",
          minWidth = 55,
          align = "right", 
          cell = function(value) scales::label_number(scale_cut = scales::cut_short_scale())(value)
        ),
        # add contributor column that links to source if it is not ICE
        Source = colDef(
          name = "Contributor",
          minWidth = 85,
          html = TRUE
        ),
        URL = colDef(name = "Download", minWidth = 75, html = TRUE)
  ),
  pagination = FALSE
    )
```


</details>
