---
title: "Immigration and Customs Enforcement"
---

```{r}
library(reactable)
library(tidyverse)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

col_defs_ice <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Identifiers = colDef(
    align = "left",
    minWidth = 70,
    html = TRUE,
    cell = function(value) {
      if (is.na(value)) {
        return(as.character(
          htmltools::tags$div(
            style = "display: flex; align-items: left;",
            htmltools::tags$i(
              class = "fas fa-xmark",
              style = "color: red; font-size: 1.2em;"
            )
          )
        ))
      }
  
      val <- trimws(value)
  
      if (val == "--") {
        return("&ndash;")  # en dash
      }
  
      as.character(
        htmltools::tags$div(
          style = "display: flex; align-items: left",
          htmltools::tags$i(
            class = "fas fa-check",
            style = "color: green; font-size: 1.2em;"
          )
        )
      )
    }
  ),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 55, html = TRUE),
  Download = colDef(minWidth = 75, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

ICE collects data on every person it encounters, arrests, detains, transports via flight, and deports. 

We post below data that ICE produced in response to several FOIA requests by multiple organizations. Crucially, in some data releases, there are linked identifiers across data types such as arrests and detainers, allowing merges that enable tracing immigrants pathways (anonymously) through the immigration enforcement pipeline. The identifiers are, unfortunately, different across releases, only enabling merging within a data release. See [below](#sec-about) for a description of each release.

::: {.callout-note appearance="simple"}

## Latest ICE data release

<div style="margin-top: 0.5em;"></div>

The most recent release of data is from June 2025. We are actively seeking ongoing updates.

```{r}
tibble::tribble(
  ~Type, ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  # edit all these to have the new info
  "Arrests", "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "249K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/x1ekojary0k7ffmr6lg1a492koh28erw.xlsx'>xlsx</a> (32 MB)",
  "Detainers", "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "306K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/sy7z6c08aq159htvfudw8q98zawv5in2.xlsx'>xlsx</a> (76 MB)",
  "Detentions", "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "1.17M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/xvpjjqjhv14en0dsri70g4caltlhoj5p.xlsx'>xlsx</a> (203 MB)", 
  "Encounters", "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "1.24M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/ohg6tz7uzp93cljg1yhhsn46jfodh3i9.xlsx'>xlsx</a> (142 MB)",
  "Removals", "Jan. 1, 2025", "Early Jun. 2025", "Jun. 2025", "106K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/li1sep40gui5dj09izhh8kzr4bajqyon.xlsx'>xlsx</a> (25 MB)"
) |>
  reactable::reactable(columns = c(col_defs_ice, list(Type = colDef(minWidth = 65))), pagination = FALSE)
```
<!-- edit the link below with a Box link to a ZIP file you create with all the new release files -->

[Download the complete latest release as a ZIP file](https://ucla.box.com/shared/static/juemu5lxbw67iwltfwk2r621mxh31cha.zip) (537 MB)

:::

::: {.callout-warning}

The removals dataset from the June 2025 ICE release only includes records from Jan. 1, 2025 onward because the records from before Jan. 1, 2025 appeared to have significant errors. Although we have not found obvious errors in the later records, which we have posted, the errors in the earlier records lead us to advise caution when using the removals data table. If you find other errors, please let us know. We are actively seeking data for the full period.

:::


## Arrests

This dataset shows the date and method of every arrest (apprehension), along with some other case information, including basic information about individuals' nationality and whether they had criminal convictions.

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  # edit this to have the new data
  "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "249K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/x1ekojary0k7ffmr6lg1a492koh28erw.xlsx'>xlsx</a> (32 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Mid Nov. 2023", "Mid Feb. 2025", "Mar. 2025", "146K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554372496'>xlsx</a> (21 MB)",
  "Oct. 1, 2016", "Sep. 30, 2023", "Nov. 2023", "912K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836542152676'>xlsx</a> (53 MB)",
  "Oct. 1, 2011", "Sep. 30, 2016", "Nov. 2023", "901K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555467571'>xlsx</a> (53 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "1M", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540105544'>xlsx</a> (71 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", NA, "682K", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557464054'>xlsx</a> (41 MB)",
  "Oct. 1, 2015", "Sept. 30, 2016", "Jul. 2024", "107K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851836294057'>xlsx</a> (63 MB)",
  "Oct. 1, 2016", "Sept. 30, 2017", "Jul. 2024", "139K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851833536271'>xlsx</a> (82 MB)",
  "Oct. 1, 2017", "Sept. 30, 2018", "Jul. 2024", "153K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851837546731'>xlsx</a> (90 MB)",
  "Oct. 1, 2018", "Sept. 30, 2019", "Jul. 2024", "139K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851831800585'>xlsx</a> (81 MB)",
  "Oct. 1, 2019", "Sept. 30, 2020", "Jul. 2024", "100K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851835191968'>xlsx</a> (59 MB)",
  "Oct. 1, 2020", "Sept. 30, 2021", "Jul. 2024", "73K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851833034596'>xlsx</a> (74 MB)",
  "Oct. 1, 2021", "Sept. 30, 2022", "Jul. 2024", "143K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851830686826'>xlsx</a> (90 MB)",
  "Oct. 1, 2022", "Sept. 30, 2023", "Jul. 2024", "171K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851836416108'>xlsx</a> (90 MB)",
  "Oct. 1, 2023", "Late Jul. 2024", "Jul. 2024", "95K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=l369bbmbori13vzdlfgp9omx2e30l5b0&file_id=f_1851836311169'>xlsx</a> (53 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Detainers

Detainers are requests that ICE makes to prisons and jails to hold individuals for transfer to immigration custody and/or to notify ICE of their release dates. This dataset tracks each detainer request.

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source,  ~Download,
  # edit this to have the new data
  "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "306K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/sy7z6c08aq159htvfudw8q98zawv5in2.xlsx'>xlsx</a> (76 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Mid Nov. 2023", "Mid Feb. 2025", "Mar. 2025", "199K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552782163'>xlsx</a> (59 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", NA, "94K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554262318'>csv</a> (21 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", NA, "86K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555104717'>csv</a> (19 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "97K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547271446'>csv</a> (22 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "79K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556496547'>txt</a> (9 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014", NA, "164K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551310786'>csv</a> (37 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", NA, "217K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550482581'>csv</a> (49 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", NA, "381K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551433566'>txt</a> (22 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", NA, "287K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540940171'>csv</a> (65 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011", NA, "317K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552467952'>csv</a> (72 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011", NA, "604K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543308523'>txt</a> (35 MB)",
  "Oct. 1, 2009", "Sep. 30, 2010", NA, "290K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555210688'>csv</a> (66 MB)",
  "Oct. 1, 2009", "Sep. 30, 2010", NA, "290K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543397795'>txt</a> (17 MB)",
  "Oct. 1, 2008", "Sep. 30, 2009", NA, "248K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543616508'>csv</a> (53 MB)",
  "Oct. 1, 2008", "Sep. 30, 2009", NA, "248K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539862966'>txt</a> (14 MB)",
  "Oct. 1, 2007", "Sep. 30, 2008", NA, "212K", "<a href='https://github.com/nprapps/sanctuary-cities'>NPR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836553974742'>txt</a> (12 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Detentions

This dataset includes a row for every detention book-in/book-out. Notice that a single stay in detention—defined by a stay book-in and stay book-out date—may include multiple rows because ICE frequently transfers people between detention centers. We urge particular caution in using this dataset because it only includes book-outs that occurred after September 2023; this means that some information concerning individuals detained at the beginning of the data may be missing.

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source,  ~Download,
  # edit to have the new data
  "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "1.17M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/xvpjjqjhv14en0dsri70g4caltlhoj5p.xlsx'>xlsx</a> (203 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Mid Nov. 2023", "Mid Feb. 2025", "Mar. 2025", "768K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836559130180'>xlsx</a> (142 MB)",
  "Oct. 1, 2023", "Sep. 30, 2024", "Jan. 2024", "115K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538575856'>xlsx</a> (21 MB)",
  "Oct. 1, 2022", "Sep. 30, 2023", "Nov. 2023", "471K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557968001'>xlsx</a> (81 MB)",
  "Oct. 1, 2022", "Sep. 30, 2023", "Jan. 2024", "514K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556182456'>xlsx</a> (96 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "Nov. 2023", "447K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537649686'>xlsx</a> (79 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "Jan. 2024", "481K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551672923'>xlsx</a> (92 MB)",
  "Oct. 1, 2020", "Sep. 30, 2021", "Nov. 2023", "441K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547497285'>xlsx</a> (77 MB)",
  "Oct. 1, 2020", "Sep. 30, 2021", "Jan. 2024", "363K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545015666'>xlsx</a> (69 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020", "Nov. 2023", "355K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540368526'>xlsx</a> (60 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020", "Jan. 2024", "415K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540429374'>xlsx</a> (76 MB)",
  "Oct. 1, 2018", "Sep. 30, 2019", "Nov. 2023", "878K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548415787'>xlsx</a> (149 MB)",
  "Oct. 1, 2018", "Sep. 30, 2019", "Jan. 2024", "941K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545192598'>xlsx</a> (172 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018", "Nov. 2023", "929K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541465248'>xlsx</a> (158 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018", "Jan. 2024", "904K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550118061'>xlsx</a> (165 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", "Nov. 2023", "781K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537006671'>xlsx</a> (132 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", "Jan. 2024", "757K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545300833'>xlsx</a> (139 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", "Nov. 2023", "772K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836547134723'>xlsx</a> (132 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", "Jan. 2024", "748K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551270304'>xlsx</a> (138 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", "Nov. 2023", "684K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538472510'>xlsx</a> (117 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", "Jan. 2024", "655K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545212556'>xlsx</a> (120 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014", "Nov. 2023", "823K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538338110'>xlsx</a> (149 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014", "Jan. 2024", "849K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270445'>xlsx</a> (157 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", "Nov. 2023", "868K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543474267'>xlsx</a> (149 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", "Jan. 2024", "877K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539896765'>xlsx</a> (163 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", "Nov. 2023", "1M", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551063854'>xlsx</a> (172 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", "Jan. 2024", "988K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538890174'>xlsx</a> (180 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011", "Jan. 2024", "60K", "<a href='https://github.com/UWCHR/ice-detain'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558695933'>xlsx</a> (12 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "665K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=44f2y370xd1ux27du97v2balb53ljp25&file_id=f_1851667352417'>xlsx</a> (241 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", NA, "764K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=knu38istxecn9cznprv8x5y7go4yy89x&file_id=f_1851662838490'>xlsx</a> (278 MB)",
  "Oct. 1, 2016", "Aug. 18, 2017", NA, "692K", "<a href='https://www.ccgarciahernandez.com'>César Cuauhtémoc García Hernández</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=u5knyff3u0gzl1gnobt3dshd40y0fnyb&file_id=f_1851661107897'>xlsx</a> (252 MB)"
) |> 
    reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Encounters

This dataset records each encounter that an ICE officer had with someone, whether or not that encounter resulted in an arrest.

```{r}
tibble::tribble(
  ~Start, ~End,  ~Identifiers, ~Records, ~Source,~Download,
  # edit to have the new data
  "Sep. 2023", "Early Jun. 2025", "Jun. 2025", "1.24M", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/ohg6tz7uzp93cljg1yhhsn46jfodh3i9.xlsx'>xlsx</a> (142 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>


<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Mid Nov. 2023", "Mid Feb. 2025", "Mar. 2025", "869K", "<a href='https://www.ice.gov'>ICE</a>",  "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544630925'>xlsx</a> (112 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "3M", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539886526'>xlsx</a> (163 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", NA, "2M", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545587160'>xlsx</a> (97 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Flights

Data on ICE-operated charter flights and passenger manifests. Flight data are at the "flight mission" level, meaning that each row represents one or more flight segments, distinguished in columns that report on each flight segment. Passenger data are at the individual passenger level, meaning that each row represents a single passenger on a flight. Individual identifiers are not relevant for the flight data; ICE has not provided data with identifiers for the passenger data.

```{r}
tibble::tribble(
  ~Description, ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Flight missions", "Oct. 1, 2018", "May. 8, 2020", "--", "3K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545668509'>xlsx</a> (460 kB)",
  "Passengers", "Oct. 1, 2018", "May. 8, 2020", NA, "341K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550007406'>xlsx</a> (55 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>


<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Description, ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Flight missions", "Oct. 1, 2018", "Sep. 30, 2019", "--", "1K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537162853'>xlsx</a> (188 kB)",
  "Passengers", "Oct. 1, 2018", "Sep. 30, 2019", NA, "37K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536207751'>xlsx</a> (6 MB)",
  "Flight missions", "Oct. 1, 2017", "Sep. 30, 2018", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550883008'>xlsx</a> (246 kB)",
  "Passengers", "Oct. 1, 2017", "Sep. 30, 2018", NA, "192K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836553076817'>xlsx</a> (28 MB)",
  "Flight missions", "Oct. 1, 2016", "Sep. 30, 2017", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549806043'>xlsx</a> (240 kB)",
  "Passengers", "Oct. 1, 2016", "Sep. 30, 2017", NA, "180K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541672269'>xlsx</a> (27 MB)",
  "Flight missions", "Oct. 1, 2015", "Sep. 30, 2016", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536493019'>xlsx</a> (273 kB)",
  "Passengers", "Oct. 1, 2015", "Sep. 30, 2016", NA, "168K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549772221'>xlsx</a> (25 MB)",
  "Flight missions", "Oct. 1, 2014", "Sep. 30, 2015", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538695921'>xlsx</a> (226 kB)",
  "Passengers", "Oct. 1, 2014", "Sep. 30, 2015", NA, "157K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539073027'>xlsx</a> (23 MB)",
  "Flight missions", "Oct. 1, 2013", "Sep. 30, 2014", "--", "6K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540958981'>xlsx</a> (642 kB)",
  "Passengers", "Oct. 1, 2013", "Sep. 30, 2014", NA, "250K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545751933'>xlsx</a> (37 MB)",
  "Flight missions", "Oct. 1, 2012", "Sep. 30, 2013", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549849021'>xlsx</a> (311 kB)",
  "Passengers", "Oct. 1, 2012", "Sep. 30, 2013", NA, "264K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555001702'>xlsx</a> (40 MB)",
  "Flight missions", "Oct. 1, 2011", "Sep. 30, 2012", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552599950'>xlsx</a> (322 kB)",
  "Passengers", "Oct. 1, 2011", "Sep. 30, 2012", NA, "282K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538136812'>xlsx</a> (44 MB)",
  "Flight missions", "Oct. 1, 2010", "Sep. 30, 2011", "--", "2K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540049661'>xlsx</a> (265 kB)",
  "Passengers", "Oct. 1, 2010", "Sep. 30, 2011", NA, "233K", "<a href='https://github.com/UWCHR/ice-air'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536399014'>xlsx</a> (36 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Removals (deportations)

This dataset includes a row for every removal (deportation) that ICE conducted. Note that individuals can be returned or expelled by CBP at the border without appearing in this dataset. 

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  # edit to have the new data
  "Jan. 1, 2025", "Early Jun. 2025", "Jun. 2025", "106K", "<a href='https://www.ice.gov'>ICE</a>", "<a href='https://ucla.box.com/shared/static/li1sep40gui5dj09izhh8kzr4bajqyon.xlsx'>xlsx</a> (25 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

::: {.callout-warning}

The removals dataset from the June 2025 ICE release only includes records from Jan. 1, 2025 onward because the records from before Jan. 1, 2025 appeared to have significant errors. Although we have not found obvious errors in the later records, which we have posted, the errors in the earlier records lead us to advise caution when using the removals data table. If you find other errors, please let us know. We are actively seeking data for the full period.

:::

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Oct. 1, 2019", "Sep. 30, 2023", "Nov. 2023", "454K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552901309'>xlsx</a> (85 MB)",
  "Oct. 1, 2016", "Sep. 30, 2019", "Nov. 2023", "752K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537875130'>xlsx</a> (137 MB)",
  "Oct. 1, 2013", "Sep. 30, 2016", "Nov. 2023", "793K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836543019179'>xlsx</a> (143 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", NA, "2M", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555735995'>xlsx</a> (95 MB)",
  "Oct. 1, 2011", "Sep. 30, 2013", "Nov. 2023", "773K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836542804617'>xlsx</a> (139 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", NA, "1M", "<a href='https://github.com/UWCHR/ice-enforce'>UWCHR</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836557461924'>xlsx</a> (60 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013",           NA,   "369K",   "<a href='https://www.ice.gov'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875139943394'>xlsx</a> (82 MB)",

  # nytimes data
  "Oct. 1, 2011", "Sep. 30, 2012",           NA,   "410K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875139734735'>xlsx</a> (88 MB)",
  "Oct. 1, 2010", "Sep. 30, 2011",           NA,   "396K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875127271383'>xlsx</a> (85 MB)",
  "Oct. 1, 2009", "Sep. 30, 2010",           NA,   "392K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875138789538'>xlsx</a> (84 MB)",
  "Oct. 1, 2008", "Sep. 30, 2009",           NA,   "385K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875137637027'>xlsx</a> (82 MB)",
  "Oct. 1, 2007", "Sep. 30, 2008",           NA,   "384K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875130303126'>xlsx</a> (79 MB)",
  "Oct. 1, 2006", "Sep. 30, 2007",           NA,   "300K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875129774679'>xlsx</a> (62 MB)",
  "Oct. 1, 2005", "Sep. 30, 2006",           NA,   "212K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875129589363'>xlsx</a> (44 MB)",
  "Oct. 1, 2004", "Sep. 30, 2005",           NA,   "184K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875135429164'>xlsx</a> (38 MB)",
  "Oct. 1, 2003", "Sep. 30, 2004",           NA,   "178K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875132208001'>xlsx</a> (37 MB)",
  "Oct. 1, 2002", "Sep. 30, 2003",           NA,   "160K",   "<a href='https://www.nytimes.com'>NYT</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1875129596640'>xlsx</a> (34 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## Risk classification assessments

This dataset shows information on each risk classification assessment (RCA)–the procedure used by ICE to determine danger and flight risk. Note that the RCA tool is used both to help ICE officers decide whether to detain or release a person and to determine risk levels for detention (see the `rca_decision_type` field). 


```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Oct. 1, 2022", "Sep. 30, 2023", "Nov. 2023", "330K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551596696'>xlsx</a> (58 MB)",
  "Oct. 1, 2021", "Sep. 30, 2022", "Nov. 2023", "347K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544905050'>xlsx</a> (60 MB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE, sortable = FALSE)
```

<div style="margin-top: 0.5em;"></div>


<details>
<summary>Show past datasets</summary>

```{r}
tibble::tribble(
  ~Start, ~End, ~Identifiers, ~Records, ~Source, ~Download,
  "Oct. 1, 2020", "Sep. 30, 2021", "Nov. 2023", "207K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836549849007'>xlsx</a> (36 MB)",
  "Oct. 1, 2019", "Sep. 30, 2020", "Nov. 2023", "83K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554341800'>xlsx</a> (22 MB)",
  "Oct. 1, 2018", "Sep. 30, 2019", "Nov. 2023", "435K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540750526'>xlsx</a> (77 MB)",
  "Oct. 1, 2017", "Sep. 30, 2018", "Nov. 2023", "433K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552112243'>xlsx</a> (77 MB)",
  "Oct. 1, 2016", "Sep. 30, 2017", "Nov. 2023", "393K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539522069'>xlsx</a> (70 MB)",
  "Oct. 1, 2015", "Sep. 30, 2016", "Nov. 2023", "353K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552159782'>xlsx</a> (63 MB)",
  "Oct. 1, 2014", "Sep. 30, 2015", "Nov. 2023", "273K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554502095'>xlsx</a> (49 MB)",
  "Oct. 1, 2013", "Sep. 30, 2014", "Nov. 2023", "368K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546882084'>xlsx</a> (66 MB)",
  "Oct. 1, 2012", "Sep. 30, 2013", "Nov. 2023", "320K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546882337'>xlsx</a> (63 MB)",
  "Oct. 1, 2011", "Sep. 30, 2012", "Nov. 2023", "2K", "<a href='https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540294710'>xlsx</a> (432 kB)"
) |>
  reactable::reactable(columns = col_defs_ice, pagination = FALSE)
```

</details>

## About ICE data releases {#sec-about}

In the table below, we enumerate each ICE data release, what data was produced, and whether there are identifiers. We provide the vintage of the identifiers in each table of data downloads above. Note that identifiers do not match across releases. Read more about the data in our [ICE data documentation](/docs/ice.html).

```{r}
#| tbl-caption: Data releases by ICE.
tibble::tribble(
  ~Agency, ~`FOIA request`, ~Date, ~Types, ~Identifiers, ~source_label, ~source_URL,
  "ICE", "2024-ICFO-39357", "Jun. 2025", "Arrests, Detainers, Detentions, Encounters, Removals", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2024-ICFO-39357", "Mar. 2025", "Arrests, Detainers, Detentions, Encounters", "Yes", "ICE", "https://www.ice.gov",
  "ICE", "2022-ICFO-22955", "Jul. 2024", "Arrests", "Yes", "García Hernández", "https://www.ccgarciahernandez.com",
  "ICE", "2022-ICFO-09022", "Jan. 2024", "Detentions", "Yes", "UWCHR", "https://github.com/UWCHR/ice-detain",
  "ICE", "2023-ICFO-42034", "Nov. 2023", "Arrests, Detentions, Removals, Risk classification assessments", "Feb. 2024", "ICE", "https://www.ice.gov/doclib/foia/thirdPartyRequests/2023-ICFO-42034.zip",
  "ICE", "2022-ICFO-09023", "Mar. 2023, Apr. 2023", "Arrests, Encounters, Removals", NA, "UWCHR", "https://github.com/UWCHR/ice-enforce",
  "ICE", "2021-ICAP-00188", "2022", "Flights", NA, "UWCHR", "https://github.com/UWCHR/ice-air",
  "ICE", "2019-ICFO-32423", "2019", "Flights", NA, "UWCHR", "https://github.com/UWCHR/ice-air",
  "ICE", "2019-ICFO-21307", "Aug. 2017", "Detentions", NA, "García Hernández", "https://www.ccgarciahernandez.com",
  "ICE", "Unknown", "2016", "Detainers", NA, "NPR", "https://github.com/nprapps/sanctuary-cities",
  "ICE", "14-03290", "2014", "Removals", NA, "NYT", "https://nytimes.com"
) |>
  mutate(Source = glue::glue("<a href='{source_URL}'>{source_label}</a>"), .keep = "unused") |>
  transmute(Date, Types, Identifiers, Source, `FOIA request`) |>
  reactable::reactable(pagination = FALSE, sortable = FALSE, resizable = FALSE, columns = list(
    Date = colDef(minWidth = 55),
    Types = colDef(minWidth = 150),
    Identifiers = colDef(
      minWidth = 55,
      cell = function(value) {
        icon <- if (is.na(value)) "xmark" else "check"
        color <- if (is.na(value)) "red" else "green"

        htmltools::tags$div(
          style = "display: flex; align-items: center; gap: 6px;",
          htmltools::tags$i(
            class = paste("fas", paste0("fa-", icon)),
            style = paste("color:", color, "; font-size: 1.2em;")
          )
        )
      }
    ),
    Source = colDef(minWidth = 55, html = TRUE)
  ))
```

