---
title: "Agency report repository"
---

```{r}
library(tidyverse)
library(reactable)
library(htmltools)

col_defs <- list(
  Start = colDef(
    minWidth = 75,
    cell = function(value) {
      if (is.null(value) || is.na(value)) {
        return("")
      }
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  End = colDef(
    minWidth = 75,
    cell = function(value) {
      if (is.null(value) || is.na(value)) {
        return("")
      }
      format(as.Date(value), "%b. %-d, %Y")
    }
  ),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(
    minWidth = 100,
    html = TRUE,
    cell = function(value) {
      if (is.null(value) || length(value) == 0) {
        return("&ndash;") # en dash
      }

      url <- as.character(value[[1]])
      size <- as.character(value[[2]])
      ext <- tolower(trimws(as.character(value[[3]])))

      paste0(
        "<a href='",
        url,
        "'>",
        "<img src='/img/",
        ext,
        ".svg' width=25 height=25 alt='",
        ext,
        "'>",
        "</a>"
        # " (",
        # size,
        # ")"
      )
    }
  )
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

Our project's focus is on collecting and posting individual-level data, but this page is an exception: here, we collect and repost government reports that draw from the individual-level datasets we post. We hope that this centralized repository of reports (and links to government websites) will help users of the individual-level data.  

The reports come from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Protection (CBP), and the Executive Office of Immigration Review (EOIR). These reports are generally available for download from the government directly; we repost them for users' convenience. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the reports before we have, we link to their sites as the source.


## Immigration and Customs Enforcement

### Detention management spreadsheet

ICE releases a spreadsheet about twice a month that tracks book-ins, case types, detention facility information, and other descriptive statistics related to detention. 

```{r}
ice_detention_management_ytd_files <-
  tibble::tribble(
    ~Start                                                                                                                                                        ,
    ~End                                                                                                                                                          ,
    ~Source                                                                                                                                                       ,
    ~Download                                                                                                                                                     ,
    as.Date("2025-10-01")                                                                                                                                         ,
    as.Date("2025-11-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_2053638251632", "215 KB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-09-25")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1998729580163", "1.6 MB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-09-11")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984418543821", "1.6 MB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-08-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984423132721", "1.6 MB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-08-14")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/eouwbvfx7x7tosqws4j4w6trbmw5smv9.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-08-01")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/lra9r9p038hsze5ngqzwqzwgqiqatoyr.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-07-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/m4cyew6nyiizbmi00ysop1n5d1a97q8t.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-07-07")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/7z4bmopvk5ww9uqutgw1pytupltj9hbe.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-06-20")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/86rndu1ry7sy50ot76nymgyopged3p4s.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-06-06")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/hvkcf6dg6o33ndywk2e769kdkzdc6cao.xlsx", "1.5 MB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-05-23")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/5l1cjsg7m5z1jymfuuvl7r9khoc9klnj.xlsx", "237 kB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-05-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/0qda0lokm4pkdmpapdt0z7196ocn5nd5.xlsx", "235 kB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-05-09")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.box.com/shared/static/ao6qved0fhe9l4a1dw17m6z2txluuu2s.xlsx", "229 kB", "xlsx")                                                            ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-04-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552829382", "232 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-03-26")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554085594", "227 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-03-14")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541591004", "223 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-03-05")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550259001", "217 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-02-27")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540128756", "225 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-02-14")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552563416", "219 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-02-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545131055", "213 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-01-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555985237", "219 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2025-01-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551099839", "216 kB", "xlsx") ,

    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2024-12-18")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554106108", "233 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2024-12-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548019897", "226 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2024-12-11")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546642190", "232 kB", "xlsx") ,
    as.Date("2024-10-01")                                                                                                                                         ,
    as.Date("2024-11-21")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555637335", "255 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-11-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941072318562", "264 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-09-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941077817551", "239 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-08-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082436598", "242 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-08-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081969293", "288 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-07-18")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941083200417", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-07-08")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085786880", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-06-20")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941084004584", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-06-06")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941080010085", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-05-24")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085247212", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-05-13")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086522189", "252 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-04-25")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082211453", "218 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-04-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074375974", "218 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-03-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082281029", "217 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-03-14")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941076962190", "216 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-02-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074359174", "215 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-02-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082190380", "215 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-02-01")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081416603", "217 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-01-11")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086543044", "208 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-01-04")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086997347", "206 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2023-12-20")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908777252", "208 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2023-12-07")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913075897", "208 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2023-11-22")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906505313", "225 kB", "xlsx") ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2023-11-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485", "224 kB", "xlsx") ,

    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2023-11-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485", "224 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-07-20")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911251765", "207 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-06-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909284347", "204 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-07-10")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913817260", "207 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-08-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907013367", "207 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-08-18")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906301076", "208 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-08-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915962929", "208 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-06-01")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905014976", "206 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-05-19")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905813740", "204 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-05-26")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906754538", "204 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-05-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913697446", "206 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-04-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912051015", "203 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-04-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909751864", "203 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-03-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912113859", "199 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-03-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909586300", "198 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-02-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915190064", "199 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-02-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910738664", "199 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-01-09")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916580593", "207 kB", "xlsx") ,

    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-12-22")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940920797250", "194 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-12-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906831784", "195 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-12-07")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911184737", "194 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-12-06")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912552762", "170 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-11-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911484515", "196 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-11-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911060682", "191 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-10-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908029365", "234 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-09-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907570429", "210 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-09-25")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911763830", "209 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-08-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906478053", "177 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-08-19")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905467769", "177 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-08-09")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919155877", "190 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-08-04")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906991764", "190 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-09-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906997367", "197 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-09-15")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910892078", "205 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-07-21")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911010158", "173 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-07-08")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940903910232", "165 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-06-27")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915903684", "167 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-06-23")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911364962", "161 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-06-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940914302649", "161 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-06-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907911462", "163 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-06-09")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919738187", "156 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-05-24")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911194243", "154 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-05-04")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912850610", "160 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-04-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905778014", "158 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-04-13")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911988538", "150 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-03-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912303490", "149 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-03-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906948837", "150 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-03-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907755224", "200 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-03-02")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906572276", "145 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-02-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910321525", "169 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-01-20")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910950158", "144 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2022-01-11")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912048442", "213 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-01-10")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907136043", "127 kB", "xlsx") ,

    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2021-12-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912536107", "141 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-11-12")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909020231", "134 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-10-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913162043", "128 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-10-07")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907496257", "147 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-10-01")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912123545", "149 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-09-16")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919802973", "149 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-09-13")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919440819", "147 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-08-24")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919320598", "140 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-08-06")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913342084", "147 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-07-22")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908650485", "140 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-07-08")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907771615", "138 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-06-24")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916407415", "137 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-06-11")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916241709", "136 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-06-09")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912953557", "129 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-05-28")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909887031", "130 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-05-13")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913297574", "133 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-05-03")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908021660", "132 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-04-29")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915947115", "132 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-04-14")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913894081", "131 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-03-31")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916285575", "127 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-03-17")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912962867", "127 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-03-01")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940904921171", "125 kB", "xlsx")
  )
```

#### Year-to-date:

```{r}
ice_detention_management_ytd_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = col_defs$Start,
      End = col_defs$End,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ytd_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = col_defs$Start,
      End = col_defs$End,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

\* The fiscal year and the dates in this file are inconsistent and we do not know which are correct.

</details>

#### End-of-fiscal-year:

```{r}
ice_detention_management_ay_files <-
  tibble::tribble(
    ~Start                                                                                                                                                        ,
    ~End                                                                                                                                                          ,
    ~Source                                                                                                                                                       ,
    ~Download                                                                                                                                                     ,
    as.Date("2023-10-01")                                                                                                                                         ,
    as.Date("2024-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537358917", "242 kB", "xlsx") ,
    as.Date("2022-10-01")                                                                                                                                         ,
    as.Date("2023-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545074923", "234 kB", "xlsx") ,
    as.Date("2021-10-01")                                                                                                                                         ,
    as.Date("2022-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537940671", "196 kB", "xlsx") ,
    as.Date("2020-10-01")                                                                                                                                         ,
    as.Date("2021-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552983586", "134 kB", "xlsx") ,
    as.Date("2019-10-01")                                                                                                                                         ,
    as.Date("2020-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270675", "136 kB", "xlsx") ,
    as.Date("2018-10-01")                                                                                                                                         ,
    as.Date("2019-09-30")                                                                                                                                         ,
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>"                                                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538549260", "132 kB", "xlsx")
  )
```

```{r}
ice_detention_management_ay_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = col_defs$Start,
      End = col_defs$End,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ay_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = col_defs$Start,
      End = col_defs$End,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Dedicated and non-dedicated detention facilities

ICE published through late 2024 a list of its dedicated and non-dedicated detention facilities, including a set of facility characteristics, on a roughly monthly basis. We do not know whether the data are up-to-date. 

```{r}
dedicated_nondedicated_files <-
  tibble::tribble(
    ~Date      ,
    ~Download  ,
    "8/28/18"  , 2049613645447 ,
    "9/1/18"   , 2049599236037 ,
    "9/17/18"  , 2049610285442 ,
    "10/17/18" , 2049608423072 ,
    "1/30/19"  , 2049609229988 ,
    "2/16/19"  , 2049595077412 ,
    "3/16/19"  , 2049612690286 ,
    "4/29/19"  , 2049610339103 ,
    "5/16/19"  , 2049600234253 ,
    "6/18/19"  , 2049613473568 ,
    "7/18/19"  , 2049607425129 ,
    "8/15/19"  , 2049604442397 ,
    "10/16/19" , 2049603598812 ,
    "11/17/19" , 2049601206633 ,
    "12/17/19" , 2049602948705 ,
    "1/16/20"  , 2049594834051 ,
    "2/19/20"  , 2049614032667 ,
    "3/13/20"  , 2049600635158 ,
    "4/15/20"  , 2049597424018 ,
    "5/13/20"  , 2049597884814 ,
    "5/13/20"  , 2049597884814 ,
    "6/11/20"  , 2049601182469 ,
    "7/14/20"  , 2049605524315 ,
    "8/15/20"  , 2049603851324 ,
    "9/19/20"  , 2049598358171 ,
    "10/28/20" , 2049598876499 ,
    "12/17/20" , 2049607266382 ,
    "1/20/21"  , 2049600501583 ,
    "2/18/21"  , 2049611826419 ,
    "3/18/21"  , 2049594796612 ,
    "3/18/21"  , 2049594796612 ,
    "3/19/21"  , 2049604062885 ,
    "4/16/21"  , 2049601146784 ,
    "5/12/21"  , 2049598204014 ,
    "6/16/21"  , 2049600311088 ,
    "7/16/21"  , 2049601050745 ,
    "8/14/21"  , 2049603774067 ,
    "9/17/21"  , 2049598583002 ,
    "11/23/21" , 2049593737456 ,
    "12/17/21" , 2049603551256 ,
    "1/24/22"  , 2049599439642 ,
    "2/20/22"  , 2049598818835 ,
    "3/21/22"  , 2049609974303 ,
    "4/18/22"  , 2049599860295 ,
    "5/26/22"  , 2049610650074 ,
    "6/25/22"  , 2049609052024 ,
    "8/1/22"   , 2049613648113 ,
    "8/23/22"  , 2049612153222 ,
    "9/24/22"  , 2049595054851 ,
    "10/27/22" , 2049594526950 ,
    "11/9/23"  , 2049609589213 ,
    "11/16/23" , 2049611543776 ,
    "11/16/23" , 2049611543776 ,
    "12/16/23" , 2049603366428 ,
    "1/17/24"  , 2049601252069 ,
    "2/16/24"  , 2049613221287 ,
    "3/13/24"  , 2049603755578 ,
    "4/13/24"  , 2049596152423 ,
    "4/13/24"  , 2049596152423 ,
    "6/12/24"  , 2049594894097 ,
    "7/19/24"  , 2049596786251 ,
    "11/13/24" , 2049601281540
  ) |>
  mutate(
    Date = mdy(Date),
    Source = "<a href='https://www.ice.gov/detain/facility-inspections'>ICE</a>",
    Download = map(
      Download,
      ~ list(
        glue::glue(
          "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_{.x}"
        ),
        "NA kB",
        "xlsx"
      )
    )
  ) |>
  relocate(Date, Source, Download) |>
  arrange(desc(Date))
```

```{r}
dedicated_nondedicated_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = col_defs$Start,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
dedicated_nondedicated_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = col_defs$Start,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Over-72-hour detention facilities

ICE published a list of facilities authorized to hold adult (non-family) detainees for longer than 72 hours. The latest file was published in January 2020, and it is not clear if it still up-to-date.

```{r}
over72_files <-
  tibble::tribble(
    ~Date     ,
    ~Download ,
    "5/2/19"  , 2049603267601 ,
    "6/11/19" , 2049600609095 ,
    "1/13/20" , 2049599555688
  ) |>
  mutate(
    Date = mdy(Date),
    Source = "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    Download = map(
      Download,
      ~ list(
        glue::glue(
          "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_{.x}"
        ),
        "NA kB",
        "xlsx"
      )
    )
  ) |>
  relocate(Date, Source, Download) |>
  arrange(desc(Date))
```

```{r}
over72_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = col_defs$Start,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
over72_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = col_defs$Start,
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Annual report

ICE compiles a variety of descriptive statistics in its annual report.

```{r}
ice_annual_reports_files <-
  tibble::tribble(
    ~Date                                                                                                                                                      ,
    ~Source                                                                                                                                                    ,
    ~Download                                                                                                                                                  ,
    "2024"                                                                                                                                                     ,
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>"                                                                                  ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539286110", "3 MB", "pdf") ,
    "2023"                                                                                                                                                     ,
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>"                                                                                  ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544782511", "4 MB", "pdf") ,
    "2022"                                                                                                                                                     ,
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>"                                                                                  ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554989243", "6 MB", "pdf") ,
    "2021"                                                                                                                                                     ,
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>"                                                                                  ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555047424", "7 MB", "pdf") ,
    "2020"                                                                                                                                                     ,
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>"                                                                                  ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556005548", "3 MB", "pdf")
  )
```

```{r}
ice_annual_reports_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Detention facility list

ICE released a list of detention facilities in 2017. These data include a facility identifier that can be joined with ICE detention data.

```{r}
tribble(
  ~Date                                                                                                                                                       ,
  ~Source                                                                                                                                                     ,
  ~Download                                                                                                                                                   ,
  as.Date("2017-11-06")                                                                                                                                       ,
  "<a href='https://immigrantjustice.org/ice-detention-facilities-november-2017'>NIJC</a>"                                                                    ,
  list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538055645", "2 MB", "xlsx")
) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

## Customs and Border Protection 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Southwest Land Border Encounters](https://www.cbp.gov/newsroom/stats/southwest-land-border-encounters)
: Dashboard tracking encounters along the southern border at and between ports of entry.

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Statistics covering many aspects of CBP's enforcement actions.

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
: Statistics tracking detention and outcomes after border encounters at and between ports of entry.

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a set of [court workload and adjudication statistics](https://www.justice.gov/eoir/workload-and-adjudication-statistics).

## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

Through January 2025, the Office of Homeland Security Statistics released a monthly spreadsheet tracking a variety of actions by both CBP and ICE. We do not know whether to expect future releases.

```{r}
enf_files <-
  tibble::tribble(
    ~Date                                                                                                                                                         ,
    ~Source                                                                                                                                                       ,
    ~Download                                                                                                                                                     ,
    "Jan. 2025"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538278882", "712 kB", "xlsx") ,
    "Dec. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538669625", "671 kB", "xlsx") ,
    "Nov. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532468031", "668 kB", "xlsx") ,
    "Oct. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522683414", "678 kB", "xlsx") ,
    "Sep. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537352654", "673 kB", "xlsx") ,
    "Aug. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538234805", "669 kB", "xlsx") ,
    "Jul. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534182041", "666 kB", "xlsx") ,
    "Jun. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521399297", "653 kB", "xlsx") ,
    "May. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532585571", "644 kB", "xlsx") ,
    "Apr. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535261459", "478 kB", "xlsx") ,
    "Mar. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530651460", "406 kB", "xlsx") ,
    "Feb. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524668163", "407 kB", "xlsx") ,
    "Jan. 2024"                                                                                                                                                   ,
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>"                                                           ,
    list("https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536929304", "401 kB", "xlsx")
  )
```

```{r}
enf_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
enf_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

