---
title: "Agency report repository"
---

```{r}
library(tidyverse)
library(reactable)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

Our project's focus is on collecting and posting individual-level data, but this page is an exception: here, we collect and repost government reports that draw from the individual-level datasets we post. We hope that this centralized repository of reports (and links to government websites) will help users of the individual-level data.  

The reports come from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Protection (CBP), and the Executive Office of Immigration Review (EOIR). These reports are generally available for download from the government directly; we repost them for users' convenience. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the reports before we have, we link to their sites as the source.


## Immigration and Customs Enforcement


```{r}
col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)
```


### Detention management spreadsheet

ICE releases a spreadsheet about twice a month that tracks book-ins, case types, detention facility information, and other descriptive statistics related to detention. 

```{r}
ice_detention_management_ytd_files <-
  tibble::tribble(
            ~Start,             ~End,                                                             ~Source,                                                                                                                                                         ~Download,
    "Oct. 1, 2024",  "Sep. 25, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1998729580163'>xlsx</a> (1.6 MB)",
    "Oct. 1, 2024",  "Sep. 11, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984418543821'>xlsx</a> (1.6 MB)",
    "Oct. 1, 2024",  "Aug. 29, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984423132721'>xlsx</a> (1.6 MB)",
    "Oct. 1, 2024",  "Aug. 14, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/eouwbvfx7x7tosqws4j4w6trbmw5smv9.xlsx'>xlsx</a> (1.5 MB)",
	"Oct. 1, 2024",  "Aug. 1, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/lra9r9p038hsze5ngqzwqzwgqiqatoyr.xlsx'>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",  "Jul. 17, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/m4cyew6nyiizbmi00ysop1n5d1a97q8t.xlsx'>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",  "Jul. 7, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/7z4bmopvk5ww9uqutgw1pytupltj9hbe.xlsx'>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",  "Jun. 20, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/86rndu1ry7sy50ot76nymgyopged3p4s.xlsx'>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",   "Jun. 6, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/hvkcf6dg6o33ndywk2e769kdkzdc6cao.xlsx'>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",   "May 23, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/5l1cjsg7m5z1jymfuuvl7r9khoc9klnj.xlsx'>xlsx</a> (237 kB)",
    "Oct. 1, 2024",   "May 12, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/0qda0lokm4pkdmpapdt0z7196ocn5nd5.xlsx'>xlsx</a> (235 kB)",
    "Oct. 1, 2024",   "May 9, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.box.com/shared/static/ao6qved0fhe9l4a1dw17m6z2txluuu2s.xlsx'>xlsx</a> (229 kB)",
    "Oct. 1, 2024",  "Apr. 16, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552829382'>xlsx</a> (232 kB)",
    "Oct. 1, 2024",  "Mar. 26, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554085594'>xlsx</a> (227 kB)",
    "Oct. 1, 2024",  "Mar. 14, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541591004'>xlsx</a> (223 kB)",
    "Oct. 1, 2024",   "Mar. 5, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550259001'>xlsx</a> (217 kB)",
    "Oct. 1, 2024",  "Feb. 27, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540128756'>xlsx</a> (225 kB)",
    "Oct. 1, 2024",  "Feb. 14, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552563416'>xlsx</a> (219 kB)",
    "Oct. 1, 2024",   "Feb. 3, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545131055'>xlsx</a> (213 kB)",
    "Oct. 1, 2024",  "Jan. 16, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555985237'>xlsx</a> (219 kB)",
    "Oct. 1, 2024",   "Jan. 3, 2025", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551099839'>xlsx</a> (216 kB)",
    
    "Oct. 1, 2024",  "Dec. 18, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554106108'>xlsx</a> (233 kB)",
    "Oct. 1, 2024",  "Dec. 12, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548019897'>xlsx</a> (226 kB)",
    "Oct. 1, 2024",  "Dec. 11, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546642190'>xlsx</a> (232 kB)",
    "Oct. 1, 2024",  "Nov. 21, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555637335'>xlsx</a> (255 kB)",
		"Oct. 1, 2023", "Nov. 15, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941072318562'>xlsx</a> (264 kB)",
		"Oct. 1, 2023", "Sep. 17, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941077817551'>xlsx</a> (239 kB)",
		"Oct. 1, 2023", "Aug. 29, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082436598'>xlsx</a> (242 kB)",
		"Oct. 1, 2023", "Aug. 15, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081969293'>xlsx</a> (288 kB)",
		"Oct. 1, 2023", "Jul. 18, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941083200417'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "Jul. 8, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085786880'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "Jun. 20, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941084004584'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "Jun. 6, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941080010085'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "May 24, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085247212'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "May 13, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086522189'>xlsx</a> (252 kB)",
		"Oct. 1, 2023", "Apr. 25, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082211453'>xlsx</a> (218 kB)",
		"Oct. 1, 2023", "Apr. 12, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074375974'>xlsx</a> (218 kB)",
		"Oct. 1, 2023", "Mar. 29, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082281029'>xlsx</a> (217 kB)",
		"Oct. 1, 2023", "Mar. 14, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941076962190'>xlsx</a> (216 kB)",
		"Oct. 1, 2023", "Feb. 29, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074359174'>xlsx</a> (215 kB)",
		"Oct. 1, 2023", "Feb. 15, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082190380'>xlsx</a> (215 kB)",
		"Oct. 1, 2023", "Feb. 1, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081416603'>xlsx</a> (217 kB)",
		"Oct. 1, 2023", "Jan. 11, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086543044'>xlsx</a> (208 kB)",
		"Oct. 1, 2023", "Jan. 4, 2024", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086997347'>xlsx</a> (206 kB)",
		"Oct. 1, 2023", "Dec. 20, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908777252'>xlsx</a> (208 kB)",
		"Oct. 1, 2023", "Dec. 7, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913075897'>xlsx</a> (208 kB)",
		"Oct. 1, 2023", "Nov. 22, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906505313'>xlsx</a> (225 kB)",
		"Oct. 1, 2023", "Nov. 15, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485'>xlsx</a> (224 kB)",

    "Oct. 1, 2023", "Dec. 20, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908777252'>xlsx</a> (208 kB)",
		"Oct. 1, 2023", "Dec. 7, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913075897'>xlsx</a> (208 kB)",
		"Oct. 1, 2023", "Nov. 22, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906505313'>xlsx</a> (225 kB)",
    "Oct. 1, 2023", "Nov. 15, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485'>xlsx</a> (224 kB)",
		"Oct. 1, 2022", "Jul. 20, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911251765'>xlsx</a> (207 kB)",
		"Oct. 1, 2022", "Jun. 12, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909284347'>xlsx</a> (204 kB)",
		"Oct. 1, 2022", "Jul. 10, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913817260'>xlsx</a> (207 kB)",
		"Oct. 1, 2022", "Aug. 31, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907013367'>xlsx</a> (207 kB)",
		"Oct. 1, 2022", "Aug. 18, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906301076'>xlsx</a> (208 kB)",
		"Oct. 1, 2022", "Aug. 3, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915962929'>xlsx</a> (208 kB)",
		"Oct. 1, 2022", "Jun. 1, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905014976'>xlsx</a> (206 kB)",
		"Oct. 1, 2022", "May 19, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905813740'>xlsx</a> (204 kB)",
		"Oct. 1, 2022", "May 26, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906754538'>xlsx</a> (204 kB)",
		"Oct. 1, 2022", "May 31, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913697446'>xlsx</a> (206 kB)",
		"Oct. 1, 2022", "Apr. 12, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912051015'>xlsx</a> (203 kB)",
		"Oct. 1, 2022", "Apr. 28, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909751864'>xlsx</a> (203 kB)",
		"Oct. 1, 2022", "Mar. 31, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912113859'>xlsx</a> (199 kB)",
		"Oct. 1, 2022", "Mar. 3, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909586300'>xlsx</a> (198 kB)",
		"Oct. 1, 2022", "Feb. 28, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915190064'>xlsx</a> (199 kB)",
		"Oct. 1, 2022", "Feb. 3, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910738664'>xlsx</a> (199 kB)",
		"Oct. 1, 2022", "Jan. 9, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916580593'>xlsx</a> (207 kB)",
		
    "Oct. 1, 2022", "Dec. 22, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940920797250'>xlsx</a> (194 kB)",
		"Oct. 1, 2022", "Dec. 12, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906831784'>xlsx</a> (195 kB)",
		"Oct. 1, 2022", "Dec. 7, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911184737'>xlsx</a> (194 kB)",
		"Oct. 1, 2022", "Dec. 6, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912552762'>xlsx</a> (170 kB)",
		"Oct. 1, 2022", "Nov. 28, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911484515'>xlsx</a> (196 kB)",
		"Oct. 1, 2022", "Nov. 16, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911060682'>xlsx</a> (191 kB)",
		"Oct. 1, 2022", "Oct. 31, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908029365'>xlsx</a> (234 kB)",
		"Oct. 1, 2022", "Sep. 29, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907570429'>xlsx</a> (210 kB)",
		"Oct. 1, 2022", "Sep. 25, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911763830'>xlsx</a> (209 kB)",
		"Oct. 1, 2021", "Aug. 31, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906478053'>xlsx</a> (177 kB)",
		"Oct. 1, 2021", "Aug. 19, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905467769'>xlsx</a> (177 kB)",
		"Oct. 1, 2021", "Aug. 9, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919155877'>xlsx</a> (190 kB)",
		"Oct. 1, 2021", "Aug. 4, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906991764'>xlsx</a> (190 kB)",
		"Oct. 1, 2021", "Sep. 29, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906997367'>xlsx</a> (197 kB)",
		"Oct. 1, 2021", "Sep. 15, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910892078'>xlsx</a> (205 kB)",
		"Oct. 1, 2021", "Jul. 21, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911010158'>xlsx</a> (173 kB)",
		"Oct. 1, 2021", "Jul. 8, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940903910232'>xlsx</a> (165 kB)",
		"Oct. 1, 2021", "Jun. 27, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915903684'>xlsx</a> (167 kB)",
		"Oct. 1, 2021", "Jun. 23, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911364962'>xlsx</a> (161 kB)",
		"Oct. 1, 2021", "Jun. 17, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940914302649'>xlsx</a> (161 kB)",
		"Oct. 1, 2021", "Jun. 16, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907911462'>xlsx</a> (163 kB)",
		"Oct. 1, 2021", "Jun. 9, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919738187'>xlsx</a> (156 kB)",
		"Oct. 1, 2021", "May 24, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911194243'>xlsx</a> (154 kB)",
		"Oct. 1, 2021", "May 4, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912850610'>xlsx</a> (160 kB)",
		"Oct. 1, 2021", "Apr. 28, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905778014'>xlsx</a> (158 kB)",
		"Oct. 1, 2021", "Apr. 13, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911988538'>xlsx</a> (150 kB)",
		"Oct. 1, 2021", "Mar. 31, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912303490'>xlsx</a> (149 kB)",
		"Oct. 1, 2021", "Mar. 17, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906948837'>xlsx</a> (150 kB)",
		"Oct. 1, 2022", "Mar. 16, 2023", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907755224'>xlsx</a> (200 kB)",
		"Oct. 1, 2021", "Mar. 2, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906572276'>xlsx</a> (145 kB)",
		"Oct. 1, 2021", "Feb. 16, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910321525'>xlsx</a> (169 kB)",
		"Oct. 1, 2021", "Jan. 20, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910950158'>xlsx</a> (144 kB)",
		"Oct. 1, 2022", "Jan. 11, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912048442'>xlsx</a> (213 kB)*",
		"Oct. 1, 2021", "Jan. 10, 2022", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907136043'>xlsx</a> (127 kB)",
    
    "Oct. 1, 2021", "Dec. 29, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912536107'>xlsx</a> (141 kB)",
		"Oct. 1, 2020", "Nov. 12, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909020231'>xlsx</a> (134 kB)",
		"Oct. 1, 2020", "Oct. 28, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913162043'>xlsx</a> (128 kB)",
		"Oct. 1, 2020", "Oct. 7, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907496257'>xlsx</a> (147 kB)",
		"Oct. 1, 2020", "Oct. 1, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912123545'>xlsx</a> (149 kB)",
		"Oct. 1, 2020", "Sep. 16, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919802973'>xlsx</a> (149 kB)",
		"Oct. 1, 2020", "Sep. 13, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919440819'>xlsx</a> (147 kB)",
		"Oct. 1, 2020", "Aug. 24, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919320598'>xlsx</a> (140 kB)",
		"Oct. 1, 2020", "Aug. 6, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913342084'>xlsx</a> (147 kB)",
		"Oct. 1, 2020", "Jul. 22, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908650485'>xlsx</a> (140 kB)",
		"Oct. 1, 2020", "Jul. 8, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907771615'>xlsx</a> (138 kB)",
		"Oct. 1, 2020", "Jun. 24, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916407415'>xlsx</a> (137 kB)",
		"Oct. 1, 2020", "Jun. 11, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916241709'>xlsx</a> (136 kB)",
		"Oct. 1, 2020", "Jun. 9, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912953557'>xlsx</a> (129 kB)",
		"Oct. 1, 2020", "May 28, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909887031'>xlsx</a> (130 kB)",
		"Oct. 1, 2020", "May 13, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913297574'>xlsx</a> (133 kB)",
		"Oct. 1, 2020", "May 3, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908021660'>xlsx</a> (132 kB)",
		"Oct. 1, 2020", "Apr. 29, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915947115'>xlsx</a> (132 kB)",
		"Oct. 1, 2020", "Apr. 14, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913894081'>xlsx</a> (131 kB)",
		"Oct. 1, 2020", "Mar. 31, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916285575'>xlsx</a> (127 kB)",
		"Oct. 1, 2020", "Mar. 17, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912962867'>xlsx</a> (127 kB)",
		"Oct. 1, 2020", "Mar. 1, 2021", "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>", "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940904921171'>xlsx</a> (125 kB)"
  )
```

#### Year-to-date:

```{r}
ice_detention_management_ytd_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ytd_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

\* The fiscal year and the dates in this file are inconsistent and we do not know which are correct.

</details>

#### End-of-fiscal-year:

```{r}
ice_detention_management_ay_files <-
  tibble::tribble(
            ~Start,            ~End,                                                              ~Source,                                                                                                                                                           ~Download,
    "Oct. 1, 2023", "Sep. 30, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537358917'>xlsx</a> (242 kB)",
    "Oct. 1, 2022", "Sep. 30, 2023",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545074923'>xlsx</a> (234 kB)",
    "Oct. 1, 2021", "Sep. 30, 2022",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537940671'>xlsx</a> (196 kB)",
    "Oct. 1, 2020", "Sep. 30, 2021",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552983586'>xlsx</a> (134 kB)",
    "Oct. 1, 2019", "Sep. 30, 2020",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270675'>xlsx</a> (136 kB)",
    "Oct. 1, 2018", "Sep. 30, 2019",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538549260'>xlsx</a> (132 kB)"
  )
```

```{r}
ice_detention_management_ay_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ay_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>

### Annual report

ICE compiles a variety of descriptive statistics in its annual report.

```{r}
ice_annual_reports_files <-
  tibble::tribble(
    ~Date,                                                                     ~Source,                                                                                                                                                        ~Download,
    "2024",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539286110'>pdf</a> (3 MB)",
    "2023",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544782511'>pdf</a> (4 MB)",
    "2022",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554989243'>pdf</a> (6 MB)",
    "2021",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555047424'>pdf</a> (7 MB)",
    "2020",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556005548'>pdf</a> (3 MB)"
  )
```

```{r}
ice_annual_reports_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>

### Detention facility list

ICE released a list of detention facilities in 2017. These data include a facility identifier that can be joined with ICE detention data.

```{r}
tibble(
  Date = "Nov. 6, 2017",
  Source = "<a href='https://immigrantjustice.org/ice-detention-facilities-november-2017'>NIJC</a>",
  Download = "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538055645'>xlsx</a> (2 MB)"
) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

## Customs and Border Protection 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Southwest Land Border Encounters](https://www.cbp.gov/newsroom/stats/southwest-land-border-encounters)
: Dashboard tracking encounters along the southern border at and between ports of entry.

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Statistics covering many aspects of CBP's enforcement actions.

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
: Statistics tracking detention and outcomes after border encounters at and between ports of entry.

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a set of [court workload and adjudication statistics](https://www.justice.gov/eoir/workload-and-adjudication-statistics).

## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

Through January 2025, the Office of Homeland Security Statistics released a monthly spreadsheet tracking a variety of actions by both CBP and ICE. We do not know whether to expect future releases.

```{r}
enf_files <-
  tibble::tribble(
          ~Date,                                                                                               ~Source,                                                                                                                                                           ~Download,
    "Jan. 2025",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538278882'>xlsx</a> (712 kB)",
    "Dec. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538669625'>xlsx</a> (671 kB)",
    "Nov. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532468031'>xlsx</a> (668 kB)",
    "Oct. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522683414'>xlsx</a> (678 kB)",
    "Sep. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537352654'>xlsx</a> (673 kB)",
    "Aug. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538234805'>xlsx</a> (669 kB)",
    "Jul. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534182041'>xlsx</a> (666 kB)",
    "Jun. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521399297'>xlsx</a> (653 kB)",
    "May. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532585571'>xlsx</a> (644 kB)",
    "Apr. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535261459'>xlsx</a> (478 kB)",
    "Mar. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530651460'>xlsx</a> (406 kB)",
    "Feb. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524668163'>xlsx</a> (407 kB)",
    "Jan. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536929304'>xlsx</a> (401 kB)"
  )
```

```{r}
enf_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
enf_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>
