---
title: "Report repository"
---

```{r}
library(tidyverse)
library(reactable)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

Our project's focus is on collecting and posting individual-level data, but this page is an exception: here, we collect and repost government reports that draw from the individual-level datasets we post. We hope that this centralized repository of reports (and links to government websites) will help users of the individual-level data.  

The reports come from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Protection (CBP), and the Executive Office of Immigration Review (EOIR). These reports are generally available for download from the government directly; we repost them for users' convenience. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the reports before we have, we link to their sites as the source.

## Customs and Border Protection 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Southwest Land Border Encounters](https://www.cbp.gov/newsroom/stats/southwest-land-border-encounters)
: Dashboard tracking encounters along the southern border at and between ports of entry.

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Statistics covering many aspects of CBP's enforcement actions.

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
: Statistics tracking detention and outcomes after border encounters at and between ports of entry.

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a set of [court workload and adjudication statistics](https://www.justice.gov/eoir/workload-and-adjudication-statistics).

## Immigration and Customs Enforcement


```{r}
col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(minWidth = 100, html = TRUE)
)
```

### Annual report

ICE compiles a variety of descriptive statistics in its annual report.

```{r}
ice_annual_reports_files <-
  tibble::tribble(
    ~Date,                                                                     ~Source,                                                                                                                                                        ~Download,
    "2024",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539286110'>pdf</a> (3 MB)",
    "2023",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544782511'>pdf</a> (4 MB)",
    "2022",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554989243'>pdf</a> (6 MB)",
    "2021",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555047424'>pdf</a> (7 MB)",
    "2020",   "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556005548'>pdf</a> (3 MB)"
  )
```

```{r}
ice_annual_reports_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>

### Detention management spreadsheet

ICE releases a spreadsheet about twice a month that tracks book-ins, case types, detention facility information, and other descriptive statistics related to detention. 

```{r}
ice_detention_management_ytd_files <-
  tibble::tribble(
            ~Start,             ~End,                                                              ~Source,                                                                                                                                                           ~Download,
    "Oct. 1, 2024",  "Jun. 6, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href=''>xlsx</a> (1.5 MB)",
    "Oct. 1, 2024",  "May 23, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.box.com/shared/static/5l1cjsg7m5z1jymfuuvl7r9khoc9klnj.xlsx'>xlsx</a> (237 kB)",
    "Oct. 1, 2024",  "May 12, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.box.com/shared/static/0qda0lokm4pkdmpapdt0z7196ocn5nd5.xlsx'>xlsx</a> (235 kB)",
    "Oct. 1, 2024",  "May 9, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.box.com/shared/static/ao6qved0fhe9l4a1dw17m6z2txluuu2s.xlsx'>xlsx</a> (229 kB)",
    "Oct. 1, 2024",  "Apr. 16, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552829382'>xlsx</a> (232 kB)",
    "Oct. 1, 2024",  "Mar. 26, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554085594'>xlsx</a> (227 kB)",
    "Oct. 1, 2024",  "Mar. 14, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541591004'>xlsx</a> (223 kB)",
    "Oct. 1, 2024",   "Mar. 5, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550259001'>xlsx</a> (217 kB)",
    "Oct. 1, 2024",  "Feb. 27, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540128756'>xlsx</a> (225 kB)",
    "Oct. 1, 2024",  "Feb. 14, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552563416'>xlsx</a> (219 kB)",
    "Oct. 1, 2024",   "Feb. 3, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545131055'>xlsx</a> (213 kB)",
    "Oct. 1, 2024",  "Jan. 16, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555985237'>xlsx</a> (219 kB)",
    "Oct. 1, 2024",   "Jan. 3, 2025",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551099839'>xlsx</a> (216 kB)",
    "Oct. 1, 2024",  "Dec. 18, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554106108'>xlsx</a> (233 kB)",
    "Oct. 1, 2024",  "Dec. 12, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548019897'>xlsx</a> (226 kB)",
    "Oct. 1, 2024",  "Dec. 11, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546642190'>xlsx</a> (232 kB)",
    "Oct. 1, 2024",  "Nov. 21, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555637335'>xlsx</a> (255 kB)",
  )
```

#### Year-to-date:

```{r}
ice_detention_management_ytd_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ytd_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>

#### End-of-fiscal-year:

```{r}
ice_detention_management_ay_files <-
  tibble::tribble(
            ~Start,            ~End,                                                              ~Source,                                                                                                                                                           ~Download,
    "Oct. 1, 2023", "Sep. 30, 2024",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537358917'>xlsx</a> (242 kB)",
    "Oct. 1, 2022", "Sep. 30, 2023",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545074923'>xlsx</a> (234 kB)",
    "Oct. 1, 2021", "Sep. 30, 2022",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537940671'>xlsx</a> (196 kB)",
    "Oct. 1, 2020", "Sep. 30, 2021",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552983586'>xlsx</a> (134 kB)",
    "Oct. 1, 2019", "Sep. 30, 2020",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270675'>xlsx</a> (136 kB)",
    "Oct. 1, 2018", "Sep. 30, 2019",  "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538549260'>xlsx</a> (132 kB)"
  )
```

```{r}
ice_detention_management_ay_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ay_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>

### Detention facility list

ICE released a list of detention facilities in 2017. These data include a facility identifier that can be joined with ICE detention data.

```{r}
tibble(
  Date = "Nov. 6, 2017",
  Source = "<a href='https://immigrantjustice.org/ice-detention-facilities-november-2017'>NIJC</a>",
  Download = "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538055645'>xlsx</a> (2 MB)"
) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

Through January 2025, the Office of Homeland Security Statistics released a monthly spreadsheet tracking a variety of actions by both CBP and ICE. We do not know whether to expect future releases.

```{r}
enf_files <-
  tibble::tribble(
          ~Date,                                                                                               ~Source,                                                                                                                                                           ~Download,
    "Jan. 2025",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538278882'>xlsx</a> (712 kB)",
    "Dec. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538669625'>xlsx</a> (671 kB)",
    "Nov. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532468031'>xlsx</a> (668 kB)",
    "Oct. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522683414'>xlsx</a> (678 kB)",
    "Sep. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537352654'>xlsx</a> (673 kB)",
    "Aug. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538234805'>xlsx</a> (669 kB)",
    "Jul. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534182041'>xlsx</a> (666 kB)",
    "Jun. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521399297'>xlsx</a> (653 kB)",
    "May. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532585571'>xlsx</a> (644 kB)",
    "Apr. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535261459'>xlsx</a> (478 kB)",
    "Mar. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530651460'>xlsx</a> (406 kB)",
    "Feb. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524668163'>xlsx</a> (407 kB)",
    "Jan. 2024",   "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",   "<a href='https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536929304'>xlsx</a> (401 kB)"
  )
```

```{r}
enf_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
enf_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = colDef(minWidth = 100, html = TRUE)
    ),
    pagination = FALSE
  )
```

</details>
