---
title: "Agency report repository"
---

```{r}
library(tidyverse)
library(reactable)
library(htmltools)

col_defs <- list(
  Start = colDef(minWidth = 75),
  End = colDef(minWidth = 75),
  Records = colDef(minWidth = 55, align = "right"),
  Source = colDef(minWidth = 65, html = TRUE),
  Download = colDef(
    minWidth = 100,
    html = TRUE,
    cell = function(value) {
      if (is.null(value) || length(value) == 0) {
        return("&ndash;") # en dash
      }

      url <- as.character(value[[1]])
      size <- as.character(value[[2]])
      ext <- tolower(trimws(as.character(value[[3]])))

      paste0(
        "<a href='",
        url,
        "'>",
        "<img src='/img/",
        ext,
        ".svg' width=25 height=25 alt='",
        ext,
        "'>",
        "</a>",
        " (",
        size,
        ")"
      )
    }
  )
)

options(
  reactable.theme = reactableTheme(
    backgroundColor = "#F4F6F7"
  )
)
```

Our project's focus is on collecting and posting individual-level data, but this page is an exception: here, we collect and repost government reports that draw from the individual-level datasets we post. We hope that this centralized repository of reports (and links to government websites) will help users of the individual-level data.  

The reports come from the Office of Homeland Security Statistics (OHSS), Immigration and Customs Enforcement (ICE), Customs and Border Protection (CBP), and the Executive Office of Immigration Review (EOIR). These reports are generally available for download from the government directly; we repost them for users' convenience. The original source is always a government agency (OHSS, ICE, CBP, or EOIR), but where other third parties have posted the reports before we have, we link to their sites as the source.


## Immigration and Customs Enforcement


### Detention management spreadsheet

ICE releases a spreadsheet about twice a month that tracks book-ins, case types, detention facility information, and other descriptive statistics related to detention. 

```{r}
ice_detention_management_ytd_files <-
  tibble::tribble(
    ~Start,
    ~End,
    ~Source,
    ~Download,
    "Oct. 1, 2024",
    "Sep. 11, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984418543821",
      "1.6 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Aug. 29, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1984423132721",
      "1.6 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Aug. 14, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/eouwbvfx7x7tosqws4j4w6trbmw5smv9.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Aug. 1, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/lra9r9p038hsze5ngqzwqzwgqiqatoyr.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jul. 17, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/m4cyew6nyiizbmi00ysop1n5d1a97q8t.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jul. 7, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/7z4bmopvk5ww9uqutgw1pytupltj9hbe.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jun. 20, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/86rndu1ry7sy50ot76nymgyopged3p4s.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jun. 6, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/hvkcf6dg6o33ndywk2e769kdkzdc6cao.xlsx",
      "1.5 MB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "May 23, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/5l1cjsg7m5z1jymfuuvl7r9khoc9klnj.xlsx",
      "237 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "May 12, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/0qda0lokm4pkdmpapdt0z7196ocn5nd5.xlsx",
      "235 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "May 9, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.box.com/shared/static/ao6qved0fhe9l4a1dw17m6z2txluuu2s.xlsx",
      "229 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Apr. 16, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552829382",
      "232 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Mar. 26, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554085594",
      "227 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Mar. 14, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836541591004",
      "223 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Mar. 5, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836550259001",
      "217 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Feb. 27, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836540128756",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Feb. 14, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552563416",
      "219 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Feb. 3, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545131055",
      "213 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jan. 16, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555985237",
      "219 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Jan. 3, 2025",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836551099839",
      "216 kB",
      "xlsx"
    ),

    "Oct. 1, 2024",
    "Dec. 18, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554106108",
      "233 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Dec. 12, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836548019897",
      "226 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Dec. 11, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836546642190",
      "232 kB",
      "xlsx"
    ),
    "Oct. 1, 2024",
    "Nov. 21, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555637335",
      "255 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Nov. 15, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941072318562",
      "264 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Sep. 17, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941077817551",
      "239 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Aug. 29, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082436598",
      "242 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Aug. 15, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081969293",
      "288 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jul. 18, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941083200417",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jul. 8, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085786880",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jun. 20, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941084004584",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jun. 6, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941080010085",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "May 24, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941085247212",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "May 13, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086522189",
      "252 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Apr. 25, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082211453",
      "218 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Apr. 12, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074375974",
      "218 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Mar. 29, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082281029",
      "217 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Mar. 14, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941076962190",
      "216 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Feb. 29, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941074359174",
      "215 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Feb. 15, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941082190380",
      "215 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Feb. 1, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941081416603",
      "217 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jan. 11, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086543044",
      "208 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Jan. 4, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1941086997347",
      "206 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Dec. 20, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908777252",
      "208 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Dec. 7, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913075897",
      "208 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Nov. 22, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906505313",
      "225 kB",
      "xlsx"
    ),
    "Oct. 1, 2023",
    "Nov. 15, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485",
      "224 kB",
      "xlsx"
    ),

    "Oct. 1, 2023",
    "Nov. 15, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911605485",
      "224 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jul. 20, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911251765",
      "207 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jun. 12, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909284347",
      "204 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jul. 10, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913817260",
      "207 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Aug. 31, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907013367",
      "207 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Aug. 18, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906301076",
      "208 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Aug. 3, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915962929",
      "208 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jun. 1, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905014976",
      "206 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "May 19, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905813740",
      "204 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "May 26, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906754538",
      "204 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "May 31, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913697446",
      "206 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Apr. 12, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912051015",
      "203 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Apr. 28, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909751864",
      "203 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Mar. 31, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912113859",
      "199 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Mar. 3, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909586300",
      "198 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Feb. 28, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915190064",
      "199 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Feb. 3, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910738664",
      "199 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jan. 9, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916580593",
      "207 kB",
      "xlsx"
    ),

    "Oct. 1, 2022",
    "Dec. 22, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940920797250",
      "194 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Dec. 12, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906831784",
      "195 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Dec. 7, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911184737",
      "194 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Dec. 6, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912552762",
      "170 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Nov. 28, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911484515",
      "196 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Nov. 16, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911060682",
      "191 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Oct. 31, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908029365",
      "234 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Sep. 29, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907570429",
      "210 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Sep. 25, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911763830",
      "209 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Aug. 31, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906478053",
      "177 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Aug. 19, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905467769",
      "177 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Aug. 9, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919155877",
      "190 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Aug. 4, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906991764",
      "190 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Sep. 29, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906997367",
      "197 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Sep. 15, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910892078",
      "205 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jul. 21, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911010158",
      "173 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jul. 8, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940903910232",
      "165 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jun. 27, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915903684",
      "167 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jun. 23, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911364962",
      "161 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jun. 17, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940914302649",
      "161 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jun. 16, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907911462",
      "163 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jun. 9, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919738187",
      "156 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "May 24, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911194243",
      "154 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "May 4, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912850610",
      "160 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Apr. 28, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940905778014",
      "158 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Apr. 13, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940911988538",
      "150 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Mar. 31, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912303490",
      "149 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Mar. 17, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906948837",
      "150 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Mar. 16, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907755224",
      "200 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Mar. 2, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940906572276",
      "145 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Feb. 16, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910321525",
      "169 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jan. 20, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940910950158",
      "144 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Jan. 11, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912048442",
      "213 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Jan. 10, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907136043",
      "127 kB",
      "xlsx"
    ),

    "Oct. 1, 2021",
    "Dec. 29, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912536107",
      "141 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Nov. 12, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909020231",
      "134 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Oct. 28, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913162043",
      "128 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Oct. 7, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907496257",
      "147 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Oct. 1, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912123545",
      "149 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Sep. 16, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919802973",
      "149 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Sep. 13, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919440819",
      "147 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Aug. 24, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940919320598",
      "140 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Aug. 6, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913342084",
      "147 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Jul. 22, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908650485",
      "140 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Jul. 8, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940907771615",
      "138 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Jun. 24, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916407415",
      "137 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Jun. 11, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916241709",
      "136 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Jun. 9, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912953557",
      "129 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "May 28, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940909887031",
      "130 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "May 13, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913297574",
      "133 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "May 3, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940908021660",
      "132 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Apr. 29, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940915947115",
      "132 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Apr. 14, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940913894081",
      "131 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Mar. 31, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940916285575",
      "127 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Mar. 17, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940912962867",
      "127 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Mar. 1, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1940904921171",
      "125 kB",
      "xlsx"
    )
  )
```

#### Year-to-date:

```{r}
ice_detention_management_ytd_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ytd_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(),
      End = colDef(),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

\* The fiscal year and the dates in this file are inconsistent and we do not know which are correct.

</details>

#### End-of-fiscal-year:

```{r}
ice_detention_management_ay_files <-
  tibble::tribble(
    ~Start,
    ~End,
    ~Source,
    ~Download,
    "Oct. 1, 2023",
    "Sep. 30, 2024",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537358917",
      "242 kB",
      "xlsx"
    ),
    "Oct. 1, 2022",
    "Sep. 30, 2023",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836545074923",
      "234 kB",
      "xlsx"
    ),
    "Oct. 1, 2021",
    "Sep. 30, 2022",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537940671",
      "196 kB",
      "xlsx"
    ),
    "Oct. 1, 2020",
    "Sep. 30, 2021",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836552983586",
      "134 kB",
      "xlsx"
    ),
    "Oct. 1, 2019",
    "Sep. 30, 2020",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836558270675",
      "136 kB",
      "xlsx"
    ),
    "Oct. 1, 2018",
    "Sep. 30, 2019",
    "<a href='https://www.ice.gov/detain/detention-management'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538549260",
      "132 kB",
      "xlsx"
    )
  )
```

```{r}
ice_detention_management_ay_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_detention_management_ay_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Start = colDef(align = "left"),
      End = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Annual report

ICE compiles a variety of descriptive statistics in its annual report.

```{r}
ice_annual_reports_files <-
  tibble::tribble(
    ~Date,
    ~Source,
    ~Download,
    "2024",
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836539286110",
      "3 MB",
      "pdf"
    ),
    "2023",
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836544782511",
      "4 MB",
      "pdf"
    ),
    "2022",
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836554989243",
      "6 MB",
      "pdf"
    ),
    "2021",
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836555047424",
      "7 MB",
      "pdf"
    ),
    "2020",
    "<a href='https://www.ice.gov/information-library/annual-report'>ICE</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836556005548",
      "3 MB",
      "pdf"
    )
  )
```

```{r}
ice_annual_reports_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
ice_annual_reports_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>

### Detention facility list

ICE released a list of detention facilities in 2017. These data include a facility identifier that can be joined with ICE detention data.

```{r}
tribble(
  ~Date,
  ~Source,
  ~Download,
  "Nov. 6, 2017",
  "<a href='https://immigrantjustice.org/ice-detention-facilities-november-2017'>NIJC</a>",
  list(
    "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538055645",
    "2 MB",
    "xlsx"
  )
) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

## Customs and Border Protection 

CBP maintains a set of dashboards including statistics from the year-to-date as well as recent fiscal years. These include:

[CBP Southwest Land Border Encounters](https://www.cbp.gov/newsroom/stats/southwest-land-border-encounters)
: Dashboard tracking encounters along the southern border at and between ports of entry.

[CBP Enforcement Statistics](https://www.cbp.gov/newsroom/stats/cbp-enforcement-statistics)
: Statistics covering many aspects of CBP's enforcement actions.

[Custody and Transfer Statistics](https://www.cbp.gov/newsroom/stats/custody-and-transfer-statistics)
: Statistics tracking detention and outcomes after border encounters at and between ports of entry.

## Executive Office for Immigration Review<br>(Immigration Courts)

The EOIR publishes a set of [court workload and adjudication statistics](https://www.justice.gov/eoir/workload-and-adjudication-statistics).

## Office of Homeland Security Statistics

### Immigration Enforcement and Legal Processes Monthly Tables

Through January 2025, the Office of Homeland Security Statistics released a monthly spreadsheet tracking a variety of actions by both CBP and ICE. We do not know whether to expect future releases.

```{r}
enf_files <-
  tibble::tribble(
    ~Date,
    ~Source,
    ~Download,
    "Jan. 2025",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538278882",
      "712 kB",
      "xlsx"
    ),
    "Dec. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538669625",
      "671 kB",
      "xlsx"
    ),
    "Nov. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532468031",
      "668 kB",
      "xlsx"
    ),
    "Oct. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836522683414",
      "678 kB",
      "xlsx"
    ),
    "Sep. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836537352654",
      "673 kB",
      "xlsx"
    ),
    "Aug. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836538234805",
      "669 kB",
      "xlsx"
    ),
    "Jul. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836534182041",
      "666 kB",
      "xlsx"
    ),
    "Jun. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836521399297",
      "653 kB",
      "xlsx"
    ),
    "May. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836532585571",
      "644 kB",
      "xlsx"
    ),
    "Apr. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836535261459",
      "478 kB",
      "xlsx"
    ),
    "Mar. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836530651460",
      "406 kB",
      "xlsx"
    ),
    "Feb. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836524668163",
      "407 kB",
      "xlsx"
    ),
    "Jan. 2024",
    "<a href='https://ohss.dhs.gov/topics/immigration/immigration-enforcement/monthly-tables'>OHSS</a>",
    list(
      "https://ucla.app.box.com/index.php?rm=box_download_shared_file&shared_name=9d8qnnduhus4bd5mwqt7l95kz34fic2v&file_id=f_1836536929304",
      "401 kB",
      "xlsx"
    )
  )
```

```{r}
enf_files |>
  slice(1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

<div style="margin-top: 0.5em;"></div>

<details>
<summary>Past reports</summary>

```{r}
enf_files |>
  slice(-1) |>
  reactable::reactable(
    columns = list(
      Date = colDef(align = "left"),
      Source = colDef(minWidth = 65, html = TRUE),
      Download = col_defs$Download
    ),
    pagination = FALSE
  )
```

</details>
